---
title: "Gathering OpenAlex Articles Using API"
author: "Alexander Harriman"
date: "2025-05-21"
output: html_document
---


Code last updated March 16, 2026.


This code gathers publishing information directly from OpenAlex using their publicly-available API, then cleans up publishing data and saves it to the library publishing database.


The Publishing Database contains the following:

* All publishing data for the UT System is up to date as of March 12, 2026 and includes 2014-2025 info. 
* All publishing data for the SEC and Peer Institutions is up to date as of August 2025 and includes 2014-2024 info.


# Load Packages


```{r, warning = FALSE}
library(dplyr)
library(tidyverse)
library(RSQLite)
library(openalexR) #This package is required to access the OpenAlex API. If this is your first time using this code, it will need to be installed before use.
```


# Input a mailto email

This improves the gathering time from the API. You can input any email here; you will not receive actual emails to it.

```{r}
options(openalexR.mailto = 'YOUREMAILHERE.edu') 
```



# Connect to the UT Publication Database

The full file path will need to go in the quotes below. The easiest method to do this is by going into your files, right-clicking on the folder, and selecting "Copy Address as Text" or "Copy as Path" (phrasing may differ on Mac).


```{r}
con <- dbConnect(SQLite(), "C:\\Users\\aharrima\\OneDrive - University of Tennessee\\Documents\\UTK_Publications.db")
```



# Institution Check

Use this query to gather information on an institution or institution(s) of interest. 

The best way to filter down to a specific group of institutions in this API is by using its/their ROR access link. ROR information can be found using this link: https://ror.org/


Once the ROR is known, this cell will gather information about the institution you are attempting to gather from. If the institution name is somewhat common, use this to make sure you're gathering the right one.

```{r}
institutionInfo <- oa_fetch(
  entity = "institutions",
  ror = "https://ror.org/020f3ap87"
)

institutionInfo
```


## Commonly Used ROR Values for the UT System, SEC, and Peer Institutions:

Make sure to copy the full URLs below if applying them to the code.


### UT System

* UT Knoxville - https://ror.org/020f3ap87
* UT Chattanooga - https://ror.org/00nqb1v70
* UT Martin - https://ror.org/01244fm76
* UT Health Science Center - https://ror.org/0011qv509

### Tennessee Universities Outside of UT System

* Vanderbilt University - https://ror.org/02vm5rt34
* University of Memphis - https://ror.org/01cq23130


### Other SEC Universities

* University of Kentucky - https://ror.org/02k3smh20
* University of Missouri - https://ror.org/02ymw8z06
* University of Florida - https://ror.org/02y3ad647
* University of Georgia - https://ror.org/00te3t702
* Louisiana State University - https://ror.org/05ect4e57
* University of Texas Austin - https://ror.org/00hj54h04
* University of Oklahoma - https://ror.org/02aqsxs83
* University of South Carolina - https://ror.org/02b6qw903
* University of Arkansas Fayetteville - https://ror.org/05jbt9m15
* University of Mississippi (Ole Miss) - https://ror.org/02teq1165
* University of Alabama - https://ror.org/03xrrjk67
* Texas A&M University - https://ror.org/01f5ytq51
* Auburn University - https://ror.org/02v80fc35
* Mississippi State University - https://ror.org/0432jq872


### UT Peer Institutions

* Clemson University - https://ror.org/037s24f05
* Iowa State - https://ror.org/04rswrd78
* University of Colorado - https://ror.org/02ttsq026
* University of Nebraska - https://ror.org/043mer456
* Virginia Tech - https://ror.org/02smfhw86





# Gather Articles

Just as with the institution query above, use the ROR to filter down to specific institutions.

There are many different columns that can be used for filtering, but OpenAlex has specific formatting for many of them. To see a full list of callable columns, scroll to the bottom of the code.



## Example: UT Knoxville Publications 2014-2025

```{r, warning = FALSE}
utKnoxvillePubs <- data.frame()


# The "i" range should be all years you wish to gather. The first and last year of the range will also be gathered.
for(i in 2014:2025){
  utKnoxvilleYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/020f3ap87',
    publication_year = i,
    verbose = TRUE
  )
  utKnoxvillePubs <- rbind(utKnoxvillePubs, utKnoxvilleYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes for each year, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step for each year. 



# Convert the Sub Dataframes Into Lists


Note that if the API is updated, the exact column formatting may change. In particular, the order of columns might require changing some of the numbers in the cell below.

```{r}
cleanExportData <- utKnoxvillePubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()
apcCost <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 1000 == 0){ #Used as a timer for large data gathering and cleaning.
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  apcCostFinal <- ''
  
  # Subjects
  subjectFrame <- cleanExportData[[32]][[i]] #The first number is the column representing Subjects (or closest synonym).
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]] #Thie first number is the column listing the author names. 
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
    utAuthorships <- append(utAuthorships, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA,
             utAuthorships = NA)
    
    # Include all references to the university in each of the grepl statements below. Note that universities may have different affiliation methods; each of the three need all known affiliation formats.
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse(grepl('University of Tennessee', corresponding$affiliation_raw[j], fixed = TRUE) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse(grepl('University of Tennessee', corresponding$affiliation_raw[j], fixed = TRUE) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse(grepl('University of Tennessee', corresponding$affiliation_raw[j], fixed = TRUE) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
  
  # APC Cost
  costs <- cleanExportData[[40]][[i]] #The first number is the column listing APC information. Note that not all publications will have this info.
  
  if(length(dim(costs)) == 0){
    apcCost <- append(apcCost, NA)
  }
  
  else{
    usdCost <- costs$value_usd[1]
    apcCost <- append(apcCost, usdCost)
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool, apcCost))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor', 'APC')

allInfo <- cbind(cleanExportData, newInformation)


# Select Columns for the Database
removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor, APC)
```

# Clean up the Columns


This cell cleans up oddly formatted text for various important columns.

```{r}
databaseTable <- removeColumns |>
  
  # Remove Special Characters and Spaces
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  
  # Campus and Data Source Identifiers
  mutate(`Publication Campus` = 'UT Knoxville',
         `Publication Source` = 'OpenAlex') |>
  
  # Clean up Publisher Names
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    host_organization_name == 'Multidisciplinary Digital Publishing Institute' ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    host_organization_name == 'AcademicPres' ~ 'Academic Press',
    host_organization_name == 'Columbia University Libraries' ~ 'Columbia University Press',
    host_organization_name == 'Indiana University' ~ 'Indiana University Press',
    host_organization_name == 'Inter-Research' ~ 'Inter-Research Science Center',
    host_organization_name == 'Royal Society' ~ 'Royal Society Publishers',
    host_organization_name == 'University of Arizona' | host_organization_name == 'University of Arizona Libraries' ~ 'University of Arizona Press',
    host_organization_name == 'Univeristy of Minnesota' ~ 'University of Minnesota Libraries Publishing',
    host_organization_name == 'Wolters Kluwer Health' ~ 'Wolters Kluwer',
    .default = host_organization_name
  )) |>
  
  # Make APCs a cost, not a string
  mutate(APC = as.numeric(APC))
```


# Save Publishing Data to Database


WARNING: Once you overwrite a table, the old information is permanently deleted! Make sure everything is properly cleaned and formatted before saving.

```{r}
dbWriteTable(con, 'openalex_pubs_utk', databaseTable, overwrite = TRUE, row.names = FALSE)
```




## Other Universities:

If you do not see the university you are gathering articles for below, you can copy the UTK chunk and edit it for that university. Edits for each new institution include:

* Changing the ROR link
* The affiliation name formats within first author, last author, and corresponding author
* The publication campus identifier line
* The name of the table in the database
* University-specific variable names (these do not technically need to be changed, but it is best practice to do so)







## UT Health Science Publications 2014-2025 (March 12, 2026)

```{r, warning = FALSE}
uthscPubs <- data.frame()


for(i in 2014:2025){
  uthscYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/0011qv509',
    publication_year = i,
    verbose = TRUE
  )
  uthscPubs <- rbind(uthscPubs, uthscYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- uthscPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()
apcCost <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 1000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  apcCostFinal <- ''
  
  # Subjects
  subjectFrame <- cleanExportData[[32]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
    utAuthorships <- append(utAuthorships, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA,
             utAuthorships = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Tennessee Health Science Center', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('University of Tennessee, Memphis', corresponding$affiliation_raw[j])) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Tennessee Health Science Center', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('University of Tennessee, Memphis', corresponding$affiliation_raw[j])) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Tennessee Health Science Center', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('University of Tennessee, Memphis', corresponding$affiliation_raw[j])) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
  
  # APC Cost
  costs <- cleanExportData[[40]][[i]]
  
  if(length(dim(costs)) == 0){
    apcCost <- append(apcCost, NA)
  }
  
  else{
    usdCost <- costs$value_usd[1]
    apcCost <- append(apcCost, usdCost)
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool, apcCost))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor', 'APC')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor, APC)
```



# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'Health Science',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    host_organization_name == 'Multidisciplinary Digital Publishing Institute' ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    host_organization_name == 'AcademicPres' ~ 'Academic Press',
    host_organization_name == 'Columbia University Libraries' ~ 'Columbia University Press',
    host_organization_name == 'Indiana University' ~ 'Indiana University Press',
    host_organization_name == 'Inter-Research' ~ 'Inter-Research Science Center',
    host_organization_name == 'Royal Society' ~ 'Royal Society Publishers',
    host_organization_name == 'University of Arizona' | host_organization_name == 'University of Arizona Libraries' ~ 'University of Arizona Press',
    host_organization_name == 'Univeristy of Minnesota' ~ 'University of Minnesota Libraries Publishing',
    host_organization_name == 'Wolters Kluwer Health' ~ 'Wolters Kluwer',
    .default = host_organization_name
  )) |>
  mutate(APC = as.numeric(APC))
```




```{r}
dbWriteTable(con, 'openalex_pubs_uthsc', databaseTable, overwrite = TRUE, row.names = FALSE)
```




## UT Chattanooga Publications 2014-2025 (March 12, 2026)

```{r, warning = FALSE}
utcPubs <- data.frame()


for(i in 2014:2025){
  utcYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/00nqb1v70',
    publication_year = i,
    verbose = TRUE
  )
  utcPubs <- rbind(utcPubs, utcYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 







# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- utcPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()
apcCost <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 1000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  apcCostFinal <- ''
  
  # Subjects
  subjectFrame <- cleanExportData[[32]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
    utAuthorships <- append(utAuthorships, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA,
             utAuthorships = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Tennessee at Chattanooga', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Chattanooga', corresponding$affiliation_raw[j])) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Tennessee at Chattanooga', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Chattanooga', corresponding$affiliation_raw[j])) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Tennessee at Chattanooga', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Chattanooga', corresponding$affiliation_raw[j])) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
  
  # APC Cost
  costs <- cleanExportData[[40]][[i]]
  
  if(length(dim(costs)) == 0){
    apcCost <- append(apcCost, NA)
  }
  
  else{
    usdCost <- costs$value_usd[1]
    apcCost <- append(apcCost, usdCost)
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool, apcCost))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor', 'APC')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor, APC)
```



# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'UT Chattanooga',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    host_organization_name == 'Multidisciplinary Digital Publishing Institute' ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    host_organization_name == 'AcademicPres' ~ 'Academic Press',
    host_organization_name == 'Columbia University Libraries' ~ 'Columbia University Press',
    host_organization_name == 'Indiana University' ~ 'Indiana University Press',
    host_organization_name == 'Inter-Research' ~ 'Inter-Research Science Center',
    host_organization_name == 'Royal Society' ~ 'Royal Society Publishers',
    host_organization_name == 'University of Arizona' | host_organization_name == 'University of Arizona Libraries' ~ 'University of Arizona Press',
    host_organization_name == 'Univeristy of Minnesota' ~ 'University of Minnesota Libraries Publishing',
    host_organization_name == 'Wolters Kluwer Health' ~ 'Wolters Kluwer',
    .default = host_organization_name
  )) |>
  mutate(APC = as.numeric(APC))
```




```{r}
dbWriteTable(con, 'openalex_pubs_utc', databaseTable, overwrite = TRUE, row.names = FALSE)
```






## UT Martin Publications 2014-2025 (March 12, 2026)

```{r, warning = FALSE}
utmPubs <- data.frame()


for(i in 2014:2025){
  utmYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/01244fm76',
    publication_year = i,
    verbose = TRUE
  )
  utmPubs <- rbind(utmPubs, utmYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 





# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- utmPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()
apcCost <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 1000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  apcCostFinal <- ''
  
  # Subjects
  subjectFrame <- cleanExportData[[32]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
    utAuthorships <- append(utAuthorships, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA,
             utAuthorships = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Tennessee at Martin', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Martin', corresponding$affiliation_raw[j]) | grepl('University of Tennessee at ,', corresponding$affiliation_raw[j])) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Tennessee at Martin', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Martin', corresponding$affiliation_raw[j]) | grepl('University of Tennessee at ,', corresponding$affiliation_raw[j])) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Tennessee at Martin', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Martin', corresponding$affiliation_raw[j]) | grepl('University of Tennessee at ,', corresponding$affiliation_raw[j])) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
  
  # APC Cost
  costs <- cleanExportData[[40]][[i]]
  
  if(length(dim(costs)) == 0){
    apcCost <- append(apcCost, NA)
  }
  
  else{
    usdCost <- costs$value_usd[1]
    apcCost <- append(apcCost, usdCost)
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool, apcCost))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor', 'APC')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor, APC)
```



# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'UT Martin',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    host_organization_name == 'Multidisciplinary Digital Publishing Institute' ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    host_organization_name == 'AcademicPres' ~ 'Academic Press',
    host_organization_name == 'Columbia University Libraries' ~ 'Columbia University Press',
    host_organization_name == 'Indiana University' ~ 'Indiana University Press',
    host_organization_name == 'Inter-Research' ~ 'Inter-Research Science Center',
    host_organization_name == 'Royal Society' ~ 'Royal Society Publishers',
    host_organization_name == 'University of Arizona' | host_organization_name == 'University of Arizona Libraries' ~ 'University of Arizona Press',
    host_organization_name == 'Univeristy of Minnesota' ~ 'University of Minnesota Libraries Publishing',
    host_organization_name == 'Wolters Kluwer Health' ~ 'Wolters Kluwer',
    .default = host_organization_name
  )) |>
  mutate(APC = as.numeric(APC))
```


```{r}
dbWriteTable(con, 'openalex_pubs_utm', databaseTable, overwrite = TRUE, row.names = FALSE)
```





# Memphis Publications



## University of Memphis Publications 2014-2024

```{r, warning = FALSE}
memphisPubs <- data.frame()


for(i in 2014:2024){
  memphisYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/01cq23130',
    publication_year = i,
    verbose = TRUE
  )
  memphisPubs <- rbind(memphisPubs, memphisYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- memphisPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 1000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('Memphis', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('Memphis', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('Memphis', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Memphis',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_umemphis', databaseTable, overwrite = TRUE, row.names = FALSE)
```












# Connect to the SEC Publication Database

```{r}
con <- dbConnect(SQLite(), "C:\\Users\\aharrima\\OneDrive - University of Tennessee\\Documents\\SEC_and_Peer_Publications.db")
```







## Vanderbilt University Publications 2014-2024

```{r, warning = FALSE}
vandyPubs <- data.frame()


for(i in 2014:2024){
  vandyYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/02vm5rt34',
    publication_year = i,
    verbose = TRUE
  )
  vandyPubs <- rbind(vandyPubs, vandyYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- vandyPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 1000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('Vanderbilt', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Vandy', corresponding$affiliation_raw[j])) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('Vanderbilt', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Vandy', corresponding$affiliation_raw[j])) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('Vanderbilt', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Vandy', corresponding$affiliation_raw[j])) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'Vanderbilt University',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_vanderbilt', databaseTable, overwrite = TRUE, row.names = FALSE)
```





## University of Kentucky Publications 2014-2024

```{r, warning = FALSE}
kentuckyPubs <- data.frame()


for(i in 2014:2024){
  kentuckyYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/02k3smh20',
    publication_year = i,
    verbose = TRUE
  )
  kentuckyPubs <- rbind(kentuckyPubs, kentuckyYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- kentuckyPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 1000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('Kentucky', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('UNIVERSITY OF KENTUCKY', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('University of KY', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('Kentucky', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('UNIVERSITY OF KENTUCKY', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('University of KY', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('Kentucky', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('UNIVERSITY OF KENTUCKY', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('University of KY', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  mutate(trueKentucky = case_when(
          (grepl('Kentucky', Affiliations, fixed = TRUE) | (grepl('UNIVERSITY OF KENTUCKY', Affiliations, fixed = TRUE)) | (grepl('University of KY', Affiliations, fixed = TRUE))) ~ 1,
    .default = 0
  )) |>
  filter(trueKentucky == 1) |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Kentucky',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_kentucky', databaseTable, overwrite = TRUE, row.names = FALSE)
```







## Mississippi State University Publications 2014-2024

```{r, warning = FALSE}
msStPubs <- data.frame()


for(i in 2014:2024){
  msStYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/0432jq872',
    publication_year = i,
    verbose = TRUE
  )
  msStPubs <- rbind(msStPubs, msStYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 







# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- msStPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 1000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('Mississippi State', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Starkville', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Mississippii State', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Mis-sissippi State', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('Mississippi State', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Starkville', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Mississippii State', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Mis-sissippi State', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('Mississippi State', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Starkville', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Mississippii State', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Mis-sissippi State', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  mutate(trueMS = case_when(
          (grepl('Mississippi State', Affiliations, fixed = TRUE) | grepl('Starkville', Affiliations, fixed = TRUE) | grepl('Mississippii State', Affiliations, fixed = TRUE) | grepl('Mis-sissippi State', Affiliations, fixed = TRUE)) ~ 1,
    .default = 0
  )) |>
  filter(trueMS == 1) |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'Mississippi State',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_mississippistate', databaseTable, overwrite = TRUE, row.names = FALSE)
```





## University of Missouri Publications 2014-2024 

```{r, warning = FALSE}
missouriPubs2 <- data.frame()


for(i in 2014:2024){
  missouriYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/02ymw8z06',
    publication_year = i,
    verbose = TRUE
  )
  missouriPubs2 <- rbind(missouriPubs2, missouriYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 





# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- missouriPubs2 |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2500 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Missouri', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Columbia MO', corresponding$affiliation_raw[j]) | (grepl('UNIVERSITY OF MISSOURI', corresponding$affiliation_raw[j], fixed = TRUE))  | (grepl('Columbia, MO', corresponding$affiliation_raw[j], fixed = TRUE))  | (grepl('Univ. of Missouri', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Missouri', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Columbia MO', corresponding$affiliation_raw[j]) | (grepl('UNIVERSITY OF MISSOURI', corresponding$affiliation_raw[j], fixed = TRUE))  | (grepl('Columbia, MO', corresponding$affiliation_raw[j], fixed = TRUE))  | (grepl('Univ. of Missouri', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Missouri', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Columbia MO', corresponding$affiliation_raw[j]) | (grepl('UNIVERSITY OF MISSOURI', corresponding$affiliation_raw[j], fixed = TRUE))  | (grepl('Columbia, MO', corresponding$affiliation_raw[j], fixed = TRUE))  | (grepl('Univ. of Missouri', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Missouri',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_missouri', databaseTable, overwrite = TRUE, row.names = FALSE)
```





## University of Florida Publications 2014-2024

```{r, warning = FALSE}
ufPubs <- data.frame()


for(i in 2014:2024){
  ufYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/02y3ad647',
    publication_year = i,
    verbose = TRUE
  )
  ufPubs <- rbind(ufPubs, ufYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- ufPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 5000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Florida', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Florida Univ', corresponding$affiliation_raw[j]) | grepl('Gainesville', corresponding$affiliation_raw[j])) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Florida', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Florida Univ', corresponding$affiliation_raw[j]) | grepl('Gainesville', corresponding$affiliation_raw[j])) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Florida', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Florida Univ', corresponding$affiliation_raw[j]) | grepl('Gainesville', corresponding$affiliation_raw[j])) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Florida',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_uflorida', databaseTable, overwrite = TRUE, row.names = FALSE)
```







## Texas A&M Publications 2014-2024

```{r, warning = FALSE}
texasAMPubs <- data.frame()


for(i in 2014:2024){
  texasAMYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/01f5ytq51',
    publication_year = i,
    verbose = TRUE
  )
  texasAMPubs <- rbind(texasAMPubs, texasAMYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- texasAMPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 5000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('Texas A&M', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('Texas A&M', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('Texas A&M', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'Texas A&M',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_texasa&m', databaseTable, overwrite = TRUE, row.names = FALSE)
```






## University of Texas Austin Publications 2014-2024

```{r, warning = FALSE}
texasPubs <- data.frame()


for(i in 2014:2024){
  texasYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/00hj54h04',
    publication_year = i,
    verbose = TRUE
  )
  texasPubs <- rbind(texasPubs, texasYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- texasPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 5000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Texas', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Texas', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Texas', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Texas Austin',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_texasaustin', databaseTable, overwrite = TRUE, row.names = FALSE)
```





## University of Alabama Publications 2014-2024

```{r, warning = FALSE}
alabamaPubs <- data.frame()


for(i in 2014:2024){
  alabamaYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/03xrrjk67',
    publication_year = i,
    verbose = TRUE
  )
  alabamaPubs <- rbind(alabamaPubs, alabamaYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- alabamaPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2500 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse(((grepl('University of Alabama', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('Universidad de Alabama', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univ. of Alabama', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('The U. of Alabama', corresponding$affiliation_raw[j], fixed = TRUE))) & (!grepl('University of Alabama at', corresponding$affiliation_raw[j], fixed = TRUE)) & (!grepl('University of AlabamaBirmingham', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse(((grepl('University of Alabama', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('Universidad de Alabama', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univ. of Alabama', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('The U. of Alabama', corresponding$affiliation_raw[j], fixed = TRUE))) & (!grepl('University of Alabama at', corresponding$affiliation_raw[j], fixed = TRUE)) & (!grepl('University of AlabamaBirmingham', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse(((grepl('University of Alabama', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('Universidad de Alabama', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univ. of Alabama', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('The U. of Alabama', corresponding$affiliation_raw[j], fixed = TRUE))) & (!grepl('University of Alabama at', corresponding$affiliation_raw[j], fixed = TRUE)) & (!grepl('University of AlabamaBirmingham', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  mutate(trueAlabama = case_when(
          (grepl('University of Alabama', Affiliations, fixed = TRUE) | (grepl('Universidad de Alabama', Affiliations, fixed = TRUE)) | (grepl('Univ. of Alabama', Affiliations, fixed = TRUE)) | (grepl('The U. of Alabama', Affiliations, fixed = TRUE))) ~ 1,
    .default = 0
  )) |>
  filter(trueAlabama == 1) |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Alabama',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_alabama', databaseTable, overwrite = TRUE, row.names = FALSE)
```







## Auburn University Publications 2014-2024

```{r, warning = FALSE}
auburnPubs <- data.frame()


for(i in 2014:2024){
  auburnYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/02v80fc35',
    publication_year = i,
    verbose = TRUE
  )
  auburnPubs <- rbind(auburnPubs, auburnYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- auburnPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2500 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('Auburn University', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('Auburn.University', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('AUBURN', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Auburn U', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Auburn ', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Auburn, AL', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('Auburn University', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('Auburn.University', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('AUBURN', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Auburn U', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Auburn ', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Auburn, AL', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('Auburn University', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('Auburn.University', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('AUBURN', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Auburn U', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Auburn ', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Auburn, AL', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  mutate(trueAuburn = case_when(
          (grepl('Auburn University', Affiliations, fixed = TRUE) | (grepl('Auburn.University', Affiliations, fixed = TRUE)) | (grepl('AUBURN', Affiliations, fixed = TRUE)) | (grepl('Auburn U', Affiliations, fixed = TRUE)) | (grepl('Auburn ', Affiliations, fixed = TRUE)) | (grepl('Auburn, AL', Affiliations, fixed = TRUE))) ~ 1,
    .default = 0
  )) |>
  filter(trueAuburn == 1) |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```



# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'Auburn University',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_auburn', databaseTable, overwrite = TRUE, row.names = FALSE)
```







## University of Oklahoma Publications 2014-2024

```{r, warning = FALSE}
oklahomaPubs <- data.frame()


for(i in 2014:2024){
  oklahomaYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/02aqsxs83',
    publication_year = i,
    verbose = TRUE
  )
  oklahomaPubs <- rbind(oklahomaPubs, oklahomaYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- oklahomaPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2500 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Oklahoma', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Oklahoma', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Oklahoma', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Oklahoma',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_oklahoma', databaseTable, overwrite = TRUE, row.names = FALSE)
```





## University of Georgia Publications 2014-2024

```{r, warning = FALSE}
georgiaPubs <- data.frame()


for(i in 2014:2024){
  georgiaYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/00te3t702',
    publication_year = i,
    verbose = TRUE
  )
  georgiaPubs <- rbind(georgiaPubs, georgiaYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- georgiaPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 5000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Georgia', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('Univ. of Georgia', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('University of  Georgia', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('U. Georgia', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Georgia', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('Univ. of Georgia', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('University of  Georgia', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('U. Georgia', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Georgia', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('Univ. of Georgia', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('University of  Georgia', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('U. Georgia', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```




# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Georgia',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_georgia', databaseTable, overwrite = TRUE, row.names = FALSE)
```








## University of South Carolina Publications 2014-2024

```{r, warning = FALSE}
chickenPubs <- data.frame()


for(i in 2014:2024){
  chickenYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/02b6qw903',
    publication_year = i,
    verbose = TRUE
  )
  chickenPubs <- rbind(chickenPubs, chickenYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- chickenPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2500 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of South Carolina', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('University of  South Carolina', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of South Carolina', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('University of  South Carolina', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of South Carolina', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('University of  South Carolina', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```

# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of South Carolina',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_southcarolina', databaseTable, overwrite = TRUE, row.names = FALSE)
```







## University of Mississippi (Ole Miss) Publications 2014-2024

```{r, warning = FALSE}
oleMissPubs <- data.frame()


for(i in 2014:2024){
  oleMissYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/02teq1165',
    publication_year = i,
    verbose = TRUE
  )
  oleMissPubs <- rbind(oleMissPubs, oleMissYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- oleMissPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2500 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Mississippi', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Univ of Mississippi', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Mississippi, USA ,', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Mississippi', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Univ of Mississippi', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Mississippi, USA ,', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Mississippi', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Univ of Mississippi', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Mississippi, USA ,', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```

# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Mississippi',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_olemiss', databaseTable, overwrite = TRUE, row.names = FALSE)
```





## Louisiana State University Publications 2014-2024

```{r, warning = FALSE}
lsuPubs <- data.frame()


for(i in 2014:2024){
  lsuYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/05ect4e57',
    publication_year = i,
    verbose = TRUE
  )
  lsuPubs <- rbind(lsuPubs, lsuYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- lsuPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2500 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('Louisiana State University', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('Louisiana State University', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('Louisiana State University', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```

# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'Louisiana State University',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_lsu', databaseTable, overwrite = TRUE, row.names = FALSE)
```






## University of Arkansas Publications 2014-2024

```{r, warning = FALSE}
arkansasPubs <- data.frame()


for(i in 2014:2024){
  arkansasYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/05jbt9m15',
    publication_year = i,
    verbose = TRUE
  )
  arkansasPubs <- rbind(arkansasPubs, arkansasYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 






# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- arkansasPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('University Of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univ. of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univerity of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('University of ArKansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('U. of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Fayetteville', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Universidad de Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('UAMS', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Uninversity of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('U of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univ. Arkansas', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('University Of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univ. of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univerity of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('University of ArKansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('U. of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Fayetteville', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Universidad de Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('UAMS', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Uninversity of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('U of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univ. Arkansas', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE) | (grepl('University Of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univ. of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univerity of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('University of ArKansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('U. of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Fayetteville', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Universidad de Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('UAMS', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Uninversity of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('U of Arkansas', corresponding$affiliation_raw[j], fixed = TRUE)) | (grepl('Univ. Arkansas', corresponding$affiliation_raw[j], fixed = TRUE))) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  mutate(trueArkansas = case_when(
          (grepl('University of Arkansas', Affiliations, fixed = TRUE) | (grepl('University Of Arkansas', Affiliations, fixed = TRUE)) | (grepl('Univ. of Arkansas', Affiliations, fixed = TRUE)) | (grepl('Univerity of Arkansas', Affiliations, fixed = TRUE)) | (grepl('University of ArKansas', Affiliations, fixed = TRUE)) | (grepl('U. of Arkansas', Affiliations, fixed = TRUE)) | (grepl('Fayetteville', Affiliations, fixed = TRUE)) | (grepl('Universidad de Arkansas', Affiliations, fixed = TRUE)) | (grepl('UAMS', Affiliations, fixed = TRUE)) | (grepl('Uninversity of Arkansas', Affiliations, fixed = TRUE)) | (grepl('U of Arkansas', Affiliations, fixed = TRUE)) | (grepl('Univ. Arkansas', Affiliations, fixed = TRUE))) ~ 1,
    .default = 0
  )) |>
  filter(trueArkansas == 1) |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor)
```

# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Arkansas',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    .default = host_organization_name
  ))
```




```{r}
dbWriteTable(con, 'openalex_pubs_arkansas', databaseTable, overwrite = TRUE, row.names = FALSE)
```






# Connect to the Peer Publication Database

```{r}
con <- dbConnect(SQLite(), "C:\\Users\\aharrima\\OneDrive - University of Tennessee\\Documents\\SEC_and_Peer_Publications.db")
```





## Clemson University Publications 2014-2024

```{r, warning = FALSE}
clemsonPubs <- data.frame()


for(i in 2014:2024){
  clemsonYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/037s24f05',
    publication_year = i,
    verbose = TRUE
  )
  clemsonPubs <- rbind(clemsonPubs, clemsonYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 




# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- clemsonPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()
apcCost <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('Clemson', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('Clemson', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('Clemson', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
  # APC Cost
  costs <- cleanExportData[[39]][[i]]
  
  if(length(dim(costs)) == 0){
    apcCost <- append(apcCost, NA)
  }
  
  else{
    usdCost <- costs$value_usd[1]
    apcCost <- append(apcCost, usdCost)
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool, apcCost))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor', 'APC')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor, APC)
```

# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'Clemson University',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    host_organization_name == 'Multidisciplinary Digital Publishing Institute' ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    host_organization_name == 'AcademicPres' ~ 'Academic Press',
    host_organization_name == 'Columbia University Libraries' ~ 'Columbia University Press',
    host_organization_name == 'Indiana University' ~ 'Indiana University Press',
    host_organization_name == 'Inter-Research' ~ 'Inter-Research Science Center',
    host_organization_name == 'Royal Society' ~ 'Royal Society Publishers',
    host_organization_name == 'University of Arizona' | host_organization_name == 'University of Arizona Libraries' ~ 'University of Arizona Press',
    host_organization_name == 'Univeristy of Minnesota' ~ 'University of Minnesota Libraries Publishing',
    host_organization_name == 'Wolters Kluwer Health' ~ 'Wolters Kluwer',
    .default = host_organization_name
  )) |>
  mutate(APC = as.numeric(APC))
```




```{r}
dbWriteTable(con, 'openalex_pubs_clemson', databaseTable, overwrite = TRUE, row.names = FALSE)
```








## Virginia Tech Publications 2014-2024

```{r, warning = FALSE}
virginiaTechPubs <- data.frame()


for(i in 2014:2024){
  virginiaTechYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/02smfhw86',
    publication_year = i,
    verbose = TRUE
  )
  virginiaTechPubs <- rbind(virginiaTechPubs, virginiaTechYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 




# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- virginiaTechPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()
apcCost <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('Virginia Tech', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Virginia Polytechnic', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('Virginia Tech', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Virginia Polytechnic', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('Virginia Tech', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Virginia Polytechnic', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
  # APC Cost
  costs <- cleanExportData[[39]][[i]]
  
  if(length(dim(costs)) == 0){
    apcCost <- append(apcCost, NA)
  }
  
  else{
    usdCost <- costs$value_usd[1]
    apcCost <- append(apcCost, usdCost)
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool, apcCost))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor', 'APC')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor, APC)


vtCheck <- removeColumns |>
  select(Affiliations)

vtCheck
```

# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'Virginia Tech',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    host_organization_name == 'Multidisciplinary Digital Publishing Institute' ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    host_organization_name == 'AcademicPres' ~ 'Academic Press',
    host_organization_name == 'Columbia University Libraries' ~ 'Columbia University Press',
    host_organization_name == 'Indiana University' ~ 'Indiana University Press',
    host_organization_name == 'Inter-Research' ~ 'Inter-Research Science Center',
    host_organization_name == 'Royal Society' ~ 'Royal Society Publishers',
    host_organization_name == 'University of Arizona' | host_organization_name == 'University of Arizona Libraries' ~ 'University of Arizona Press',
    host_organization_name == 'Univeristy of Minnesota' ~ 'University of Minnesota Libraries Publishing',
    host_organization_name == 'Wolters Kluwer Health' ~ 'Wolters Kluwer',
    .default = host_organization_name
  )) |>
  mutate(APC = as.numeric(APC))
```




```{r}
dbWriteTable(con, 'openalex_pubs_virginiatech', databaseTable, overwrite = TRUE, row.names = FALSE)
```









## Iowa State Publications 2014-2024

```{r, warning = FALSE}
iowaStatePubs <- data.frame()


for(i in 2014:2024){
  iowaStateYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/04rswrd78',
    publication_year = i,
    verbose = TRUE
  )
  iowaStatePubs <- rbind(iowaStatePubs, iowaStateYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 




# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- iowaStatePubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()
apcCost <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('Iowa State', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('Iowa State', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('Iowa State', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
  # APC Cost
  costs <- cleanExportData[[39]][[i]]
  
  if(length(dim(costs)) == 0){
    apcCost <- append(apcCost, NA)
  }
  
  else{
    usdCost <- costs$value_usd[1]
    apcCost <- append(apcCost, usdCost)
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool, apcCost))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor', 'APC')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor, APC)


iowaStateCheck <- removeColumns |>
  select(Affiliations)

iowaStateCheck
```

# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'Iowa State',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    host_organization_name == 'Multidisciplinary Digital Publishing Institute' ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    host_organization_name == 'AcademicPres' ~ 'Academic Press',
    host_organization_name == 'Columbia University Libraries' ~ 'Columbia University Press',
    host_organization_name == 'Indiana University' ~ 'Indiana University Press',
    host_organization_name == 'Inter-Research' ~ 'Inter-Research Science Center',
    host_organization_name == 'Royal Society' ~ 'Royal Society Publishers',
    host_organization_name == 'University of Arizona' | host_organization_name == 'University of Arizona Libraries' ~ 'University of Arizona Press',
    host_organization_name == 'Univeristy of Minnesota' ~ 'University of Minnesota Libraries Publishing',
    host_organization_name == 'Wolters Kluwer Health' ~ 'Wolters Kluwer',
    .default = host_organization_name
  )) |>
  mutate(APC = as.numeric(APC))
```




```{r}
dbWriteTable(con, 'openalex_pubs_iowastate', databaseTable, overwrite = TRUE, row.names = FALSE)
```









## Nebraska Publications 2014-2024

```{r, warning = FALSE}
nebraskaPubs <- data.frame()


for(i in 2014:2024){
  nebraskaYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/043mer456',
    publication_year = i,
    verbose = TRUE
  )
  nebraskaPubs <- rbind(nebraskaPubs, nebraskaYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 




# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- nebraskaPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()
apcCost <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Nebraska', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('university of nebraska', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Nebraska Univ.', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Univ. of Nebraska', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Nebraska', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('university of nebraska', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Nebraska Univ.', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Univ. of Nebraska', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Nebraska', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('university of nebraska', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Nebraska Univ.', corresponding$affiliation_raw[j], fixed = TRUE) | grepl('Univ. of Nebraska', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
  # APC Cost
  costs <- cleanExportData[[39]][[i]]
  
  if(length(dim(costs)) == 0){
    apcCost <- append(apcCost, NA)
  }
  
  else{
    usdCost <- costs$value_usd[1]
    apcCost <- append(apcCost, usdCost)
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool, apcCost))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor', 'APC')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor, APC)


nebraskaCheck <- removeColumns |>
  select(Affiliations)

nebraskaCheck
```

# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Nebraska',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    host_organization_name == 'Multidisciplinary Digital Publishing Institute' ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    host_organization_name == 'AcademicPres' ~ 'Academic Press',
    host_organization_name == 'Columbia University Libraries' ~ 'Columbia University Press',
    host_organization_name == 'Indiana University' ~ 'Indiana University Press',
    host_organization_name == 'Inter-Research' ~ 'Inter-Research Science Center',
    host_organization_name == 'Royal Society' ~ 'Royal Society Publishers',
    host_organization_name == 'University of Arizona' | host_organization_name == 'University of Arizona Libraries' ~ 'University of Arizona Press',
    host_organization_name == 'Univeristy of Minnesota' ~ 'University of Minnesota Libraries Publishing',
    host_organization_name == 'Wolters Kluwer Health' ~ 'Wolters Kluwer',
    .default = host_organization_name
  )) |>
  mutate(APC = as.numeric(APC))
```




```{r}
dbWriteTable(con, 'openalex_pubs_nebraska', databaseTable, overwrite = TRUE, row.names = FALSE)
```















## Colorado Publications 2014-2024

```{r, warning = FALSE}
coloradoPubs <- data.frame()


for(i in 2014:2024){
  coloradoYear <- oa_fetch(
    entity = 'works',
    authorships.institutions.ror = 'https://ror.org/02ttsq026',
    publication_year = i,
    verbose = TRUE
  )
  coloradoPubs <- rbind(coloradoPubs, coloradoYear)
}

```


**NOTE:** After running a query, OpenAlex will gather all of the "pages" of article data (which is how OpenAlex stores publications on its database) before a second round of querying creates a data frame. This process can take several minutes, varying greatly depending on the number of articles being gathered. The code automatically creates a progress bar that will run in the Console to show how much time the code needs to finish each step. 




# Convert the Sub Dataframes Into Lists

```{r}
cleanExportData <- coloradoPubs |>
  filter(is_retracted == FALSE) |>
  arrange(id)

subjectList <- c()
authorships <- c()
affiliations <- c()
isFirstSchool <- c()
isLastSchool <- c()
isCorrespondingSchool <- c()
apcCost <- c()



for(i in 1:dim(cleanExportData)[1]){
  if(i %% 2000 == 0){
    print(i)
  }
  subjectFinal <- ''
  authorsFinal <- ''
  affiliationFinal <- ''
  # Subjects
  subjectFrame <- cleanExportData[[33]][[i]]
  
  if(dim(subjectFrame)[1] == 0){
    subjectList <- append(subjectList, NA)
  }
  else{
    subjects <- subjectFrame |>
      filter(type == 'field') |>
      select(display_name)
  
    for(j in 1:dim(subjects)[1]){
      subjectFinal <- paste(subjectFinal, subjects$display_name[j], ',')
    }
    
    subjectList <- append(subjectList, subjectFinal)

  }  
  
  # Authors
  authorFrame <- cleanExportData[[4]][[i]]
  if(dim(authorFrame)[1] == 0){
    authorships <- append(authorships, NA)
  }
  else{
    authors <- authorFrame |>
      select(display_name)
    
    for(j in 1:dim(authors)[1]){
      authorsFinal <- paste(authorsFinal, authors$display_name[j], ',')
    }
    
    authorships <- append(authorships, authorsFinal)
  }
  
  # Author Affiliations
  affiliationInfo <- authorFrame |>
    select(affiliation_raw)
  
  if(dim(affiliationInfo)[1] == 0){
    affiliations <- append(affiliations, NA)
  }
  else{
    for(j in 1:dim(affiliationInfo)[1]){
      affiliationFinal <- paste(affiliationFinal, affiliationInfo$affiliation_raw[j], ',')
    }
    
    affiliations <- append(affiliations, affiliationFinal)
  }
  
  
  # First, Last, and Corresponding Author
  if(dim(authorFrame)[1] == 0){
    isFirstSchool <- append(isFirstSchool, NA)
    isLastSchool <- append(isLastSchool, NA)
    isCorrespondingSchool <- append(isCorrespondingSchool, NA)
  }
  else{
    corresponding <- authorFrame |>
      select(author_position, is_corresponding, affiliation_raw) |>
      mutate(isFirst = NA,
             isLast = NA,
             isCorresponding = NA)
    
    for(j in 1:dim(corresponding)[1]){
      corresponding$isFirst[j] <- ifelse((grepl('University of Colorado', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'first', 'Yes', 'No')
      corresponding$isLast[j] <- ifelse((grepl('University of Colorado', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$author_position[j] == 'last', 'Yes', 'No')
      corresponding$isCorresponding[j] <- ifelse((grepl('University of Colorado', corresponding$affiliation_raw[j], fixed = TRUE)) & corresponding$is_corresponding[j] == TRUE, 'Yes', 'No')
    }
    
    isFirstSchool <- append(isFirstSchool, ifelse('Yes' %in% corresponding$isFirst, 'Yes', 'No'))
    isLastSchool <- append(isLastSchool, ifelse('Yes' %in% corresponding$isLast, 'Yes', 'No'))
    isCorrespondingSchool <- append(isCorrespondingSchool, ifelse('Yes' %in% corresponding$isCorresponding, 'Yes', 'No'))
  }
  # APC Cost
  costs <- cleanExportData[[39]][[i]]
  
  if(length(dim(costs)) == 0){
    apcCost <- append(apcCost, NA)
  }
  
  else{
    usdCost <- costs$value_usd[1]
    apcCost <- append(apcCost, usdCost)
  }
}

newInformation <- as.data.frame(cbind(subjectList, authorships, affiliations, isFirstSchool, isLastSchool, isCorrespondingSchool, apcCost))

colnames(newInformation) <- c('Subjects', 'Authors', 'Affiliations', 'isFirstSchool', 'isLastSchool', 'isCorrespondingAuthor', 'APC')

allInfo <- cbind(cleanExportData, newInformation)

removeColumns <- allInfo |>
  select(id, title, display_name, abstract, doi, publication_date, publication_year, cited_by_count, type, is_oa, is_oa_anywhere, oa_status, any_repository_has_fulltext, language, source_display_name, issn_l, host_organization_name, referenced_works_count, first_page, last_page, volume, issue, fwci, Subjects, Authors, Affiliations, isFirstSchool, isLastSchool, isCorrespondingAuthor, APC)


coloradoCheck <- removeColumns |>
  select(Affiliations)

coloradoCheck
```

# Clean up the Columns


```{r}
databaseTable <- removeColumns |>
  mutate(Affiliations = gsub('#TAB#', '', Affiliations)) |>
  mutate(Affiliations = gsub('#N#', '', Affiliations)) |>
  mutate(Affiliations = gsub(',$', '', Affiliations),
         Authors = gsub(',$', '', Authors),
         Subjects = gsub(',$', '', Subjects)) |>
  mutate(Affiliations = str_trim(Affiliations),
         Authors = str_trim(Authors),
         Subjects = str_trim(Subjects)) |>
  mutate(`Publication Campus` = 'University of Colorado',
         `Publication Source` = 'OpenAlex') |>
  mutate(`Unified Publisher` = case_when(
    grepl('Elsevier', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Churchill', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Saunders', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Cell Press', host_organization_name) == TRUE ~ 'Elsevier',
    grepl('Nature', host_organization_name) == TRUE ~ 'Nature',
    grepl('IOP', host_organization_name) == TRUE ~ 'IOP',
    grepl('Sage', host_organization_name) == TRUE ~ 'Sage',
    grepl('SAGE', host_organization_name) == TRUE ~ 'Sage',
    grepl('Wiley', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Hindawi', host_organization_name) == TRUE ~ 'Wiley',
    grepl('Oxford', host_organization_name) == TRUE ~ 'OUP',
    grepl('Springer', host_organization_name) == TRUE ~ 'Springer',
    grepl('BMC', host_organization_name) == TRUE ~ 'Springer',
    grepl('MDPI', host_organization_name) == TRUE ~ 'MDPI',
    host_organization_name == 'Multidisciplinary Digital Publishing Institute' ~ 'MDPI',
    grepl('IEEE', host_organization_name) == TRUE ~ 'IEEE',
    grepl('Cambridge', host_organization_name) == TRUE ~ 'Cambridge',
    grepl('Taylor & Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    grepl('Taylor and Francis', host_organization_name) == TRUE ~ 'Taylor & Francis',
    host_organization_name == 'AcademicPres' ~ 'Academic Press',
    host_organization_name == 'Columbia University Libraries' ~ 'Columbia University Press',
    host_organization_name == 'Indiana University' ~ 'Indiana University Press',
    host_organization_name == 'Inter-Research' ~ 'Inter-Research Science Center',
    host_organization_name == 'Royal Society' ~ 'Royal Society Publishers',
    host_organization_name == 'University of Arizona' | host_organization_name == 'University of Arizona Libraries' ~ 'University of Arizona Press',
    host_organization_name == 'Univeristy of Minnesota' ~ 'University of Minnesota Libraries Publishing',
    host_organization_name == 'Wolters Kluwer Health' ~ 'Wolters Kluwer',
    .default = host_organization_name
  )) |>
  mutate(APC = as.numeric(APC))
```




```{r}
dbWriteTable(con, 'openalex_pubs_colorado', databaseTable, overwrite = TRUE, row.names = FALSE)
```








# Full Column Format List

**WARNING: Due to its long length and use of jargon, it may be easier to search this list for specific keywords.**



*abstract.search, abstract.search.no_stem, apc_list.currency, apc_list.provenance, apc_list.value, apc_list.value_usd, apc_paid.currency, apc_paid.provenance, apc_paid.value, apc_paid.value_usd, author.id, author.orcid, authors_count, authorships.affiliations.institution_ids, authorships.author.id, authorships.author.orcid, authorships.countries, authorships.institutions.continent, authorships.institutions.country_code, authorships.institutions.id, authorships.institutions.is_global_south, authorships.institutions.lineage, authorships.institutions.ror, authorships.institutions.type, authorships.is_corresponding, best_oa_location.is_accepted, best_oa_location.is_oa, best_oa_location.is_published, best_oa_location.landing_page_url, best_oa_location.license, best_oa_location.license_id, best_oa_location.source.host_organization, best_oa_location.source.host_organization_lineage, best_oa_location.source.id, best_oa_location.source.is_in_doaj, best_oa_location.source.is_oa, best_oa_location.source.issn, best_oa_location.source.type, best_oa_location.version, best_open_version, biblio.first_page, biblio.issue, biblio.last_page, biblio.volume, citation_normalized_percentile.is_in_top_10_percent, citation_normalized_percentile.is_in_top_1_percent, citation_normalized_percentile.value, cited_by, cited_by_count, cited_by_percentile_year.max, cited_by_percentile_year.min, cites, concept.id, concepts.id, concepts.wikidata, concepts_count, corresponding_author_ids, corresponding_institution_ids, countries_distinct_count, datasets, default.search, display_name, display_name.search, display_name.search.no_stem, doi, doi_starts_with, from_created_date, from_publication_date, fulltext.search, fulltext_origin, fwci, grants.award_id, grants.funder, has_abstract, has_doi, has_embeddings, has_fulltext, has_oa_accepted_or_published_version, has_oa_submitted_version, has_old_authors, has_orcid, has_pdf_url, has_pmcid, has_pmid, has_raw_affiliation_strings, has_references, ids.mag, ids.openalex, ids.pmcid, ids.pmid, indexed_in, institution.id, institution_assertions.country_code, institution_assertions.id, institution_assertions.lineage, institution_assertions.ror, institution_assertions.type, institutions.continent, institutions.country_code, institutions.id, institutions.is_global_south, institutions.ror, institutions.type, institutions_distinct_count, is_corresponding, is_oa, is_paratext, is_retracted, journal, keyword.search, keywords.id, language, locations.is_accepted, locations.is_oa, locations.is_published, locations.landing_page_url, locations.license, locations.license_id, locations.source.has_issn, locations.source.host_institution_lineage, locations.source.host_organization, locations.source.host_organization_lineage, locations.source.id, locations.source.is_core, locations.source.is_in_doaj, locations.source.is_oa, locations.source.issn, locations.source.publisher_lineage, locations.source.type, locations.version, locations_count, mag, mag_only, oa_status, open_access.any_repository_has_fulltext, open_access.is_oa, open_access.oa_status, openalex, openalex_id, pmcid, pmid, primary_location.is_accepted, primary_location.is_oa, primary_location.is_published, primary_location.landing_page_url, primary_location.license, primary_location.license_id, primary_location.source.has_issn, primary_location.source.host_institution_lineage, primary_location.source.host_organization, primary_location.source.host_organization_lineage, primary_location.source.id, primary_location.source.is_core, primary_location.source.is_in_doaj, primary_location.source.is_oa, primary_location.source.issn, primary_location.source.publisher_lineage, primary_location.source.type, primary_location.version, primary_topic.domain.id, primary_topic.field.id, primary_topic.id, primary_topic.subfield.id, publication_date, publication_year, raw_affiliation_strings.search, raw_author_name.search, referenced_works, referenced_works_count, related_to, repository, semantic.search, sustainable_development_goals.id, sustainable_development_goals.score, title.search, title.search.no_stem, title_and_abstract.search, title_and_abstract.search.no_stem, to_created_date, to_publication_date, to_updated_date, topics.domain.id, topics.field.id, topics.id, topics.subfield.id, topics_count, type, type_crossref, version*




# Next Steps:


### Looking to join this to the other databases?


If you are gathering UT System data, check out the "UT System Publication Joining" R code. Note that the PowerBI publishing dashboard only contains OpenAlex data for the SEC schools.


### Looking to use this data for a project?


You are good to use the database tables already! Connect the database to another code, or access it via SQLite3 on your computer if you just need to query it.


### Looking to gather other databases' publication data?

Check out the "Peer Institution" or "UT" Summary of Publications code files for code designed to clean those up, along with info on how to access the raw publication data. Or, you can check out the "Article Gathering Using APIs" code for the sources that offer their own API integration.


