---
title: "UT System Journal Database Combination"
author: "Alexander Harriman"
date: "2025-04-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning = FALSE}
library(readr)
library(RSQLite)
library(dplyr)
library(tidyverse)
library(data.table)
library(writexl)
```



```{r}
con <- dbConnect(SQLite(), "C:/Users/aharrima/OneDrive - University of Tennessee/Documents/SEC_and_Peer_Publications.db")
```



# Web of Science

```{r}
webOfScience <- dbGetQuery(con, 
                           "
                           SELECT *
                           FROM wos_pubs_peerinstitutions
                           ")

webOfScience
```



# Scopus


```{r}
scopus <- dbGetQuery(con,
                     "
                     SELECT *
                     FROM scopus_pubs_peerinstitutions
                     ")

scopus
```



# Dimensions


```{r}
dimensions <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM dimensions_pubs_peerinstitutions
                         ")

dimensions
```



# OpenAlex

```{r}
openAlexAuburn <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM openalex_pubs_auburn
                         ") |>
  select("id", "title", "display_name", "abstract", "doi", "publication_date", "publication_year", "cited_by_count", "type", "is_oa", "is_oa_anywhere", "oa_status", "any_repository_has_fulltext", "language", "source_display_name", "issn_l", "host_organization_name", "referenced_works_count", "first_page", "last_page", "volume", "issue", "fwci", "Subjects", "Authors", "Affiliations", "isFirstSchool", "isLastSchool", "isCorrespondingAuthor", "Publication Campus", "Publication Source", "Unified Publisher")

openAlexClemson <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM openalex_pubs_clemson
                         ") |>
  select("id", "title", "display_name", "abstract", "doi", "publication_date", "publication_year", "cited_by_count", "type", "is_oa", "is_oa_anywhere", "oa_status", "any_repository_has_fulltext", "language", "source_display_name", "issn_l", "host_organization_name", "referenced_works_count", "first_page", "last_page", "volume", "issue", "fwci", "Subjects", "Authors", "Affiliations", "isFirstSchool", "isLastSchool", "isCorrespondingAuthor", "Publication Campus", "Publication Source", "Unified Publisher")

openAlexColorado <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM openalex_pubs_colorado
                         ") |>
  select("id", "title", "display_name", "abstract", "doi", "publication_date", "publication_year", "cited_by_count", "type", "is_oa", "is_oa_anywhere", "oa_status", "any_repository_has_fulltext", "language", "source_display_name", "issn_l", "host_organization_name", "referenced_works_count", "first_page", "last_page", "volume", "issue", "fwci", "Subjects", "Authors", "Affiliations", "isFirstSchool", "isLastSchool", "isCorrespondingAuthor", "Publication Campus", "Publication Source", "Unified Publisher")

openAlexKentucky <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM openalex_pubs_kentucky
                         ") |>
  select("id", "title", "display_name", "abstract", "doi", "publication_date", "publication_year", "cited_by_count", "type", "is_oa", "is_oa_anywhere", "oa_status", "any_repository_has_fulltext", "language", "source_display_name", "issn_l", "host_organization_name", "referenced_works_count", "first_page", "last_page", "volume", "issue", "fwci", "Subjects", "Authors", "Affiliations", "isFirstSchool", "isLastSchool", "isCorrespondingAuthor", "Publication Campus", "Publication Source", "Unified Publisher")

openAlexIowaState <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM openalex_pubs_iowastate
                         ") |>
  select("id", "title", "display_name", "abstract", "doi", "publication_date", "publication_year", "cited_by_count", "type", "is_oa", "is_oa_anywhere", "oa_status", "any_repository_has_fulltext", "language", "source_display_name", "issn_l", "host_organization_name", "referenced_works_count", "first_page", "last_page", "volume", "issue", "fwci", "Subjects", "Authors", "Affiliations", "isFirstSchool", "isLastSchool", "isCorrespondingAuthor", "Publication Campus", "Publication Source", "Unified Publisher")

openAlexMissouri <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM openalex_pubs_missouri
                         ") |>
  select("id", "title", "display_name", "abstract", "doi", "publication_date", "publication_year", "cited_by_count", "type", "is_oa", "is_oa_anywhere", "oa_status", "any_repository_has_fulltext", "language", "source_display_name", "issn_l", "host_organization_name", "referenced_works_count", "first_page", "last_page", "volume", "issue", "fwci", "Subjects", "Authors", "Affiliations", "isFirstSchool", "isLastSchool", "isCorrespondingAuthor", "Publication Campus", "Publication Source", "Unified Publisher")

openAlexNebraska <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM openalex_pubs_nebraska
                         ") |>
  select("id", "title", "display_name", "abstract", "doi", "publication_date", "publication_year", "cited_by_count", "type", "is_oa", "is_oa_anywhere", "oa_status", "any_repository_has_fulltext", "language", "source_display_name", "issn_l", "host_organization_name", "referenced_works_count", "first_page", "last_page", "volume", "issue", "fwci", "Subjects", "Authors", "Affiliations", "isFirstSchool", "isLastSchool", "isCorrespondingAuthor", "Publication Campus", "Publication Source", "Unified Publisher")

openAlexOklahoma <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM openalex_pubs_oklahoma
                         ") |>
  select("id", "title", "display_name", "abstract", "doi", "publication_date", "publication_year", "cited_by_count", "type", "is_oa", "is_oa_anywhere", "oa_status", "any_repository_has_fulltext", "language", "source_display_name", "issn_l", "host_organization_name", "referenced_works_count", "first_page", "last_page", "volume", "issue", "fwci", "Subjects", "Authors", "Affiliations", "isFirstSchool", "isLastSchool", "isCorrespondingAuthor", "Publication Campus", "Publication Source", "Unified Publisher")

openAlexSC <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM openalex_pubs_southcarolina
                         ") |>
  select("id", "title", "display_name", "abstract", "doi", "publication_date", "publication_year", "cited_by_count", "type", "is_oa", "is_oa_anywhere", "oa_status", "any_repository_has_fulltext", "language", "source_display_name", "issn_l", "host_organization_name", "referenced_works_count", "first_page", "last_page", "volume", "issue", "fwci", "Subjects", "Authors", "Affiliations", "isFirstSchool", "isLastSchool", "isCorrespondingAuthor", "Publication Campus", "Publication Source", "Unified Publisher")

openAlexVT <- dbGetQuery(con,
                         "
                         SELECT *
                         FROM openalex_pubs_virginiatech
                         ") |>
  select("id", "title", "display_name", "abstract", "doi", "publication_date", "publication_year", "cited_by_count", "type", "is_oa", "is_oa_anywhere", "oa_status", "any_repository_has_fulltext", "language", "source_display_name", "issn_l", "host_organization_name", "referenced_works_count", "first_page", "last_page", "volume", "issue", "fwci", "Subjects", "Authors", "Affiliations", "isFirstSchool", "isLastSchool", "isCorrespondingAuthor", "Publication Campus", "Publication Source", "Unified Publisher")

openAlex <- rbind(openAlexAuburn, openAlexClemson, openAlexColorado, openAlexKentucky, openAlexIowaState, openAlexMissouri, openAlexNebraska, openAlexOklahoma, openAlexSC, openAlexVT)

#dbWriteTable(con, 'openalex_pubs_peerinstitutions', openAlex, overwrite = TRUE, row.names = FALSE)
```




# Auburn Publications

```{r, warning = FALSE}
auburnSmallA <- webOfScience |>
  filter(`Publication Campus` == 'Auburn University') |>
  select(`Publication Type`, Authors, `Source Title`, `Book Author Full Names`, `Article Title`, `Document Type`, Affiliations, ORCIDs, `Funding Orgs`, `Cited Reference Count`, `Times Cited, All Databases`, Publisher, ISSN, eISSN, ISBN, `Publication Date`, `Publication Year`, DOI, `DOI Link`, `Book DOI`, `WoS Categories`, `Research Areas`, `Pubmed Id`, `Open Access Designations`, `Highly Cited Status`, `Hot Paper Status`, `Publication Campus`, `Unified Publisher`, Resource, `Number of Pages`, `Reprint Addresses`)

auburnSmallB <- scopus |>
  filter(`Publication Campus` == 'Auburn University') |>
  select(Authors, Title, Year, DOI, `Source title`, Link, Affiliations, Publisher, Sponsors, ISSN, ISBN, `PubMed ID`, `Document Type`, `Publication Campus`, `Unified Publisher`, Resource, `Open Access`, `Page count`) |>
  mutate(`Page count` = as.numeric(`Page count`))

auburnSmallC <- dimensions |>
  filter(`Publication Campus` == 'Auburn University') |>
  select(DOI, ISBN, Title, Funding, Publisher, `Source title`, ISSN, `Publication date`, PubYear, `Open Access`, `Publication Type`, `Document Type`, Authors, `Corresponding Authors`, `Authors Affiliations`, Funder, `Times cited`, `Publication Campus`, `Unified Publisher`, PMID, Resource, `Units of Assessment`, `Funder Group`, Pagination, `Corresponding Authors`) |>
  mutate(`Page count` = ifelse(length(str_split(dimensions$Pagination[1], "-")[[1]]) != 2, NA, as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][2]) - as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][1])))

auburnSmallD <- openAlex |>
  filter(`Publication Campus` == 'Auburn University') |>
  mutate(`Page count` = ifelse(is.na(last_page) == TRUE | is.na(first_page) == TRUE, 0, as.numeric(last_page) - as.numeric(first_page)),
         doi = substring(doi, 17, length(doi)),
         PubMedID = NA,
         Funding = NA,
         ISBN = NA)
```


## Clean Up Columns

```{r}
auburnCleanA <- auburnSmallA |>
  select(DOI, `Article Title`, Resource, `Publication Year`, `Unified Publisher`, `Open Access Designations`, `Pubmed Id`, Authors, `Source Title`, `Document Type`, `Research Areas`, `Times Cited, All Databases`, Affiliations, ISSN, ISBN, `Number of Pages`, `Reprint Addresses`) |>
  mutate(`Source Title` = str_to_title(`Source Title`),
         `Number of Pages` = ifelse(is.na(`Number of Pages`) == TRUE, 0, `Number of Pages`))

auburnCleanB <- auburnSmallB |>
  select(DOI, Title, Resource, Year, `Unified Publisher`, `Open Access`, `PubMed ID`, Authors, `Source title`, `Document Type`, Affiliations, ISSN, ISBN, `Page count`) |>
  mutate(`Research Areas` = NA,
         `Times Cited` = 0,
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`),
         `Correspondence Address` = NA)

auburnCleanC <- auburnSmallC |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Units of Assessment`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`) |>
  mutate(`Research Areas` = substr(`Units of Assessment`, 5, nchar(`Units of Assessment`)),
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`)) |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Research Areas`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`)

auburnCleanD <- auburnSmallD |>
  select(doi, title, `Publication Source`, publication_year, `Unified Publisher`, oa_status, PubMedID, Authors, source_display_name, type, Subjects, cited_by_count, Affiliations, issn_l, ISBN, `Page count`, isCorrespondingAuthor) |>
  mutate(isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 'Yes', 'Auburn University', isCorrespondingAuthor))

colnames(auburnCleanA) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(auburnCleanC) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(auburnCleanD) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
```


## Row Bind the Tables

```{r}
auburnFull <- rbind(auburnCleanA, auburnCleanB, auburnCleanC, auburnCleanD)
```



## Clean Final Table

```{r}
auburnFinal <- auburnFull |>
  group_by(DOI) |>
  summarise(locationCount = length(unique(Resource)),
            locationA = Resource[1],
            locationB = ifelse(length(unique(Resource)) == 1, '', Resource[2]),
            locationC = ifelse(length(unique(Resource)) < 3, '', Resource[3]),
            locationD = ifelse(length(unique(Resource)) == 4, Resource[4], ''),
            pubYear = min(Year),
            `Unified Publisher` = `Unified Publisher`[1],
            OA1 = `Open Access`[1],
            OA2 = ifelse(length(unique(Resource)) == 1, '', `Open Access`[2]),
            OA3 = ifelse(length(unique(Resource)) < 3, '', `Open Access`[3]),
            OA4 = ifelse(length(unique(Resource)) == 4, `Open Access`[4], ''),
            PubMedID = ifelse(is.na(`PubMed ID`[1]) == FALSE, `PubMed ID`[1],
                              ifelse(is.na(`PubMed ID`[2]) == FALSE, `PubMed ID`[2],
                                           ifelse(is.na(`PubMed ID`[3]) == FALSE, `PubMed ID`[3], `PubMed ID`[4]))),
            Authors = ifelse(is.na(`Authors`[1]) == FALSE, Authors[1],
                              ifelse(is.na(Authors[2]) == FALSE, Authors[2],
                                           ifelse(is.na(Authors[3]) == FALSE, Authors[3], Authors[4]))),
            NumAuthors = ifelse(Resource[1] == 'OpenAlex', length(str_split(Authors[1], ',')[[1]]), length(str_split(Authors[1], ';')[[1]])),
            SourceTitleA = `Source title`[1],
            SourceTitleB = ifelse(length(unique(Resource)) == 1, '', `Source title`[2]),
            SourceTitleC = ifelse(length(unique(Resource)) < 3, '', `Source title`[3]),
            SourceTitleD = ifelse(length(unique(Resource)) == 4, `Source title`[4], ''),
            DocumentType = `Document Type`[1],
            ResearchArea1 = `Research Areas`[1],
            ResearchArea2 = ifelse(length(unique(Resource)) == 1, '', `Research Areas`[2]),
            ResearchArea3 = ifelse(length(unique(Resource)) < 3, '', `Research Areas`[3]),
            ResearchArea4 = ifelse(length(unique(Resource)) == 4, `Research Areas`[4], ''),
            TimesCited = max(`Times Cited`, na.rm = TRUE),
            Affiliation1 = Affiliations[1],
            Affiliation2 = ifelse(length(unique(Resource)) == 1, '', Affiliations[2]),
            Affiliation3 = ifelse(length(unique(Resource)) < 3, '', Affiliations[3]),
            Affiliation4 = ifelse(length(unique(Resource)) == 4, Affiliations[4], ''),
            ISBN1 = ISBN[1],
            ISBN2 = ifelse(length(unique(Resource)) == 1, '', ISBN[2]),
            ISBN3 = ifelse(length(unique(Resource)) < 3, '', ISBN[3]),
            ISBN4 = ifelse(length(unique(Resource)) == 4, ISBN[4], ''),
            ISSN1 = ISSN[1],
            ISSN2 = ifelse(length(unique(Resource)) == 1, '', ISSN[2]),
            ISSN3 = ifelse(length(unique(Resource)) < 3, '', ISSN[3]),
            ISSN4 = ifelse(length(unique(Resource)) == 4, ISSN[4], ''),
            pageCount1 = `Page count`[1],
            pageCount2 = `Page count`[2],
            pageCount3 = `Page count`[3],
            pageCount4 = `Page count`[4],
            Title = Title[1],
            isCA1 = ifelse(grepl('Auburn', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | `Correspondence Address`[1] == 'Yes', 1, 0),
            isCA2 = ifelse(grepl('Auburn', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | `Correspondence Address`[2] == 'Yes', 1, 0),
            isCA3 = ifelse(grepl('Auburn', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | `Correspondence Address`[3] == 'Yes', 1, 0),
            isCA4 = ifelse(grepl('Auburn', `Correspondence Address`[4], ignore.case = TRUE) == TRUE | `Correspondence Address`[4] == 'Yes', 1, 0)) |>
  mutate(isCA1 = ifelse(is.na(isCA1) == TRUE, 0, isCA1),
         isCA2 = ifelse(is.na(isCA2) == TRUE, 0, isCA2),
         isCA3 = ifelse(is.na(isCA3) == TRUE, 0, isCA3),
         isCA4 = ifelse(is.na(isCA4) == TRUE, 0, isCA4)) |>
  mutate(OpenAccess = case_when(
          OA4 == 'closed' | OA3 == 'Closed' | OA2 == 'Closed' | OA1 == 'Closed' ~ 'Closed',
          str_detect(OA4, 'diamond') | str_detect(OA3, 'diamond') | str_detect(OA2, 'diamond') | str_detect(OA1, 'diamond') ~ 'Diamond',
          str_detect(OA4, 'hybrid') | str_detect(OA3, 'Hybrid') | str_detect(OA2, 'Hybrid') | str_detect(OA1, 'Hybrid') | str_detect(OA1, 'hybrid') ~ 'Hybrid',
          str_detect(OA4, 'gold') | str_detect(OA3, 'Gold') | str_detect(OA2, 'Gold') | str_detect(OA1, 'Gold') | str_detect(OA1, 'gold')  ~ 'Gold',
          str_detect(OA4, 'bronze') | str_detect(OA3, 'Bronze') | str_detect(OA2, 'Bronze') | str_detect(OA1, 'Bronze') ~ 'Bronze',
          str_detect(OA4, 'green') | str_detect(OA3, 'Green') | str_detect(OA2, 'Green') | str_detect(OA1, 'Green') ~ 'Green',
          .default = 'Not Given'
        ),
        pageCount = pmax(pageCount1, pageCount2, pageCount3, pageCount4, na.rm = TRUE),
        SourceTitle = case_when(
          SourceTitleD != '' ~ SourceTitleD,
          SourceTitleC != '' ~ SourceTitleC,
          SourceTitleB != '' ~ SourceTitleB,
          SourceTitleA != '' ~ SourceTitleA,
          .default = 'Not Given'
        ),
        ResearchArea = case_when(
          ResearchArea4 != '' ~ ResearchArea4,
          ResearchArea3 != '' ~ ResearchArea3,
          ResearchArea2 != '' ~ ResearchArea2,
          ResearchArea1 != '' ~ ResearchArea1,
          .default = 'Not Given'
        ),
        Affiliation = case_when(
          Affiliation4 != '' ~ Affiliation4,
          Affiliation3 != '' ~ Affiliation3,
          Affiliation2 != '' ~ Affiliation2,
          Affiliation1 != '' ~ Affiliation1,
          .default = 'Not Given'
        ),
        ISSN = case_when(
          ISSN4 != '' ~ ISSN4,
          ISSN3 != '' ~ ISSN3,
          ISSN2 != '' ~ ISSN2,
          ISSN1 != '' ~ ISSN1,
          .default = 'Not Given'
        ),
        ISBN = case_when(
          ISBN4 != '' ~ ISBN4,
          ISBN3 != '' ~ ISBN3,
          ISBN2 != '' ~ ISBN2,
          ISBN1 != '' ~ ISBN1,
          .default = 'Not Given'
        ),
        isCorrespondingAuthor = ifelse(isCA1 == 1 | isCA2 == 1 | isCA3 == 1 | isCA4 == 1, 1, 0),
        Databases = paste0(locationA, ', ', locationB, ', ', locationC, ', ', locationD)) |>
  mutate(Databases = str_replace(Databases, ",,", ",")) |>
  mutate(Databases = str_replace(Databases, " ,", ",")) |>
  mutate(Databases = str_replace(Databases, ",,", "")) |>
  mutate(Databases = ifelse(
    substr(Databases, nchar(Databases) - 1, nchar(Databases)) == ', ', substr(Databases, 1, nchar(Databases) - 2), Databases
  )) |>
  mutate(`Unified Document Type` = case_when(
    DocumentType %in% c('Review', 'Review Article', 'Book Review', 'Review; Book Chapter', 'Review; Early Access', 'Art Exhibit Review', 'Music Performance Review', 'Theater Review', 'Book Review; Early Access', 'Film Review', 'Art Exhibit Review', 'Book Review; Book Chapter', 'Database Review', 'review', 'peer-review') ~ 'Review',
    DocumentType %in% c('Article', 'Research Article', 'Article; Early Access', 'Article; Data Paper', 'Article; Publication with Expression of Concern', 'Article in press', 'article', 'preprint', 'report', 'dissertation') ~ 'Article',
    DocumentType %in% c('Book', 'Book chapter', 'Article; Book Chapter', 'Fiction, Creative Prose', 'Biographical-Item; Book Chapter', 'book-chapter', 'book') ~ 'Book',
    DocumentType %in% c('Letter', 'Letter To Editor', 'Letter to Editor', 'Editorial', 'Editorial Material', 'Editorial Material; Early Access', 'Editorial Material; Book Chapter', 'Letter; Early Access', 'editorial', 'letter') ~ 'Editorial Material',
    DocumentType %in% c('Correction', 'Correction; Book Chapter', 'Correction Erratum', 'Correction; Early Access') ~ 'Correction',
    DocumentType %in% c('Conference paper', 'Proceedings Paper', 'Article; Proceedings Paper') ~ 'Proceedings Paper',
    DocumentType %in% c('Conference Abstract', 'Meeting Abstract') ~ 'Abstract',
    .default = 'Other'
  )) |>
  mutate(ResearchArea = sapply(ResearchArea, function(x) paste(unique(unlist(str_split(x," , "))), collapse = ", "))) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor) |>
  mutate(`Publication Campus` = 'Auburn University')



for (i in 1:dim(auburnFinal)[1]){

  stringSplit = ifelse(
    length(str_split(auburnFinal$Affiliation[i], ' , ')[[1]]) > 1, str_split(auburnFinal$Affiliation[i], ' , ')[[1]], str_split(auburnFinal$Affiliation[i], ';')[[1]]
  )

  auburnFinal$isFirstAuthor[i] = ifelse(grepl('Auburn', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
  auburnFinal$isLastAuthor[i] = ifelse(grepl('Auburn', stringSplit[length(stringSplit)], fixed = TRUE) == TRUE , 1, 0)
}



auburnFinal
```




## Export to the Database


```{r}
dbWriteTable(con, name = 'full_pubs_auburn', value = auburnFinal, append = FALSE, overwrite = TRUE)
```








# Clemson Publications

```{r, warning = FALSE}
clemsonSmallA <- webOfScience |>
  filter(`Publication Campus` == 'Clemson University') |>
  select(`Publication Type`, Authors, `Source Title`, `Book Author Full Names`, `Article Title`, `Document Type`, Affiliations, ORCIDs, `Funding Orgs`, `Cited Reference Count`, `Times Cited, All Databases`, Publisher, ISSN, eISSN, ISBN, `Publication Date`, `Publication Year`, DOI, `DOI Link`, `Book DOI`, `WoS Categories`, `Research Areas`, `Pubmed Id`, `Open Access Designations`, `Highly Cited Status`, `Hot Paper Status`, `Publication Campus`, `Unified Publisher`, Resource, `Number of Pages`, `Reprint Addresses`)

clemsonSmallB <- scopus |>
  filter(`Publication Campus` == 'Clemson University') |>
  select(Authors, Title, Year, DOI, `Source title`, Link, Affiliations, Publisher, Sponsors, ISSN, ISBN, `PubMed ID`, `Document Type`, `Publication Campus`, `Unified Publisher`, Resource, `Open Access`, `Page count`) |>
  mutate(`Page count` = as.numeric(`Page count`))

clemsonSmallC <- dimensions |>
  filter(`Publication Campus` == 'Clemson University') |>
  select(DOI, ISBN, Title, Funding, Publisher, `Source title`, ISSN, `Publication date`, PubYear, `Open Access`, `Publication Type`, `Document Type`, Authors, `Corresponding Authors`, `Authors Affiliations`, Funder, `Times cited`, `Publication Campus`, `Unified Publisher`, PMID, Resource, `Units of Assessment`, `Funder Group`, Pagination, `Corresponding Authors`) |>
  mutate(`Page count` = ifelse(length(str_split(dimensions$Pagination[1], "-")[[1]]) != 2, NA, as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][2]) - as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][1])))

clemsonSmallD <- openAlex |>
  filter(`Publication Campus` == 'Clemson University') |>
  mutate(`Page count` = ifelse(is.na(last_page) == TRUE | is.na(first_page) == TRUE, 0, as.numeric(last_page) - as.numeric(first_page)),
         doi = substring(doi, 17, length(doi)),
         PubMedID = NA,
         Funding = NA,
         ISBN = NA)
```


## Clean Up Columns

```{r}
clemsonCleanA <- clemsonSmallA |>
  select(DOI, `Article Title`, Resource, `Publication Year`, `Unified Publisher`, `Open Access Designations`, `Pubmed Id`, Authors, `Source Title`, `Document Type`, `Research Areas`, `Times Cited, All Databases`, Affiliations, ISSN, ISBN, `Number of Pages`, `Reprint Addresses`) |>
  mutate(`Source Title` = str_to_title(`Source Title`),
         `Number of Pages` = ifelse(is.na(`Number of Pages`) == TRUE, 0, `Number of Pages`))

clemsonCleanB <- clemsonSmallB |>
  select(DOI, Title, Resource, Year, `Unified Publisher`, `Open Access`, `PubMed ID`, Authors, `Source title`, `Document Type`, Affiliations, ISSN, ISBN, `Page count`) |>
  mutate(`Research Areas` = NA,
         `Times Cited` = 0,
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`),
         `Correspondence Address` = NA)

clemsonCleanC <- clemsonSmallC |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Units of Assessment`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`) |>
  mutate(`Research Areas` = substr(`Units of Assessment`, 5, nchar(`Units of Assessment`)),
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`)) |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Research Areas`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`)

clemsonCleanD <- clemsonSmallD |>
  select(doi, title, `Publication Source`, publication_year, `Unified Publisher`, oa_status, PubMedID, Authors, source_display_name, type, Subjects, cited_by_count, Affiliations, issn_l, ISBN, `Page count`, isCorrespondingAuthor) |>
  mutate(isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 'Yes', 'Clemson University', isCorrespondingAuthor))

colnames(clemsonCleanA) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(clemsonCleanC) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(clemsonCleanD) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
```


## Row Bind the Tables

```{r}
clemsonFull <- rbind(clemsonCleanA, clemsonCleanB, clemsonCleanC, clemsonCleanD)
```



## Clean Final Table

```{r}
clemsonFinal <- clemsonFull |>
  group_by(DOI) |>
  summarise(locationCount = length(unique(Resource)),
            locationA = Resource[1],
            locationB = ifelse(length(unique(Resource)) == 1, '', Resource[2]),
            locationC = ifelse(length(unique(Resource)) < 3, '', Resource[3]),
            locationD = ifelse(length(unique(Resource)) == 4, Resource[4], ''),
            pubYear = min(Year),
            `Unified Publisher` = `Unified Publisher`[1],
            OA1 = `Open Access`[1],
            OA2 = ifelse(length(unique(Resource)) == 1, '', `Open Access`[2]),
            OA3 = ifelse(length(unique(Resource)) < 3, '', `Open Access`[3]),
            OA4 = ifelse(length(unique(Resource)) == 4, `Open Access`[4], ''),
            PubMedID = ifelse(is.na(`PubMed ID`[1]) == FALSE, `PubMed ID`[1],
                              ifelse(is.na(`PubMed ID`[2]) == FALSE, `PubMed ID`[2],
                                           ifelse(is.na(`PubMed ID`[3]) == FALSE, `PubMed ID`[3], `PubMed ID`[4]))),
            Authors = ifelse(is.na(`Authors`[1]) == FALSE, Authors[1],
                              ifelse(is.na(Authors[2]) == FALSE, Authors[2],
                                           ifelse(is.na(Authors[3]) == FALSE, Authors[3], Authors[4]))),
            NumAuthors = ifelse(Resource[1] == 'OpenAlex', length(str_split(Authors[1], ',')[[1]]), length(str_split(Authors[1], ';')[[1]])),
            SourceTitleA = `Source title`[1],
            SourceTitleB = ifelse(length(unique(Resource)) == 1, '', `Source title`[2]),
            SourceTitleC = ifelse(length(unique(Resource)) < 3, '', `Source title`[3]),
            SourceTitleD = ifelse(length(unique(Resource)) == 4, `Source title`[4], ''),
            DocumentType = `Document Type`[1],
            ResearchArea1 = `Research Areas`[1],
            ResearchArea2 = ifelse(length(unique(Resource)) == 1, '', `Research Areas`[2]),
            ResearchArea3 = ifelse(length(unique(Resource)) < 3, '', `Research Areas`[3]),
            ResearchArea4 = ifelse(length(unique(Resource)) == 4, `Research Areas`[4], ''),
            TimesCited = max(`Times Cited`, na.rm = TRUE),
            Affiliation1 = Affiliations[1],
            Affiliation2 = ifelse(length(unique(Resource)) == 1, '', Affiliations[2]),
            Affiliation3 = ifelse(length(unique(Resource)) < 3, '', Affiliations[3]),
            Affiliation4 = ifelse(length(unique(Resource)) == 4, Affiliations[4], ''),
            ISBN1 = ISBN[1],
            ISBN2 = ifelse(length(unique(Resource)) == 1, '', ISBN[2]),
            ISBN3 = ifelse(length(unique(Resource)) < 3, '', ISBN[3]),
            ISBN4 = ifelse(length(unique(Resource)) == 4, ISBN[4], ''),
            ISSN1 = ISSN[1],
            ISSN2 = ifelse(length(unique(Resource)) == 1, '', ISSN[2]),
            ISSN3 = ifelse(length(unique(Resource)) < 3, '', ISSN[3]),
            ISSN4 = ifelse(length(unique(Resource)) == 4, ISSN[4], ''),
            pageCount1 = `Page count`[1],
            pageCount2 = `Page count`[2],
            pageCount3 = `Page count`[3],
            pageCount4 = `Page count`[4],
            Title = Title[1],
            isCA1 = ifelse(grepl('Clemson', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | `Correspondence Address`[1] == 'Yes', 1, 0),
            isCA2 = ifelse(grepl('Clemson', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | `Correspondence Address`[2] == 'Yes', 1, 0),
            isCA3 = ifelse(grepl('Clemson', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | `Correspondence Address`[3] == 'Yes', 1, 0),
            isCA4 = ifelse(grepl('Clemson', `Correspondence Address`[4], ignore.case = TRUE) == TRUE | `Correspondence Address`[4] == 'Yes', 1, 0)) |>
  mutate(isCA1 = ifelse(is.na(isCA1) == TRUE, 0, isCA1),
         isCA2 = ifelse(is.na(isCA2) == TRUE, 0, isCA2),
         isCA3 = ifelse(is.na(isCA3) == TRUE, 0, isCA3),
         isCA4 = ifelse(is.na(isCA4) == TRUE, 0, isCA4)) |>
  mutate(OpenAccess = case_when(
          OA4 == 'closed' | OA3 == 'Closed' | OA2 == 'Closed' | OA1 == 'Closed' ~ 'Closed',
          str_detect(OA4, 'diamond') | str_detect(OA3, 'diamond') | str_detect(OA2, 'diamond') | str_detect(OA1, 'diamond') ~ 'Diamond',
          str_detect(OA4, 'hybrid') | str_detect(OA3, 'Hybrid') | str_detect(OA2, 'Hybrid') | str_detect(OA1, 'Hybrid') | str_detect(OA1, 'hybrid') ~ 'Hybrid',
          str_detect(OA4, 'gold') | str_detect(OA3, 'Gold') | str_detect(OA2, 'Gold') | str_detect(OA1, 'Gold') | str_detect(OA1, 'gold')  ~ 'Gold',
          str_detect(OA4, 'bronze') | str_detect(OA3, 'Bronze') | str_detect(OA2, 'Bronze') | str_detect(OA1, 'Bronze') ~ 'Bronze',
          str_detect(OA4, 'green') | str_detect(OA3, 'Green') | str_detect(OA2, 'Green') | str_detect(OA1, 'Green') ~ 'Green',
          .default = 'Not Given'
        ),
        pageCount = pmax(pageCount1, pageCount2, pageCount3, pageCount4, na.rm = TRUE),
        SourceTitle = case_when(
          SourceTitleD != '' ~ SourceTitleD,
          SourceTitleC != '' ~ SourceTitleC,
          SourceTitleB != '' ~ SourceTitleB,
          SourceTitleA != '' ~ SourceTitleA,
          .default = 'Not Given'
        ),
        ResearchArea = case_when(
          ResearchArea4 != '' ~ ResearchArea4,
          ResearchArea3 != '' ~ ResearchArea3,
          ResearchArea2 != '' ~ ResearchArea2,
          ResearchArea1 != '' ~ ResearchArea1,
          .default = 'Not Given'
        ),
        Affiliation = case_when(
          Affiliation4 != '' ~ Affiliation4,
          Affiliation3 != '' ~ Affiliation3,
          Affiliation2 != '' ~ Affiliation2,
          Affiliation1 != '' ~ Affiliation1,
          .default = 'Not Given'
        ),
        ISSN = case_when(
          ISSN4 != '' ~ ISSN4,
          ISSN3 != '' ~ ISSN3,
          ISSN2 != '' ~ ISSN2,
          ISSN1 != '' ~ ISSN1,
          .default = 'Not Given'
        ),
        ISBN = case_when(
          ISBN4 != '' ~ ISBN4,
          ISBN3 != '' ~ ISBN3,
          ISBN2 != '' ~ ISBN2,
          ISBN1 != '' ~ ISBN1,
          .default = 'Not Given'
        ),
        isCorrespondingAuthor = ifelse(isCA1 == 1 | isCA2 == 1 | isCA3 == 1 | isCA4 == 1, 1, 0),
        Databases = paste0(locationA, ', ', locationB, ', ', locationC, ', ', locationD)) |>
  mutate(Databases = str_replace(Databases, ",,", ",")) |>
  mutate(Databases = str_replace(Databases, " ,", ",")) |>
  mutate(Databases = str_replace(Databases, ",,", "")) |>
  mutate(Databases = ifelse(
    substr(Databases, nchar(Databases) - 1, nchar(Databases)) == ', ', substr(Databases, 1, nchar(Databases) - 2), Databases
  )) |>
  mutate(`Unified Document Type` = case_when(
    DocumentType %in% c('Review', 'Review Article', 'Book Review', 'Review; Book Chapter', 'Review; Early Access', 'Art Exhibit Review', 'Music Performance Review', 'Theater Review', 'Book Review; Early Access', 'Film Review', 'Art Exhibit Review', 'Book Review; Book Chapter', 'Database Review', 'review', 'peer-review') ~ 'Review',
    DocumentType %in% c('Article', 'Research Article', 'Article; Early Access', 'Article; Data Paper', 'Article; Publication with Expression of Concern', 'Article in press', 'article', 'preprint', 'report', 'dissertation') ~ 'Article',
    DocumentType %in% c('Book', 'Book chapter', 'Article; Book Chapter', 'Fiction, Creative Prose', 'Biographical-Item; Book Chapter', 'book-chapter', 'book') ~ 'Book',
    DocumentType %in% c('Letter', 'Letter To Editor', 'Letter to Editor', 'Editorial', 'Editorial Material', 'Editorial Material; Early Access', 'Editorial Material; Book Chapter', 'Letter; Early Access', 'editorial', 'letter') ~ 'Editorial Material',
    DocumentType %in% c('Correction', 'Correction; Book Chapter', 'Correction Erratum', 'Correction; Early Access') ~ 'Correction',
    DocumentType %in% c('Conference paper', 'Proceedings Paper', 'Article; Proceedings Paper') ~ 'Proceedings Paper',
    DocumentType %in% c('Conference Abstract', 'Meeting Abstract') ~ 'Abstract',
    .default = 'Other'
  )) |>
  mutate(ResearchArea = sapply(ResearchArea, function(x) paste(unique(unlist(str_split(x," , "))), collapse = ", "))) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor) |>
  mutate(`Publication Campus` = 'Clemson University')



for (i in 1:dim(clemsonFinal)[1]){

  stringSplit = ifelse(
    length(str_split(clemsonFinal$Affiliation[i], ' , ')[[1]]) > 1, str_split(clemsonFinal$Affiliation[i], ' , ')[[1]], str_split(clemsonFinal$Affiliation[i], ';')[[1]]
  )

  clemsonFinal$isFirstAuthor[i] = ifelse(grepl('Clemson', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
  clemsonFinal$isLastAuthor[i] = ifelse(grepl('Clemson', stringSplit[length(stringSplit)], fixed = TRUE) == TRUE , 1, 0)
}


clemsonFinal
```




## Export to the Database


```{r}
dbWriteTable(con, name = 'full_pubs_clemson', value = clemsonFinal, append = FALSE, overwrite = TRUE)
```














# Iowa State Publications

```{r, warning = FALSE}
iowaStateSmallA <- webOfScience |>
  filter(`Publication Campus` == 'Iowa State') |>
  select(`Publication Type`, Authors, `Source Title`, `Book Author Full Names`, `Article Title`, `Document Type`, Affiliations, ORCIDs, `Funding Orgs`, `Cited Reference Count`, `Times Cited, All Databases`, Publisher, ISSN, eISSN, ISBN, `Publication Date`, `Publication Year`, DOI, `DOI Link`, `Book DOI`, `WoS Categories`, `Research Areas`, `Pubmed Id`, `Open Access Designations`, `Highly Cited Status`, `Hot Paper Status`, `Publication Campus`, `Unified Publisher`, Resource, `Number of Pages`, `Reprint Addresses`)

iowaStateSmallB <- scopus |>
  filter(`Publication Campus` == 'Iowa State') |>
  select(Authors, Title, Year, DOI, `Source title`, Link, Affiliations, Publisher, Sponsors, ISSN, ISBN, `PubMed ID`, `Document Type`, `Publication Campus`, `Unified Publisher`, Resource, `Open Access`, `Page count`) |>
  mutate(`Page count` = as.numeric(`Page count`))

iowaStateSmallC <- dimensions |>
  filter(`Publication Campus` == 'Iowa State') |>
  select(DOI, ISBN, Title, Funding, Publisher, `Source title`, ISSN, `Publication date`, PubYear, `Open Access`, `Publication Type`, `Document Type`, Authors, `Corresponding Authors`, `Authors Affiliations`, Funder, `Times cited`, `Publication Campus`, `Unified Publisher`, PMID, Resource, `Units of Assessment`, `Funder Group`, Pagination, `Corresponding Authors`) |>
  mutate(`Page count` = ifelse(length(str_split(dimensions$Pagination[1], "-")[[1]]) != 2, NA, as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][2]) - as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][1])))

iowaStateSmallD <- openAlex |>
  filter(`Publication Campus` == 'Iowa State') |>
  mutate(`Page count` = ifelse(is.na(last_page) == TRUE | is.na(first_page) == TRUE, 0, as.numeric(last_page) - as.numeric(first_page)),
         doi = substring(doi, 17, length(doi)),
         PubMedID = NA,
         Funding = NA,
         ISBN = NA)
```


## Clean Up Columns

```{r}
iowaStateCleanA <- iowaStateSmallA |>
  select(DOI, `Article Title`, Resource, `Publication Year`, `Unified Publisher`, `Open Access Designations`, `Pubmed Id`, Authors, `Source Title`, `Document Type`, `Research Areas`, `Times Cited, All Databases`, Affiliations, ISSN, ISBN, `Number of Pages`, `Reprint Addresses`) |>
  mutate(`Source Title` = str_to_title(`Source Title`),
         `Number of Pages` = ifelse(is.na(`Number of Pages`) == TRUE, 0, `Number of Pages`))

iowaStateCleanB <- iowaStateSmallB |>
  select(DOI, Title, Resource, Year, `Unified Publisher`, `Open Access`, `PubMed ID`, Authors, `Source title`, `Document Type`, Affiliations, ISSN, ISBN, `Page count`) |>
  mutate(`Research Areas` = NA,
         `Times Cited` = 0,
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`),
         `Correspondence Address` = NA)

iowaStateCleanC <- iowaStateSmallC |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Units of Assessment`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`) |>
  mutate(`Research Areas` = substr(`Units of Assessment`, 5, nchar(`Units of Assessment`)),
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`)) |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Research Areas`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`)

iowaStateCleanD <- iowaStateSmallD |>
  select(doi, title, `Publication Source`, publication_year, `Unified Publisher`, oa_status, PubMedID, Authors, source_display_name, type, Subjects, cited_by_count, Affiliations, issn_l, ISBN, `Page count`, isCorrespondingAuthor) |>
  mutate(isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 'Yes', 'Iowa State', isCorrespondingAuthor))

colnames(iowaStateCleanA) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(iowaStateCleanC) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(iowaStateCleanD) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
```


## Row Bind the Tables

```{r}
iowaStateFull <- rbind(iowaStateCleanA, iowaStateCleanB, iowaStateCleanC, iowaStateCleanD)
```



## Clean Final Table

```{r}
iowaStateFinal <- iowaStateFull |>
  group_by(DOI) |>
  summarise(locationCount = length(unique(Resource)),
            locationA = Resource[1],
            locationB = ifelse(length(unique(Resource)) == 1, '', Resource[2]),
            locationC = ifelse(length(unique(Resource)) < 3, '', Resource[3]),
            locationD = ifelse(length(unique(Resource)) == 4, Resource[4], ''),
            pubYear = min(Year),
            `Unified Publisher` = `Unified Publisher`[1],
            OA1 = `Open Access`[1],
            OA2 = ifelse(length(unique(Resource)) == 1, '', `Open Access`[2]),
            OA3 = ifelse(length(unique(Resource)) < 3, '', `Open Access`[3]),
            OA4 = ifelse(length(unique(Resource)) == 4, `Open Access`[4], ''),
            PubMedID = ifelse(is.na(`PubMed ID`[1]) == FALSE, `PubMed ID`[1],
                              ifelse(is.na(`PubMed ID`[2]) == FALSE, `PubMed ID`[2],
                                           ifelse(is.na(`PubMed ID`[3]) == FALSE, `PubMed ID`[3], `PubMed ID`[4]))),
            Authors = ifelse(is.na(`Authors`[1]) == FALSE, Authors[1],
                              ifelse(is.na(Authors[2]) == FALSE, Authors[2],
                                           ifelse(is.na(Authors[3]) == FALSE, Authors[3], Authors[4]))),
            NumAuthors = ifelse(Resource[1] == 'OpenAlex', length(str_split(Authors[1], ',')[[1]]), length(str_split(Authors[1], ';')[[1]])),
            SourceTitleA = `Source title`[1],
            SourceTitleB = ifelse(length(unique(Resource)) == 1, '', `Source title`[2]),
            SourceTitleC = ifelse(length(unique(Resource)) < 3, '', `Source title`[3]),
            SourceTitleD = ifelse(length(unique(Resource)) == 4, `Source title`[4], ''),
            DocumentType = `Document Type`[1],
            ResearchArea1 = `Research Areas`[1],
            ResearchArea2 = ifelse(length(unique(Resource)) == 1, '', `Research Areas`[2]),
            ResearchArea3 = ifelse(length(unique(Resource)) < 3, '', `Research Areas`[3]),
            ResearchArea4 = ifelse(length(unique(Resource)) == 4, `Research Areas`[4], ''),
            TimesCited = max(`Times Cited`, na.rm = TRUE),
            Affiliation1 = Affiliations[1],
            Affiliation2 = ifelse(length(unique(Resource)) == 1, '', Affiliations[2]),
            Affiliation3 = ifelse(length(unique(Resource)) < 3, '', Affiliations[3]),
            Affiliation4 = ifelse(length(unique(Resource)) == 4, Affiliations[4], ''),
            ISBN1 = ISBN[1],
            ISBN2 = ifelse(length(unique(Resource)) == 1, '', ISBN[2]),
            ISBN3 = ifelse(length(unique(Resource)) < 3, '', ISBN[3]),
            ISBN4 = ifelse(length(unique(Resource)) == 4, ISBN[4], ''),
            ISSN1 = ISSN[1],
            ISSN2 = ifelse(length(unique(Resource)) == 1, '', ISSN[2]),
            ISSN3 = ifelse(length(unique(Resource)) < 3, '', ISSN[3]),
            ISSN4 = ifelse(length(unique(Resource)) == 4, ISSN[4], ''),
            pageCount1 = `Page count`[1],
            pageCount2 = `Page count`[2],
            pageCount3 = `Page count`[3],
            pageCount4 = `Page count`[4],
            Title = Title[1],
            isCA1 = ifelse(grepl('Iowa State', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | `Correspondence Address`[1] == 'Yes', 1, 0),
            isCA2 = ifelse(grepl('Iowa State', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | `Correspondence Address`[2] == 'Yes', 1, 0),
            isCA3 = ifelse(grepl('Iowa State', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | `Correspondence Address`[3] == 'Yes', 1, 0),
            isCA4 = ifelse(grepl('Iowa State', `Correspondence Address`[4], ignore.case = TRUE) == TRUE | `Correspondence Address`[4] == 'Yes', 1, 0)) |>
  mutate(isCA1 = ifelse(is.na(isCA1) == TRUE, 0, isCA1),
         isCA2 = ifelse(is.na(isCA2) == TRUE, 0, isCA2),
         isCA3 = ifelse(is.na(isCA3) == TRUE, 0, isCA3),
         isCA4 = ifelse(is.na(isCA4) == TRUE, 0, isCA4)) |>
  mutate(OpenAccess = case_when(
          OA4 == 'closed' | OA3 == 'Closed' | OA2 == 'Closed' | OA1 == 'Closed' ~ 'Closed',
          str_detect(OA4, 'diamond') | str_detect(OA3, 'diamond') | str_detect(OA2, 'diamond') | str_detect(OA1, 'diamond') ~ 'Diamond',
          str_detect(OA4, 'hybrid') | str_detect(OA3, 'Hybrid') | str_detect(OA2, 'Hybrid') | str_detect(OA1, 'Hybrid') | str_detect(OA1, 'hybrid') ~ 'Hybrid',
          str_detect(OA4, 'gold') | str_detect(OA3, 'Gold') | str_detect(OA2, 'Gold') | str_detect(OA1, 'Gold') | str_detect(OA1, 'gold')  ~ 'Gold',
          str_detect(OA4, 'bronze') | str_detect(OA3, 'Bronze') | str_detect(OA2, 'Bronze') | str_detect(OA1, 'Bronze') ~ 'Bronze',
          str_detect(OA4, 'green') | str_detect(OA3, 'Green') | str_detect(OA2, 'Green') | str_detect(OA1, 'Green') ~ 'Green',
          .default = 'Not Given'
        ),
        pageCount = pmax(pageCount1, pageCount2, pageCount3, pageCount4, na.rm = TRUE),
        SourceTitle = case_when(
          SourceTitleD != '' ~ SourceTitleD,
          SourceTitleC != '' ~ SourceTitleC,
          SourceTitleB != '' ~ SourceTitleB,
          SourceTitleA != '' ~ SourceTitleA,
          .default = 'Not Given'
        ),
        ResearchArea = case_when(
          ResearchArea4 != '' ~ ResearchArea4,
          ResearchArea3 != '' ~ ResearchArea3,
          ResearchArea2 != '' ~ ResearchArea2,
          ResearchArea1 != '' ~ ResearchArea1,
          .default = 'Not Given'
        ),
        Affiliation = case_when(
          Affiliation4 != '' ~ Affiliation4,
          Affiliation3 != '' ~ Affiliation3,
          Affiliation2 != '' ~ Affiliation2,
          Affiliation1 != '' ~ Affiliation1,
          .default = 'Not Given'
        ),
        ISSN = case_when(
          ISSN4 != '' ~ ISSN4,
          ISSN3 != '' ~ ISSN3,
          ISSN2 != '' ~ ISSN2,
          ISSN1 != '' ~ ISSN1,
          .default = 'Not Given'
        ),
        ISBN = case_when(
          ISBN4 != '' ~ ISBN4,
          ISBN3 != '' ~ ISBN3,
          ISBN2 != '' ~ ISBN2,
          ISBN1 != '' ~ ISBN1,
          .default = 'Not Given'
        ),
        isCorrespondingAuthor = ifelse(isCA1 == 1 | isCA2 == 1 | isCA3 == 1 | isCA4 == 1, 1, 0),
        Databases = paste0(locationA, ', ', locationB, ', ', locationC, ', ', locationD)) |>
  mutate(Databases = str_replace(Databases, ",,", ",")) |>
  mutate(Databases = str_replace(Databases, " ,", ",")) |>
  mutate(Databases = str_replace(Databases, ",,", "")) |>
  mutate(Databases = ifelse(
    substr(Databases, nchar(Databases) - 1, nchar(Databases)) == ', ', substr(Databases, 1, nchar(Databases) - 2), Databases
  )) |>
  mutate(`Unified Document Type` = case_when(
    DocumentType %in% c('Review', 'Review Article', 'Book Review', 'Review; Book Chapter', 'Review; Early Access', 'Art Exhibit Review', 'Music Performance Review', 'Theater Review', 'Book Review; Early Access', 'Film Review', 'Art Exhibit Review', 'Book Review; Book Chapter', 'Database Review', 'review', 'peer-review') ~ 'Review',
    DocumentType %in% c('Article', 'Research Article', 'Article; Early Access', 'Article; Data Paper', 'Article; Publication with Expression of Concern', 'Article in press', 'article', 'preprint', 'report', 'dissertation') ~ 'Article',
    DocumentType %in% c('Book', 'Book chapter', 'Article; Book Chapter', 'Fiction, Creative Prose', 'Biographical-Item; Book Chapter', 'book-chapter', 'book') ~ 'Book',
    DocumentType %in% c('Letter', 'Letter To Editor', 'Letter to Editor', 'Editorial', 'Editorial Material', 'Editorial Material; Early Access', 'Editorial Material; Book Chapter', 'Letter; Early Access', 'editorial', 'letter') ~ 'Editorial Material',
    DocumentType %in% c('Correction', 'Correction; Book Chapter', 'Correction Erratum', 'Correction; Early Access') ~ 'Correction',
    DocumentType %in% c('Conference paper', 'Proceedings Paper', 'Article; Proceedings Paper') ~ 'Proceedings Paper',
    DocumentType %in% c('Conference Abstract', 'Meeting Abstract') ~ 'Abstract',
    .default = 'Other'
  )) |>
  mutate(ResearchArea = sapply(ResearchArea, function(x) paste(unique(unlist(str_split(x," , "))), collapse = ", "))) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor) |>
  mutate(`Publication Campus` = 'Iowa State')



for (i in 1:dim(iowaStateFinal)[1]){

  stringSplit = ifelse(
    length(str_split(iowaStateFinal$Affiliation[i], ' , ')[[1]]) > 1, str_split(iowaStateFinal$Affiliation[i], ' , ')[[1]], str_split(iowaStateFinal$Affiliation[i], ';')[[1]]
  )

  iowaStateFinal$isFirstAuthor[i] = ifelse(grepl('Iowa State', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
  iowaStateFinal$isLastAuthor[i] = ifelse(grepl('Iowa State', stringSplit[length(stringSplit)], fixed = TRUE) == TRUE , 1, 0)
}


iowaStateFinal
```




## Export to the Database


```{r}
dbWriteTable(con, name = 'full_pubs_iowastate', value = iowaStateFinal, append = FALSE, overwrite = TRUE)
```













# Colorado Publications

```{r, warning = FALSE}
coloradoSmallA <- webOfScience |>
  filter(`Publication Campus` == 'University of Colorado') |>
  select(`Publication Type`, Authors, `Source Title`, `Book Author Full Names`, `Article Title`, `Document Type`, Affiliations, ORCIDs, `Funding Orgs`, `Cited Reference Count`, `Times Cited, All Databases`, Publisher, ISSN, eISSN, ISBN, `Publication Date`, `Publication Year`, DOI, `DOI Link`, `Book DOI`, `WoS Categories`, `Research Areas`, `Pubmed Id`, `Open Access Designations`, `Highly Cited Status`, `Hot Paper Status`, `Publication Campus`, `Unified Publisher`, Resource, `Number of Pages`, `Reprint Addresses`)

coloradoSmallB <- scopus |>
  filter(`Publication Campus` == 'University of Colorado') |>
  select(Authors, Title, Year, DOI, `Source title`, Link, Affiliations, Publisher, Sponsors, ISSN, ISBN, `PubMed ID`, `Document Type`, `Publication Campus`, `Unified Publisher`, Resource, `Open Access`, `Page count`) |>
  mutate(`Page count` = as.numeric(`Page count`))

coloradoSmallC <- dimensions |>
  filter(`Publication Campus` == 'University of Colorado') |>
  select(DOI, ISBN, Title, Funding, Publisher, `Source title`, ISSN, `Publication date`, PubYear, `Open Access`, `Publication Type`, `Document Type`, Authors, `Corresponding Authors`, `Authors Affiliations`, Funder, `Times cited`, `Publication Campus`, `Unified Publisher`, PMID, Resource, `Units of Assessment`, `Funder Group`, Pagination, `Corresponding Authors`) |>
  mutate(`Page count` = ifelse(length(str_split(dimensions$Pagination[1], "-")[[1]]) != 2, NA, as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][2]) - as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][1])))

coloradoSmallD <- openAlex |>
  filter(`Publication Campus` == 'University of Colorado') |>
  mutate(`Page count` = ifelse(is.na(last_page) == TRUE | is.na(first_page) == TRUE, 0, as.numeric(last_page) - as.numeric(first_page)),
         doi = substring(doi, 17, length(doi)),
         PubMedID = NA,
         Funding = NA,
         ISBN = NA)
```


## Clean Up Columns

```{r}
coloradoCleanA <- coloradoSmallA |>
  select(DOI, `Article Title`, Resource, `Publication Year`, `Unified Publisher`, `Open Access Designations`, `Pubmed Id`, Authors, `Source Title`, `Document Type`, `Research Areas`, `Times Cited, All Databases`, Affiliations, ISSN, ISBN, `Number of Pages`, `Reprint Addresses`) |>
  mutate(`Source Title` = str_to_title(`Source Title`),
         `Number of Pages` = ifelse(is.na(`Number of Pages`) == TRUE, 0, `Number of Pages`))

coloradoCleanB <- coloradoSmallB |>
  select(DOI, Title, Resource, Year, `Unified Publisher`, `Open Access`, `PubMed ID`, Authors, `Source title`, `Document Type`, Affiliations, ISSN, ISBN, `Page count`) |>
  mutate(`Research Areas` = NA,
         `Times Cited` = 0,
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`),
         `Correspondence Address` = NA)

coloradoCleanC <- coloradoSmallC |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Units of Assessment`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`) |>
  mutate(`Research Areas` = substr(`Units of Assessment`, 5, nchar(`Units of Assessment`)),
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`)) |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Research Areas`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`)

coloradoCleanD <- coloradoSmallD |>
  select(doi, title, `Publication Source`, publication_year, `Unified Publisher`, oa_status, PubMedID, Authors, source_display_name, type, Subjects, cited_by_count, Affiliations, issn_l, ISBN, `Page count`, isCorrespondingAuthor) |>
  mutate(isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 'Yes', 'University of Colorado', isCorrespondingAuthor))

colnames(coloradoCleanA) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(coloradoCleanC) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(coloradoCleanD) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
```


## Row Bind the Tables

```{r}
coloradoFull <- rbind(coloradoCleanA, coloradoCleanB, coloradoCleanC, coloradoCleanD)
```



## Clean Final Table

```{r}
coloradoFinal <- coloradoFull |>
  group_by(DOI) |>
  summarise(locationCount = length(unique(Resource)),
            locationA = Resource[1],
            locationB = ifelse(length(unique(Resource)) == 1, '', Resource[2]),
            locationC = ifelse(length(unique(Resource)) < 3, '', Resource[3]),
            locationD = ifelse(length(unique(Resource)) == 4, Resource[4], ''),
            pubYear = min(Year),
            `Unified Publisher` = `Unified Publisher`[1],
            OA1 = `Open Access`[1],
            OA2 = ifelse(length(unique(Resource)) == 1, '', `Open Access`[2]),
            OA3 = ifelse(length(unique(Resource)) < 3, '', `Open Access`[3]),
            OA4 = ifelse(length(unique(Resource)) == 4, `Open Access`[4], ''),
            PubMedID = ifelse(is.na(`PubMed ID`[1]) == FALSE, `PubMed ID`[1],
                              ifelse(is.na(`PubMed ID`[2]) == FALSE, `PubMed ID`[2],
                                           ifelse(is.na(`PubMed ID`[3]) == FALSE, `PubMed ID`[3], `PubMed ID`[4]))),
            Authors = ifelse(is.na(`Authors`[1]) == FALSE, Authors[1],
                              ifelse(is.na(Authors[2]) == FALSE, Authors[2],
                                           ifelse(is.na(Authors[3]) == FALSE, Authors[3], Authors[4]))),
            NumAuthors = ifelse(Resource[1] == 'OpenAlex', length(str_split(Authors[1], ',')[[1]]), length(str_split(Authors[1], ';')[[1]])),
            SourceTitleA = `Source title`[1],
            SourceTitleB = ifelse(length(unique(Resource)) == 1, '', `Source title`[2]),
            SourceTitleC = ifelse(length(unique(Resource)) < 3, '', `Source title`[3]),
            SourceTitleD = ifelse(length(unique(Resource)) == 4, `Source title`[4], ''),
            DocumentType = `Document Type`[1],
            ResearchArea1 = `Research Areas`[1],
            ResearchArea2 = ifelse(length(unique(Resource)) == 1, '', `Research Areas`[2]),
            ResearchArea3 = ifelse(length(unique(Resource)) < 3, '', `Research Areas`[3]),
            ResearchArea4 = ifelse(length(unique(Resource)) == 4, `Research Areas`[4], ''),
            TimesCited = max(`Times Cited`, na.rm = TRUE),
            Affiliation1 = Affiliations[1],
            Affiliation2 = ifelse(length(unique(Resource)) == 1, '', Affiliations[2]),
            Affiliation3 = ifelse(length(unique(Resource)) < 3, '', Affiliations[3]),
            Affiliation4 = ifelse(length(unique(Resource)) == 4, Affiliations[4], ''),
            ISBN1 = ISBN[1],
            ISBN2 = ifelse(length(unique(Resource)) == 1, '', ISBN[2]),
            ISBN3 = ifelse(length(unique(Resource)) < 3, '', ISBN[3]),
            ISBN4 = ifelse(length(unique(Resource)) == 4, ISBN[4], ''),
            ISSN1 = ISSN[1],
            ISSN2 = ifelse(length(unique(Resource)) == 1, '', ISSN[2]),
            ISSN3 = ifelse(length(unique(Resource)) < 3, '', ISSN[3]),
            ISSN4 = ifelse(length(unique(Resource)) == 4, ISSN[4], ''),
            pageCount1 = `Page count`[1],
            pageCount2 = `Page count`[2],
            pageCount3 = `Page count`[3],
            pageCount4 = `Page count`[4],
            Title = Title[1],
            isCA1 = ifelse(grepl('Boulder', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | `Correspondence Address`[1] == 'Yes', 1, 0),
            isCA2 = ifelse(grepl('Boulder', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | `Correspondence Address`[2] == 'Yes', 1, 0),
            isCA3 = ifelse(grepl('Boulder', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | `Correspondence Address`[3] == 'Yes', 1, 0),
            isCA4 = ifelse(grepl('Boulder', `Correspondence Address`[4], ignore.case = TRUE) == TRUE | `Correspondence Address`[4] == 'Yes', 1, 0)) |>
  mutate(isCA1 = ifelse(is.na(isCA1) == TRUE, 0, isCA1),
         isCA2 = ifelse(is.na(isCA2) == TRUE, 0, isCA2),
         isCA3 = ifelse(is.na(isCA3) == TRUE, 0, isCA3),
         isCA4 = ifelse(is.na(isCA4) == TRUE, 0, isCA4)) |>
  mutate(OpenAccess = case_when(
          OA4 == 'closed' | OA3 == 'Closed' | OA2 == 'Closed' | OA1 == 'Closed' ~ 'Closed',
          str_detect(OA4, 'diamond') | str_detect(OA3, 'diamond') | str_detect(OA2, 'diamond') | str_detect(OA1, 'diamond') ~ 'Diamond',
          str_detect(OA4, 'hybrid') | str_detect(OA3, 'Hybrid') | str_detect(OA2, 'Hybrid') | str_detect(OA1, 'Hybrid') | str_detect(OA1, 'hybrid') ~ 'Hybrid',
          str_detect(OA4, 'gold') | str_detect(OA3, 'Gold') | str_detect(OA2, 'Gold') | str_detect(OA1, 'Gold') | str_detect(OA1, 'gold')  ~ 'Gold',
          str_detect(OA4, 'bronze') | str_detect(OA3, 'Bronze') | str_detect(OA2, 'Bronze') | str_detect(OA1, 'Bronze') ~ 'Bronze',
          str_detect(OA4, 'green') | str_detect(OA3, 'Green') | str_detect(OA2, 'Green') | str_detect(OA1, 'Green') ~ 'Green',
          .default = 'Not Given'
        ),
        pageCount = pmax(pageCount1, pageCount2, pageCount3, pageCount4, na.rm = TRUE),
        SourceTitle = case_when(
          SourceTitleD != '' ~ SourceTitleD,
          SourceTitleC != '' ~ SourceTitleC,
          SourceTitleB != '' ~ SourceTitleB,
          SourceTitleA != '' ~ SourceTitleA,
          .default = 'Not Given'
        ),
        ResearchArea = case_when(
          ResearchArea4 != '' ~ ResearchArea4,
          ResearchArea3 != '' ~ ResearchArea3,
          ResearchArea2 != '' ~ ResearchArea2,
          ResearchArea1 != '' ~ ResearchArea1,
          .default = 'Not Given'
        ),
        Affiliation = case_when(
          Affiliation4 != '' ~ Affiliation4,
          Affiliation3 != '' ~ Affiliation3,
          Affiliation2 != '' ~ Affiliation2,
          Affiliation1 != '' ~ Affiliation1,
          .default = 'Not Given'
        ),
        ISSN = case_when(
          ISSN4 != '' ~ ISSN4,
          ISSN3 != '' ~ ISSN3,
          ISSN2 != '' ~ ISSN2,
          ISSN1 != '' ~ ISSN1,
          .default = 'Not Given'
        ),
        ISBN = case_when(
          ISBN4 != '' ~ ISBN4,
          ISBN3 != '' ~ ISBN3,
          ISBN2 != '' ~ ISBN2,
          ISBN1 != '' ~ ISBN1,
          .default = 'Not Given'
        ),
        isCorrespondingAuthor = ifelse(isCA1 == 1 | isCA2 == 1 | isCA3 == 1 | isCA4 == 1, 1, 0),
        Databases = paste0(locationA, ', ', locationB, ', ', locationC, ', ', locationD)) |>
  mutate(Databases = str_replace(Databases, ",,", ",")) |>
  mutate(Databases = str_replace(Databases, " ,", ",")) |>
  mutate(Databases = str_replace(Databases, ",,", "")) |>
  mutate(Databases = ifelse(
    substr(Databases, nchar(Databases) - 1, nchar(Databases)) == ', ', substr(Databases, 1, nchar(Databases) - 2), Databases
  )) |>
  mutate(`Unified Document Type` = case_when(
    DocumentType %in% c('Review', 'Review Article', 'Book Review', 'Review; Book Chapter', 'Review; Early Access', 'Art Exhibit Review', 'Music Performance Review', 'Theater Review', 'Book Review; Early Access', 'Film Review', 'Art Exhibit Review', 'Book Review; Book Chapter', 'Database Review', 'review', 'peer-review') ~ 'Review',
    DocumentType %in% c('Article', 'Research Article', 'Article; Early Access', 'Article; Data Paper', 'Article; Publication with Expression of Concern', 'Article in press', 'article', 'preprint', 'report', 'dissertation') ~ 'Article',
    DocumentType %in% c('Book', 'Book chapter', 'Article; Book Chapter', 'Fiction, Creative Prose', 'Biographical-Item; Book Chapter', 'book-chapter', 'book') ~ 'Book',
    DocumentType %in% c('Letter', 'Letter To Editor', 'Letter to Editor', 'Editorial', 'Editorial Material', 'Editorial Material; Early Access', 'Editorial Material; Book Chapter', 'Letter; Early Access', 'editorial', 'letter') ~ 'Editorial Material',
    DocumentType %in% c('Correction', 'Correction; Book Chapter', 'Correction Erratum', 'Correction; Early Access') ~ 'Correction',
    DocumentType %in% c('Conference paper', 'Proceedings Paper', 'Article; Proceedings Paper') ~ 'Proceedings Paper',
    DocumentType %in% c('Conference Abstract', 'Meeting Abstract') ~ 'Abstract',
    .default = 'Other'
  )) |>
  mutate(ResearchArea = sapply(ResearchArea, function(x) paste(unique(unlist(str_split(x," , "))), collapse = ", "))) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor) |>
  mutate(`Publication Campus` = 'University of Colorado')



for (i in 1:dim(coloradoFinal)[1]){

  stringSplit = ifelse(
    length(str_split(coloradoFinal$Affiliation[i], ' , ')[[1]]) > 1, str_split(coloradoFinal$Affiliation[i], ' , ')[[1]], str_split(coloradoFinal$Affiliation[i], ';')[[1]]
  )

  coloradoFinal$isFirstAuthor[i] = ifelse(grepl('Boulder', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
  coloradoFinal$isLastAuthor[i] = ifelse(grepl('Boulder', stringSplit[length(stringSplit)], fixed = TRUE) == TRUE , 1, 0)
}


coloradoFinal
```




## Export to the Database


```{r}
dbWriteTable(con, name = 'full_pubs_colorado', value = coloradoFinal, append = FALSE, overwrite = TRUE)
```











# Kentucky Publications

```{r, warning = FALSE}
kentuckySmallA <- webOfScience |>
  filter(`Publication Campus` == 'University of Kentucky') |>
  select(`Publication Type`, Authors, `Source Title`, `Book Author Full Names`, `Article Title`, `Document Type`, Affiliations, ORCIDs, `Funding Orgs`, `Cited Reference Count`, `Times Cited, All Databases`, Publisher, ISSN, eISSN, ISBN, `Publication Date`, `Publication Year`, DOI, `DOI Link`, `Book DOI`, `WoS Categories`, `Research Areas`, `Pubmed Id`, `Open Access Designations`, `Highly Cited Status`, `Hot Paper Status`, `Publication Campus`, `Unified Publisher`, Resource, `Number of Pages`, `Reprint Addresses`)

kentuckySmallB <- scopus |>
  filter(`Publication Campus` == 'University of Kentucky') |>
  select(Authors, Title, Year, DOI, `Source title`, Link, Affiliations, Publisher, Sponsors, ISSN, ISBN, `PubMed ID`, `Document Type`, `Publication Campus`, `Unified Publisher`, Resource, `Open Access`, `Page count`) |>
  mutate(`Page count` = as.numeric(`Page count`))

kentuckySmallC <- dimensions |>
  filter(`Publication Campus` == 'University of Kentucky') |>
  select(DOI, ISBN, Title, Funding, Publisher, `Source title`, ISSN, `Publication date`, PubYear, `Open Access`, `Publication Type`, `Document Type`, Authors, `Corresponding Authors`, `Authors Affiliations`, Funder, `Times cited`, `Publication Campus`, `Unified Publisher`, PMID, Resource, `Units of Assessment`, `Funder Group`, Pagination, `Corresponding Authors`) |>
  mutate(`Page count` = ifelse(length(str_split(dimensions$Pagination[1], "-")[[1]]) != 2, NA, as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][2]) - as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][1])))

kentuckySmallD <- openAlex |>
  filter(`Publication Campus` == 'University of Kentucky') |>
  mutate(`Page count` = ifelse(is.na(last_page) == TRUE | is.na(first_page) == TRUE, 0, as.numeric(last_page) - as.numeric(first_page)),
         doi = substring(doi, 17, length(doi)),
         PubMedID = NA,
         Funding = NA,
         ISBN = NA)
```


## Clean Up Columns

```{r}
kentuckyCleanA <- kentuckySmallA |>
  select(DOI, `Article Title`, Resource, `Publication Year`, `Unified Publisher`, `Open Access Designations`, `Pubmed Id`, Authors, `Source Title`, `Document Type`, `Research Areas`, `Times Cited, All Databases`, Affiliations, ISSN, ISBN, `Number of Pages`, `Reprint Addresses`) |>
  mutate(`Source Title` = str_to_title(`Source Title`),
         `Number of Pages` = ifelse(is.na(`Number of Pages`) == TRUE, 0, `Number of Pages`))

kentuckyCleanB <- kentuckySmallB |>
  select(DOI, Title, Resource, Year, `Unified Publisher`, `Open Access`, `PubMed ID`, Authors, `Source title`, `Document Type`, Affiliations, ISSN, ISBN, `Page count`) |>
  mutate(`Research Areas` = NA,
         `Times Cited` = 0,
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`),
         `Correspondence Address` = NA)

kentuckyCleanC <- kentuckySmallC |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Units of Assessment`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`) |>
  mutate(`Research Areas` = substr(`Units of Assessment`, 5, nchar(`Units of Assessment`)),
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`)) |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Research Areas`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`)

kentuckyCleanD <- kentuckySmallD |>
  select(doi, title, `Publication Source`, publication_year, `Unified Publisher`, oa_status, PubMedID, Authors, source_display_name, type, Subjects, cited_by_count, Affiliations, issn_l, ISBN, `Page count`, isCorrespondingAuthor) |>
  mutate(isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 'Yes', 'University of Kentucky', isCorrespondingAuthor))

colnames(kentuckyCleanA) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(kentuckyCleanC) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(kentuckyCleanD) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
```


## Row Bind the Tables

```{r}
kentuckyFull <- rbind(kentuckyCleanA, kentuckyCleanB, kentuckyCleanC, kentuckyCleanD)
```



## Clean Final Table

```{r}
kentuckyFinal <- kentuckyFull |>
  group_by(DOI) |>
  summarise(locationCount = length(unique(Resource)),
            locationA = Resource[1],
            locationB = ifelse(length(unique(Resource)) == 1, '', Resource[2]),
            locationC = ifelse(length(unique(Resource)) < 3, '', Resource[3]),
            locationD = ifelse(length(unique(Resource)) == 4, Resource[4], ''),
            pubYear = min(Year),
            `Unified Publisher` = `Unified Publisher`[1],
            OA1 = `Open Access`[1],
            OA2 = ifelse(length(unique(Resource)) == 1, '', `Open Access`[2]),
            OA3 = ifelse(length(unique(Resource)) < 3, '', `Open Access`[3]),
            OA4 = ifelse(length(unique(Resource)) == 4, `Open Access`[4], ''),
            PubMedID = ifelse(is.na(`PubMed ID`[1]) == FALSE, `PubMed ID`[1],
                              ifelse(is.na(`PubMed ID`[2]) == FALSE, `PubMed ID`[2],
                                           ifelse(is.na(`PubMed ID`[3]) == FALSE, `PubMed ID`[3], `PubMed ID`[4]))),
            Authors = ifelse(is.na(`Authors`[1]) == FALSE, Authors[1],
                              ifelse(is.na(Authors[2]) == FALSE, Authors[2],
                                           ifelse(is.na(Authors[3]) == FALSE, Authors[3], Authors[4]))),
            NumAuthors = ifelse(Resource[1] == 'OpenAlex', length(str_split(Authors[1], ',')[[1]]), length(str_split(Authors[1], ';')[[1]])),
            SourceTitleA = `Source title`[1],
            SourceTitleB = ifelse(length(unique(Resource)) == 1, '', `Source title`[2]),
            SourceTitleC = ifelse(length(unique(Resource)) < 3, '', `Source title`[3]),
            SourceTitleD = ifelse(length(unique(Resource)) == 4, `Source title`[4], ''),
            DocumentType = `Document Type`[1],
            ResearchArea1 = `Research Areas`[1],
            ResearchArea2 = ifelse(length(unique(Resource)) == 1, '', `Research Areas`[2]),
            ResearchArea3 = ifelse(length(unique(Resource)) < 3, '', `Research Areas`[3]),
            ResearchArea4 = ifelse(length(unique(Resource)) == 4, `Research Areas`[4], ''),
            TimesCited = max(`Times Cited`, na.rm = TRUE),
            Affiliation1 = Affiliations[1],
            Affiliation2 = ifelse(length(unique(Resource)) == 1, '', Affiliations[2]),
            Affiliation3 = ifelse(length(unique(Resource)) < 3, '', Affiliations[3]),
            Affiliation4 = ifelse(length(unique(Resource)) == 4, Affiliations[4], ''),
            ISBN1 = ISBN[1],
            ISBN2 = ifelse(length(unique(Resource)) == 1, '', ISBN[2]),
            ISBN3 = ifelse(length(unique(Resource)) < 3, '', ISBN[3]),
            ISBN4 = ifelse(length(unique(Resource)) == 4, ISBN[4], ''),
            ISSN1 = ISSN[1],
            ISSN2 = ifelse(length(unique(Resource)) == 1, '', ISSN[2]),
            ISSN3 = ifelse(length(unique(Resource)) < 3, '', ISSN[3]),
            ISSN4 = ifelse(length(unique(Resource)) == 4, ISSN[4], ''),
            pageCount1 = `Page count`[1],
            pageCount2 = `Page count`[2],
            pageCount3 = `Page count`[3],
            pageCount4 = `Page count`[4],
            Title = Title[1],
            isCA1 = ifelse(grepl('University of Kentucky', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | `Correspondence Address`[1] == 'Yes', 1, 0),
            isCA2 = ifelse(grepl('University of Kentucky', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | `Correspondence Address`[2] == 'Yes', 1, 0),
            isCA3 = ifelse(grepl('University of Kentucky', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | `Correspondence Address`[3] == 'Yes', 1, 0),
            isCA4 = ifelse(grepl('University of Kentucky', `Correspondence Address`[4], ignore.case = TRUE) == TRUE | `Correspondence Address`[4] == 'Yes', 1, 0)) |>
  mutate(isCA1 = ifelse(is.na(isCA1) == TRUE, 0, isCA1),
         isCA2 = ifelse(is.na(isCA2) == TRUE, 0, isCA2),
         isCA3 = ifelse(is.na(isCA3) == TRUE, 0, isCA3),
         isCA4 = ifelse(is.na(isCA4) == TRUE, 0, isCA4)) |>
  mutate(OpenAccess = case_when(
          OA4 == 'closed' | OA3 == 'Closed' | OA2 == 'Closed' | OA1 == 'Closed' ~ 'Closed',
          str_detect(OA4, 'diamond') | str_detect(OA3, 'diamond') | str_detect(OA2, 'diamond') | str_detect(OA1, 'diamond') ~ 'Diamond',
          str_detect(OA4, 'hybrid') | str_detect(OA3, 'Hybrid') | str_detect(OA2, 'Hybrid') | str_detect(OA1, 'Hybrid') | str_detect(OA1, 'hybrid') ~ 'Hybrid',
          str_detect(OA4, 'gold') | str_detect(OA3, 'Gold') | str_detect(OA2, 'Gold') | str_detect(OA1, 'Gold') | str_detect(OA1, 'gold')  ~ 'Gold',
          str_detect(OA4, 'bronze') | str_detect(OA3, 'Bronze') | str_detect(OA2, 'Bronze') | str_detect(OA1, 'Bronze') ~ 'Bronze',
          str_detect(OA4, 'green') | str_detect(OA3, 'Green') | str_detect(OA2, 'Green') | str_detect(OA1, 'Green') ~ 'Green',
          .default = 'Not Given'
        ),
        pageCount = pmax(pageCount1, pageCount2, pageCount3, pageCount4, na.rm = TRUE),
        SourceTitle = case_when(
          SourceTitleD != '' ~ SourceTitleD,
          SourceTitleC != '' ~ SourceTitleC,
          SourceTitleB != '' ~ SourceTitleB,
          SourceTitleA != '' ~ SourceTitleA,
          .default = 'Not Given'
        ),
        ResearchArea = case_when(
          ResearchArea4 != '' ~ ResearchArea4,
          ResearchArea3 != '' ~ ResearchArea3,
          ResearchArea2 != '' ~ ResearchArea2,
          ResearchArea1 != '' ~ ResearchArea1,
          .default = 'Not Given'
        ),
        Affiliation = case_when(
          Affiliation4 != '' ~ Affiliation4,
          Affiliation3 != '' ~ Affiliation3,
          Affiliation2 != '' ~ Affiliation2,
          Affiliation1 != '' ~ Affiliation1,
          .default = 'Not Given'
        ),
        ISSN = case_when(
          ISSN4 != '' ~ ISSN4,
          ISSN3 != '' ~ ISSN3,
          ISSN2 != '' ~ ISSN2,
          ISSN1 != '' ~ ISSN1,
          .default = 'Not Given'
        ),
        ISBN = case_when(
          ISBN4 != '' ~ ISBN4,
          ISBN3 != '' ~ ISBN3,
          ISBN2 != '' ~ ISBN2,
          ISBN1 != '' ~ ISBN1,
          .default = 'Not Given'
        ),
        isCorrespondingAuthor = ifelse(isCA1 == 1 | isCA2 == 1 | isCA3 == 1 | isCA4 == 1, 1, 0),
        Databases = paste0(locationA, ', ', locationB, ', ', locationC, ', ', locationD)) |>
  mutate(Databases = str_replace(Databases, ",,", ",")) |>
  mutate(Databases = str_replace(Databases, " ,", ",")) |>
  mutate(Databases = str_replace(Databases, ",,", "")) |>
  mutate(Databases = ifelse(
    substr(Databases, nchar(Databases) - 1, nchar(Databases)) == ', ', substr(Databases, 1, nchar(Databases) - 2), Databases
  )) |>
  mutate(`Unified Document Type` = case_when(
    DocumentType %in% c('Review', 'Review Article', 'Book Review', 'Review; Book Chapter', 'Review; Early Access', 'Art Exhibit Review', 'Music Performance Review', 'Theater Review', 'Book Review; Early Access', 'Film Review', 'Art Exhibit Review', 'Book Review; Book Chapter', 'Database Review', 'review', 'peer-review') ~ 'Review',
    DocumentType %in% c('Article', 'Research Article', 'Article; Early Access', 'Article; Data Paper', 'Article; Publication with Expression of Concern', 'Article in press', 'article', 'preprint', 'report', 'dissertation') ~ 'Article',
    DocumentType %in% c('Book', 'Book chapter', 'Article; Book Chapter', 'Fiction, Creative Prose', 'Biographical-Item; Book Chapter', 'book-chapter', 'book') ~ 'Book',
    DocumentType %in% c('Letter', 'Letter To Editor', 'Letter to Editor', 'Editorial', 'Editorial Material', 'Editorial Material; Early Access', 'Editorial Material; Book Chapter', 'Letter; Early Access', 'editorial', 'letter') ~ 'Editorial Material',
    DocumentType %in% c('Correction', 'Correction; Book Chapter', 'Correction Erratum', 'Correction; Early Access') ~ 'Correction',
    DocumentType %in% c('Conference paper', 'Proceedings Paper', 'Article; Proceedings Paper') ~ 'Proceedings Paper',
    DocumentType %in% c('Conference Abstract', 'Meeting Abstract') ~ 'Abstract',
    .default = 'Other'
  )) |>
  mutate(ResearchArea = sapply(ResearchArea, function(x) paste(unique(unlist(str_split(x," , "))), collapse = ", "))) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor) |>
  mutate(`Publication Campus` = 'University of Kentucky')

for (i in 1:dim(kentuckyFinal)[1]){

  stringSplit = ifelse(
    length(str_split(kentuckyFinal$Affiliation[i], ' , ')[[1]]) > 1, str_split(kentuckyFinal$Affiliation[i], ' , ')[[1]], str_split(kentuckyFinal$Affiliation[i], ';')[[1]]
  )

  kentuckyFinal$isFirstAuthor[i] = ifelse(grepl('University of Kentucky', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
  kentuckyFinal$isLastAuthor[i] = ifelse(grepl('University of Kentucky', stringSplit[length(stringSplit)], fixed = TRUE) == TRUE , 1, 0)
}




kentuckyFinal
```




## Export to the Database


```{r}
dbWriteTable(con, name = 'full_pubs_kentucky', value = kentuckyFinal, append = FALSE, overwrite = TRUE)
```












# Missouri Publications

```{r, warning = FALSE}
missouriSmallA <- webOfScience |>
  filter(`Publication Campus` == 'University of Missouri') |>
  select(`Publication Type`, Authors, `Source Title`, `Book Author Full Names`, `Article Title`, `Document Type`, Affiliations, ORCIDs, `Funding Orgs`, `Cited Reference Count`, `Times Cited, All Databases`, Publisher, ISSN, eISSN, ISBN, `Publication Date`, `Publication Year`, DOI, `DOI Link`, `Book DOI`, `WoS Categories`, `Research Areas`, `Pubmed Id`, `Open Access Designations`, `Highly Cited Status`, `Hot Paper Status`, `Publication Campus`, `Unified Publisher`, Resource, `Number of Pages`, `Reprint Addresses`)

missouriSmallB <- scopus |>
  filter(`Publication Campus` == 'University of Missouri') |>
  select(Authors, Title, Year, DOI, `Source title`, Link, Affiliations, Publisher, Sponsors, ISSN, ISBN, `PubMed ID`, `Document Type`, `Publication Campus`, `Unified Publisher`, Resource, `Open Access`, `Page count`) |>
  mutate(`Page count` = as.numeric(`Page count`))

missouriSmallC <- dimensions |>
  filter(`Publication Campus` == 'University of Missouri') |>
  select(DOI, ISBN, Title, Funding, Publisher, `Source title`, ISSN, `Publication date`, PubYear, `Open Access`, `Publication Type`, `Document Type`, Authors, `Corresponding Authors`, `Authors Affiliations`, Funder, `Times cited`, `Publication Campus`, `Unified Publisher`, PMID, Resource, `Units of Assessment`, `Funder Group`, Pagination, `Corresponding Authors`) |>
  mutate(`Page count` = ifelse(length(str_split(dimensions$Pagination[1], "-")[[1]]) != 2, NA, as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][2]) - as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][1])))

missouriSmallD <- openAlex |>
  filter(`Publication Campus` == 'University of Missouri') |>
  mutate(`Page count` = ifelse(is.na(last_page) == TRUE | is.na(first_page) == TRUE, 0, as.numeric(last_page) - as.numeric(first_page)),
         doi = substring(doi, 17, length(doi)),
         PubMedID = NA,
         Funding = NA,
         ISBN = NA)
```


## Clean Up Columns

```{r}
missouriCleanA <- missouriSmallA |>
  select(DOI, `Article Title`, Resource, `Publication Year`, `Unified Publisher`, `Open Access Designations`, `Pubmed Id`, Authors, `Source Title`, `Document Type`, `Research Areas`, `Times Cited, All Databases`, Affiliations, ISSN, ISBN, `Number of Pages`, `Reprint Addresses`) |>
  mutate(`Source Title` = str_to_title(`Source Title`),
         `Number of Pages` = ifelse(is.na(`Number of Pages`) == TRUE, 0, `Number of Pages`))

missouriCleanB <- missouriSmallB |>
  select(DOI, Title, Resource, Year, `Unified Publisher`, `Open Access`, `PubMed ID`, Authors, `Source title`, `Document Type`, Affiliations, ISSN, ISBN, `Page count`) |>
  mutate(`Research Areas` = NA,
         `Times Cited` = 0,
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`),
         `Correspondence Address` = NA)

missouriCleanC <- missouriSmallC |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Units of Assessment`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`) |>
  mutate(`Research Areas` = substr(`Units of Assessment`, 5, nchar(`Units of Assessment`)),
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`)) |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Research Areas`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`)

missouriCleanD <- missouriSmallD |>
  select(doi, title, `Publication Source`, publication_year, `Unified Publisher`, oa_status, PubMedID, Authors, source_display_name, type, Subjects, cited_by_count, Affiliations, issn_l, ISBN, `Page count`, isCorrespondingAuthor) |>
  mutate(isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 'Yes', 'University of Missouri', isCorrespondingAuthor))

colnames(missouriCleanA) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(missouriCleanC) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(missouriCleanD) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
```


## Row Bind the Tables

```{r}
missouriFull <- rbind(missouriCleanA, missouriCleanB, missouriCleanC, missouriCleanD)
```



## Clean Final Table

```{r}
missouriFinal <- missouriFull |>
  group_by(DOI) |>
  summarise(locationCount = length(unique(Resource)),
            locationA = Resource[1],
            locationB = ifelse(length(unique(Resource)) == 1, '', Resource[2]),
            locationC = ifelse(length(unique(Resource)) < 3, '', Resource[3]),
            locationD = ifelse(length(unique(Resource)) == 4, Resource[4], ''),
            pubYear = min(Year),
            `Unified Publisher` = `Unified Publisher`[1],
            OA1 = `Open Access`[1],
            OA2 = ifelse(length(unique(Resource)) == 1, '', `Open Access`[2]),
            OA3 = ifelse(length(unique(Resource)) < 3, '', `Open Access`[3]),
            OA4 = ifelse(length(unique(Resource)) == 4, `Open Access`[4], ''),
            PubMedID = ifelse(is.na(`PubMed ID`[1]) == FALSE, `PubMed ID`[1],
                              ifelse(is.na(`PubMed ID`[2]) == FALSE, `PubMed ID`[2],
                                           ifelse(is.na(`PubMed ID`[3]) == FALSE, `PubMed ID`[3], `PubMed ID`[4]))),
            Authors = ifelse(is.na(`Authors`[1]) == FALSE, Authors[1],
                              ifelse(is.na(Authors[2]) == FALSE, Authors[2],
                                           ifelse(is.na(Authors[3]) == FALSE, Authors[3], Authors[4]))),
            NumAuthors = ifelse(Resource[1] == 'OpenAlex', length(str_split(Authors[1], ',')[[1]]), length(str_split(Authors[1], ';')[[1]])),
            SourceTitleA = `Source title`[1],
            SourceTitleB = ifelse(length(unique(Resource)) == 1, '', `Source title`[2]),
            SourceTitleC = ifelse(length(unique(Resource)) < 3, '', `Source title`[3]),
            SourceTitleD = ifelse(length(unique(Resource)) == 4, `Source title`[4], ''),
            DocumentType = `Document Type`[1],
            ResearchArea1 = `Research Areas`[1],
            ResearchArea2 = ifelse(length(unique(Resource)) == 1, '', `Research Areas`[2]),
            ResearchArea3 = ifelse(length(unique(Resource)) < 3, '', `Research Areas`[3]),
            ResearchArea4 = ifelse(length(unique(Resource)) == 4, `Research Areas`[4], ''),
            TimesCited = max(`Times Cited`, na.rm = TRUE),
            Affiliation1 = Affiliations[1],
            Affiliation2 = ifelse(length(unique(Resource)) == 1, '', Affiliations[2]),
            Affiliation3 = ifelse(length(unique(Resource)) < 3, '', Affiliations[3]),
            Affiliation4 = ifelse(length(unique(Resource)) == 4, Affiliations[4], ''),
            ISBN1 = ISBN[1],
            ISBN2 = ifelse(length(unique(Resource)) == 1, '', ISBN[2]),
            ISBN3 = ifelse(length(unique(Resource)) < 3, '', ISBN[3]),
            ISBN4 = ifelse(length(unique(Resource)) == 4, ISBN[4], ''),
            ISSN1 = ISSN[1],
            ISSN2 = ifelse(length(unique(Resource)) == 1, '', ISSN[2]),
            ISSN3 = ifelse(length(unique(Resource)) < 3, '', ISSN[3]),
            ISSN4 = ifelse(length(unique(Resource)) == 4, ISSN[4], ''),
            pageCount1 = `Page count`[1],
            pageCount2 = `Page count`[2],
            pageCount3 = `Page count`[3],
            pageCount4 = `Page count`[4],
            Title = Title[1],
            isCA1 = ifelse(grepl('Missouri', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | `Correspondence Address`[1] == 'Yes', 1, 0),
            isCA2 = ifelse(grepl('Missouri', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | `Correspondence Address`[2] == 'Yes', 1, 0),
            isCA3 = ifelse(grepl('Missouri', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | `Correspondence Address`[3] == 'Yes', 1, 0),
            isCA4 = ifelse(grepl('Missouri', `Correspondence Address`[4], ignore.case = TRUE) == TRUE | `Correspondence Address`[4] == 'Yes', 1, 0)) |>
  mutate(isCA1 = ifelse(is.na(isCA1) == TRUE, 0, isCA1),
         isCA2 = ifelse(is.na(isCA2) == TRUE, 0, isCA2),
         isCA3 = ifelse(is.na(isCA3) == TRUE, 0, isCA3),
         isCA4 = ifelse(is.na(isCA4) == TRUE, 0, isCA4)) |>
  mutate(OpenAccess = case_when(
          OA4 == 'closed' | OA3 == 'Closed' | OA2 == 'Closed' | OA1 == 'Closed' ~ 'Closed',
          str_detect(OA4, 'diamond') | str_detect(OA3, 'diamond') | str_detect(OA2, 'diamond') | str_detect(OA1, 'diamond') ~ 'Diamond',
          str_detect(OA4, 'hybrid') | str_detect(OA3, 'Hybrid') | str_detect(OA2, 'Hybrid') | str_detect(OA1, 'Hybrid') | str_detect(OA1, 'hybrid') ~ 'Hybrid',
          str_detect(OA4, 'gold') | str_detect(OA3, 'Gold') | str_detect(OA2, 'Gold') | str_detect(OA1, 'Gold') | str_detect(OA1, 'gold')  ~ 'Gold',
          str_detect(OA4, 'bronze') | str_detect(OA3, 'Bronze') | str_detect(OA2, 'Bronze') | str_detect(OA1, 'Bronze') ~ 'Bronze',
          str_detect(OA4, 'green') | str_detect(OA3, 'Green') | str_detect(OA2, 'Green') | str_detect(OA1, 'Green') ~ 'Green',
          .default = 'Not Given'
        ),
        pageCount = pmax(pageCount1, pageCount2, pageCount3, pageCount4, na.rm = TRUE),
        SourceTitle = case_when(
          SourceTitleD != '' ~ SourceTitleD,
          SourceTitleC != '' ~ SourceTitleC,
          SourceTitleB != '' ~ SourceTitleB,
          SourceTitleA != '' ~ SourceTitleA,
          .default = 'Not Given'
        ),
        ResearchArea = case_when(
          ResearchArea4 != '' ~ ResearchArea4,
          ResearchArea3 != '' ~ ResearchArea3,
          ResearchArea2 != '' ~ ResearchArea2,
          ResearchArea1 != '' ~ ResearchArea1,
          .default = 'Not Given'
        ),
        Affiliation = case_when(
          Affiliation4 != '' ~ Affiliation4,
          Affiliation3 != '' ~ Affiliation3,
          Affiliation2 != '' ~ Affiliation2,
          Affiliation1 != '' ~ Affiliation1,
          .default = 'Not Given'
        ),
        ISSN = case_when(
          ISSN4 != '' ~ ISSN4,
          ISSN3 != '' ~ ISSN3,
          ISSN2 != '' ~ ISSN2,
          ISSN1 != '' ~ ISSN1,
          .default = 'Not Given'
        ),
        ISBN = case_when(
          ISBN4 != '' ~ ISBN4,
          ISBN3 != '' ~ ISBN3,
          ISBN2 != '' ~ ISBN2,
          ISBN1 != '' ~ ISBN1,
          .default = 'Not Given'
        ),
        isCorrespondingAuthor = ifelse(isCA1 == 1 | isCA2 == 1 | isCA3 == 1 | isCA4 == 1, 1, 0),
        Databases = paste0(locationA, ', ', locationB, ', ', locationC, ', ', locationD)) |>
  mutate(Databases = str_replace(Databases, ",,", ",")) |>
  mutate(Databases = str_replace(Databases, " ,", ",")) |>
  mutate(Databases = str_replace(Databases, ",,", "")) |>
  mutate(Databases = ifelse(
    substr(Databases, nchar(Databases) - 1, nchar(Databases)) == ', ', substr(Databases, 1, nchar(Databases) - 2), Databases
  )) |>
  mutate(`Unified Document Type` = case_when(
    DocumentType %in% c('Review', 'Review Article', 'Book Review', 'Review; Book Chapter', 'Review; Early Access', 'Art Exhibit Review', 'Music Performance Review', 'Theater Review', 'Book Review; Early Access', 'Film Review', 'Art Exhibit Review', 'Book Review; Book Chapter', 'Database Review', 'review', 'peer-review') ~ 'Review',
    DocumentType %in% c('Article', 'Research Article', 'Article; Early Access', 'Article; Data Paper', 'Article; Publication with Expression of Concern', 'Article in press', 'article', 'preprint', 'report', 'dissertation') ~ 'Article',
    DocumentType %in% c('Book', 'Book chapter', 'Article; Book Chapter', 'Fiction, Creative Prose', 'Biographical-Item; Book Chapter', 'book-chapter', 'book') ~ 'Book',
    DocumentType %in% c('Letter', 'Letter To Editor', 'Letter to Editor', 'Editorial', 'Editorial Material', 'Editorial Material; Early Access', 'Editorial Material; Book Chapter', 'Letter; Early Access', 'editorial', 'letter') ~ 'Editorial Material',
    DocumentType %in% c('Correction', 'Correction; Book Chapter', 'Correction Erratum', 'Correction; Early Access') ~ 'Correction',
    DocumentType %in% c('Conference paper', 'Proceedings Paper', 'Article; Proceedings Paper') ~ 'Proceedings Paper',
    DocumentType %in% c('Conference Abstract', 'Meeting Abstract') ~ 'Abstract',
    .default = 'Other'
  )) |>
  mutate(ResearchArea = sapply(ResearchArea, function(x) paste(unique(unlist(str_split(x," , "))), collapse = ", "))) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor) |>
  mutate(`Publication Campus` = 'University of Missouri')



for (i in 1:dim(missouriFinal)[1]){

  stringSplit = ifelse(
    length(str_split(missouriFinal$Affiliation[i], ' , ')[[1]]) > 1, str_split(missouriFinal$Affiliation[i], ' , ')[[1]], str_split(missouriFinal$Affiliation[i], ';')[[1]]
  )

  missouriFinal$isFirstAuthor[i] = ifelse(grepl('University of Missouri', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
  missouriFinal$isLastAuthor[i] = ifelse(grepl('University of Missouri', stringSplit[length(stringSplit)], fixed = TRUE) == TRUE , 1, 0)
}



missouriFinal
```




## Export to the Database


```{r}
dbWriteTable(con, name = 'full_pubs_missouri', value = missouriFinal, append = FALSE, overwrite = TRUE)
```












# Nebraska Publications

```{r, warning = FALSE}
nebraskaSmallA <- webOfScience |>
  filter(`Publication Campus` == 'University of Nebraska') |>
  select(`Publication Type`, Authors, `Source Title`, `Book Author Full Names`, `Article Title`, `Document Type`, Affiliations, ORCIDs, `Funding Orgs`, `Cited Reference Count`, `Times Cited, All Databases`, Publisher, ISSN, eISSN, ISBN, `Publication Date`, `Publication Year`, DOI, `DOI Link`, `Book DOI`, `WoS Categories`, `Research Areas`, `Pubmed Id`, `Open Access Designations`, `Highly Cited Status`, `Hot Paper Status`, `Publication Campus`, `Unified Publisher`, Resource, `Number of Pages`, `Reprint Addresses`)

nebraskaSmallB <- scopus |>
  filter(`Publication Campus` == 'University of Nebraska') |>
  select(Authors, Title, Year, DOI, `Source title`, Link, Affiliations, Publisher, Sponsors, ISSN, ISBN, `PubMed ID`, `Document Type`, `Publication Campus`, `Unified Publisher`, Resource, `Open Access`, `Page count`) |>
  mutate(`Page count` = as.numeric(`Page count`))

nebraskaSmallC <- dimensions |>
  filter(`Publication Campus` == 'University of Nebraska') |>
  select(DOI, ISBN, Title, Funding, Publisher, `Source title`, ISSN, `Publication date`, PubYear, `Open Access`, `Publication Type`, `Document Type`, Authors, `Corresponding Authors`, `Authors Affiliations`, Funder, `Times cited`, `Publication Campus`, `Unified Publisher`, PMID, Resource, `Units of Assessment`, `Funder Group`, Pagination, `Corresponding Authors`) |>
  mutate(`Page count` = ifelse(length(str_split(dimensions$Pagination[1], "-")[[1]]) != 2, NA, as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][2]) - as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][1])))

nebraskaSmallD <- openAlex |>
  filter(`Publication Campus` == 'University of Nebraska') |>
  mutate(`Page count` = ifelse(is.na(last_page) == TRUE | is.na(first_page) == TRUE, 0, as.numeric(last_page) - as.numeric(first_page)),
         doi = substring(doi, 17, length(doi)),
         PubMedID = NA,
         Funding = NA,
         ISBN = NA)
```


## Clean Up Columns

```{r}
nebraskaCleanA <- nebraskaSmallA |>
  select(DOI, `Article Title`, Resource, `Publication Year`, `Unified Publisher`, `Open Access Designations`, `Pubmed Id`, Authors, `Source Title`, `Document Type`, `Research Areas`, `Times Cited, All Databases`, Affiliations, ISSN, ISBN, `Number of Pages`, `Reprint Addresses`) |>
  mutate(`Source Title` = str_to_title(`Source Title`),
         `Number of Pages` = ifelse(is.na(`Number of Pages`) == TRUE, 0, `Number of Pages`))

nebraskaCleanB <- nebraskaSmallB |>
  select(DOI, Title, Resource, Year, `Unified Publisher`, `Open Access`, `PubMed ID`, Authors, `Source title`, `Document Type`, Affiliations, ISSN, ISBN, `Page count`) |>
  mutate(`Research Areas` = NA,
         `Times Cited` = 0,
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`),
         `Correspondence Address` = NA)

nebraskaCleanC <- nebraskaSmallC |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Units of Assessment`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`) |>
  mutate(`Research Areas` = substr(`Units of Assessment`, 5, nchar(`Units of Assessment`)),
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`)) |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Research Areas`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`)

nebraskaCleanD <- nebraskaSmallD |>
  select(doi, title, `Publication Source`, publication_year, `Unified Publisher`, oa_status, PubMedID, Authors, source_display_name, type, Subjects, cited_by_count, Affiliations, issn_l, ISBN, `Page count`, isCorrespondingAuthor) |>
  mutate(isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 'Yes', 'University of Nebraska', isCorrespondingAuthor))

colnames(nebraskaCleanA) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(nebraskaCleanC) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(nebraskaCleanD) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
```


## Row Bind the Tables

```{r}
nebraskaFull <- rbind(nebraskaCleanA, nebraskaCleanB, nebraskaCleanC, nebraskaCleanD)
```



## Clean Final Table

```{r}
nebraskaFinal <- nebraskaFull |>
  group_by(DOI) |>
  summarise(locationCount = length(unique(Resource)),
            locationA = Resource[1],
            locationB = ifelse(length(unique(Resource)) == 1, '', Resource[2]),
            locationC = ifelse(length(unique(Resource)) < 3, '', Resource[3]),
            locationD = ifelse(length(unique(Resource)) == 4, Resource[4], ''),
            pubYear = min(Year),
            `Unified Publisher` = `Unified Publisher`[1],
            OA1 = `Open Access`[1],
            OA2 = ifelse(length(unique(Resource)) == 1, '', `Open Access`[2]),
            OA3 = ifelse(length(unique(Resource)) < 3, '', `Open Access`[3]),
            OA4 = ifelse(length(unique(Resource)) == 4, `Open Access`[4], ''),
            PubMedID = ifelse(is.na(`PubMed ID`[1]) == FALSE, `PubMed ID`[1],
                              ifelse(is.na(`PubMed ID`[2]) == FALSE, `PubMed ID`[2],
                                           ifelse(is.na(`PubMed ID`[3]) == FALSE, `PubMed ID`[3], `PubMed ID`[4]))),
            Authors = ifelse(is.na(`Authors`[1]) == FALSE, Authors[1],
                              ifelse(is.na(Authors[2]) == FALSE, Authors[2],
                                           ifelse(is.na(Authors[3]) == FALSE, Authors[3], Authors[4]))),
            NumAuthors = ifelse(Resource[1] == 'OpenAlex', length(str_split(Authors[1], ',')[[1]]), length(str_split(Authors[1], ';')[[1]])),
            SourceTitleA = `Source title`[1],
            SourceTitleB = ifelse(length(unique(Resource)) == 1, '', `Source title`[2]),
            SourceTitleC = ifelse(length(unique(Resource)) < 3, '', `Source title`[3]),
            SourceTitleD = ifelse(length(unique(Resource)) == 4, `Source title`[4], ''),
            DocumentType = `Document Type`[1],
            ResearchArea1 = `Research Areas`[1],
            ResearchArea2 = ifelse(length(unique(Resource)) == 1, '', `Research Areas`[2]),
            ResearchArea3 = ifelse(length(unique(Resource)) < 3, '', `Research Areas`[3]),
            ResearchArea4 = ifelse(length(unique(Resource)) == 4, `Research Areas`[4], ''),
            TimesCited = max(`Times Cited`, na.rm = TRUE),
            Affiliation1 = Affiliations[1],
            Affiliation2 = ifelse(length(unique(Resource)) == 1, '', Affiliations[2]),
            Affiliation3 = ifelse(length(unique(Resource)) < 3, '', Affiliations[3]),
            Affiliation4 = ifelse(length(unique(Resource)) == 4, Affiliations[4], ''),
            ISBN1 = ISBN[1],
            ISBN2 = ifelse(length(unique(Resource)) == 1, '', ISBN[2]),
            ISBN3 = ifelse(length(unique(Resource)) < 3, '', ISBN[3]),
            ISBN4 = ifelse(length(unique(Resource)) == 4, ISBN[4], ''),
            ISSN1 = ISSN[1],
            ISSN2 = ifelse(length(unique(Resource)) == 1, '', ISSN[2]),
            ISSN3 = ifelse(length(unique(Resource)) < 3, '', ISSN[3]),
            ISSN4 = ifelse(length(unique(Resource)) == 4, ISSN[4], ''),
            pageCount1 = `Page count`[1],
            pageCount2 = `Page count`[2],
            pageCount3 = `Page count`[3],
            pageCount4 = `Page count`[4],
            Title = Title[1],
            isCA1 = ifelse(grepl('Lincoln', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | `Correspondence Address`[1] == 'Yes', 1, 0),
            isCA2 = ifelse(grepl('Lincoln', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | `Correspondence Address`[2] == 'Yes', 1, 0),
            isCA3 = ifelse(grepl('Lincoln', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | `Correspondence Address`[3] == 'Yes', 1, 0),
            isCA4 = ifelse(grepl('Lincoln', `Correspondence Address`[4], ignore.case = TRUE) == TRUE | `Correspondence Address`[4] == 'Yes', 1, 0)) |>
  mutate(isCA1 = ifelse(is.na(isCA1) == TRUE, 0, isCA1),
         isCA2 = ifelse(is.na(isCA2) == TRUE, 0, isCA2),
         isCA3 = ifelse(is.na(isCA3) == TRUE, 0, isCA3),
         isCA4 = ifelse(is.na(isCA4) == TRUE, 0, isCA4)) |>
  mutate(OpenAccess = case_when(
          OA4 == 'closed' | OA3 == 'Closed' | OA2 == 'Closed' | OA1 == 'Closed' ~ 'Closed',
          str_detect(OA4, 'diamond') | str_detect(OA3, 'diamond') | str_detect(OA2, 'diamond') | str_detect(OA1, 'diamond') ~ 'Diamond',
          str_detect(OA4, 'hybrid') | str_detect(OA3, 'Hybrid') | str_detect(OA2, 'Hybrid') | str_detect(OA1, 'Hybrid') | str_detect(OA1, 'hybrid') ~ 'Hybrid',
          str_detect(OA4, 'gold') | str_detect(OA3, 'Gold') | str_detect(OA2, 'Gold') | str_detect(OA1, 'Gold') | str_detect(OA1, 'gold')  ~ 'Gold',
          str_detect(OA4, 'bronze') | str_detect(OA3, 'Bronze') | str_detect(OA2, 'Bronze') | str_detect(OA1, 'Bronze') ~ 'Bronze',
          str_detect(OA4, 'green') | str_detect(OA3, 'Green') | str_detect(OA2, 'Green') | str_detect(OA1, 'Green') ~ 'Green',
          .default = 'Not Given'
        ),
        pageCount = pmax(pageCount1, pageCount2, pageCount3, pageCount4, na.rm = TRUE),
        SourceTitle = case_when(
          SourceTitleD != '' ~ SourceTitleD,
          SourceTitleC != '' ~ SourceTitleC,
          SourceTitleB != '' ~ SourceTitleB,
          SourceTitleA != '' ~ SourceTitleA,
          .default = 'Not Given'
        ),
        ResearchArea = case_when(
          ResearchArea4 != '' ~ ResearchArea4,
          ResearchArea3 != '' ~ ResearchArea3,
          ResearchArea2 != '' ~ ResearchArea2,
          ResearchArea1 != '' ~ ResearchArea1,
          .default = 'Not Given'
        ),
        Affiliation = case_when(
          Affiliation4 != '' ~ Affiliation4,
          Affiliation3 != '' ~ Affiliation3,
          Affiliation2 != '' ~ Affiliation2,
          Affiliation1 != '' ~ Affiliation1,
          .default = 'Not Given'
        ),
        ISSN = case_when(
          ISSN4 != '' ~ ISSN4,
          ISSN3 != '' ~ ISSN3,
          ISSN2 != '' ~ ISSN2,
          ISSN1 != '' ~ ISSN1,
          .default = 'Not Given'
        ),
        ISBN = case_when(
          ISBN4 != '' ~ ISBN4,
          ISBN3 != '' ~ ISBN3,
          ISBN2 != '' ~ ISBN2,
          ISBN1 != '' ~ ISBN1,
          .default = 'Not Given'
        ),
        isCorrespondingAuthor = ifelse(isCA1 == 1 | isCA2 == 1 | isCA3 == 1 | isCA4 == 1, 1, 0),
        Databases = paste0(locationA, ', ', locationB, ', ', locationC, ', ', locationD)) |>
  mutate(Databases = str_replace(Databases, ",,", ",")) |>
  mutate(Databases = str_replace(Databases, " ,", ",")) |>
  mutate(Databases = str_replace(Databases, ",,", "")) |>
  mutate(Databases = ifelse(
    substr(Databases, nchar(Databases) - 1, nchar(Databases)) == ', ', substr(Databases, 1, nchar(Databases) - 2), Databases
  )) |>
  mutate(`Unified Document Type` = case_when(
    DocumentType %in% c('Review', 'Review Article', 'Book Review', 'Review; Book Chapter', 'Review; Early Access', 'Art Exhibit Review', 'Music Performance Review', 'Theater Review', 'Book Review; Early Access', 'Film Review', 'Art Exhibit Review', 'Book Review; Book Chapter', 'Database Review', 'review', 'peer-review') ~ 'Review',
    DocumentType %in% c('Article', 'Research Article', 'Article; Early Access', 'Article; Data Paper', 'Article; Publication with Expression of Concern', 'Article in press', 'article', 'preprint', 'report', 'dissertation') ~ 'Article',
    DocumentType %in% c('Book', 'Book chapter', 'Article; Book Chapter', 'Fiction, Creative Prose', 'Biographical-Item; Book Chapter', 'book-chapter', 'book') ~ 'Book',
    DocumentType %in% c('Letter', 'Letter To Editor', 'Letter to Editor', 'Editorial', 'Editorial Material', 'Editorial Material; Early Access', 'Editorial Material; Book Chapter', 'Letter; Early Access', 'editorial', 'letter') ~ 'Editorial Material',
    DocumentType %in% c('Correction', 'Correction; Book Chapter', 'Correction Erratum', 'Correction; Early Access') ~ 'Correction',
    DocumentType %in% c('Conference paper', 'Proceedings Paper', 'Article; Proceedings Paper') ~ 'Proceedings Paper',
    DocumentType %in% c('Conference Abstract', 'Meeting Abstract') ~ 'Abstract',
    .default = 'Other'
  )) |>
  mutate(ResearchArea = sapply(ResearchArea, function(x) paste(unique(unlist(str_split(x," , "))), collapse = ", "))) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor) |>
  mutate(`Publication Campus` = 'University of Nebraska')



for (i in 1:dim(nebraskaFinal)[1]){

  stringSplit = ifelse(
    length(str_split(nebraskaFinal$Affiliation[i], ' , ')[[1]]) > 1, str_split(nebraskaFinal$Affiliation[i], ' , ')[[1]], str_split(nebraskaFinal$Affiliation[i], ';')[[1]]
  )

  nebraskaFinal$isFirstAuthor[i] = ifelse(grepl('University of Nebraska', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
  nebraskaFinal$isLastAuthor[i] = ifelse(grepl('University of Nebraska', stringSplit[length(stringSplit)], fixed = TRUE) == TRUE , 1, 0)
}



nebraskaFinal
```




## Export to the Database


```{r}
dbWriteTable(con, name = 'full_pubs_nebraska', value = missouriFinal, append = FALSE, overwrite = TRUE)
```












# Oklahoma Publications

```{r, warning = FALSE}
oklahomaSmallA <- webOfScience |>
  filter(`Publication Campus` == 'University of Oklahoma') |>
  select(`Publication Type`, Authors, `Source Title`, `Book Author Full Names`, `Article Title`, `Document Type`, Affiliations, ORCIDs, `Funding Orgs`, `Cited Reference Count`, `Times Cited, All Databases`, Publisher, ISSN, eISSN, ISBN, `Publication Date`, `Publication Year`, DOI, `DOI Link`, `Book DOI`, `WoS Categories`, `Research Areas`, `Pubmed Id`, `Open Access Designations`, `Highly Cited Status`, `Hot Paper Status`, `Publication Campus`, `Unified Publisher`, Resource, `Number of Pages`, `Reprint Addresses`)

oklahomaSmallB <- scopus |>
  filter(`Publication Campus` == 'University of Oklahoma') |>
  select(Authors, Title, Year, DOI, `Source title`, Link, Affiliations, Publisher, Sponsors, ISSN, ISBN, `PubMed ID`, `Document Type`, `Publication Campus`, `Unified Publisher`, Resource, `Open Access`, `Page count`) |>
  mutate(`Page count` = as.numeric(`Page count`))

oklahomaSmallC <- dimensions |>
  filter(`Publication Campus` == 'University of Oklahoma') |>
  select(DOI, ISBN, Title, Funding, Publisher, `Source title`, ISSN, `Publication date`, PubYear, `Open Access`, `Publication Type`, `Document Type`, Authors, `Corresponding Authors`, `Authors Affiliations`, Funder, `Times cited`, `Publication Campus`, `Unified Publisher`, PMID, Resource, `Units of Assessment`, `Funder Group`, Pagination, `Corresponding Authors`) |>
  mutate(`Page count` = ifelse(length(str_split(dimensions$Pagination[1], "-")[[1]]) != 2, NA, as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][2]) - as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][1])))

oklahomaSmallD <- openAlex |>
  filter(`Publication Campus` == 'University of Oklahoma') |>
  mutate(`Page count` = ifelse(is.na(last_page) == TRUE | is.na(first_page) == TRUE, 0, as.numeric(last_page) - as.numeric(first_page)),
         doi = substring(doi, 17, length(doi)),
         PubMedID = NA,
         Funding = NA,
         ISBN = NA)
```


## Clean Up Columns

```{r}
oklahomaCleanA <- oklahomaSmallA |>
  select(DOI, `Article Title`, Resource, `Publication Year`, `Unified Publisher`, `Open Access Designations`, `Pubmed Id`, Authors, `Source Title`, `Document Type`, `Research Areas`, `Times Cited, All Databases`, Affiliations, ISSN, ISBN, `Number of Pages`, `Reprint Addresses`) |>
  mutate(`Source Title` = str_to_title(`Source Title`),
         `Number of Pages` = ifelse(is.na(`Number of Pages`) == TRUE, 0, `Number of Pages`))

oklahomaCleanB <- oklahomaSmallB |>
  select(DOI, Title, Resource, Year, `Unified Publisher`, `Open Access`, `PubMed ID`, Authors, `Source title`, `Document Type`, Affiliations, ISSN, ISBN, `Page count`) |>
  mutate(`Research Areas` = NA,
         `Times Cited` = 0,
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`),
         `Correspondence Address` = NA)

oklahomaCleanC <- oklahomaSmallC |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Units of Assessment`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`) |>
  mutate(`Research Areas` = substr(`Units of Assessment`, 5, nchar(`Units of Assessment`)),
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`)) |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Research Areas`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`)

oklahomaCleanD <- oklahomaSmallD |>
  select(doi, title, `Publication Source`, publication_year, `Unified Publisher`, oa_status, PubMedID, Authors, source_display_name, type, Subjects, cited_by_count, Affiliations, issn_l, ISBN, `Page count`, isCorrespondingAuthor) |>
  mutate(isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 'Yes', 'University of Oklahoma', isCorrespondingAuthor))

colnames(oklahomaCleanA) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(oklahomaCleanC) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(oklahomaCleanD) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
```


## Row Bind the Tables

```{r}
oklahomaFull <- rbind(oklahomaCleanA, oklahomaCleanB, oklahomaCleanC, oklahomaCleanD)
```



## Clean Final Table

```{r}
oklahomaFinal <- oklahomaFull |>
  group_by(DOI) |>
  summarise(locationCount = length(unique(Resource)),
            locationA = Resource[1],
            locationB = ifelse(length(unique(Resource)) == 1, '', Resource[2]),
            locationC = ifelse(length(unique(Resource)) < 3, '', Resource[3]),
            locationD = ifelse(length(unique(Resource)) == 4, Resource[4], ''),
            pubYear = min(Year),
            `Unified Publisher` = `Unified Publisher`[1],
            OA1 = `Open Access`[1],
            OA2 = ifelse(length(unique(Resource)) == 1, '', `Open Access`[2]),
            OA3 = ifelse(length(unique(Resource)) < 3, '', `Open Access`[3]),
            OA4 = ifelse(length(unique(Resource)) == 4, `Open Access`[4], ''),
            PubMedID = ifelse(is.na(`PubMed ID`[1]) == FALSE, `PubMed ID`[1],
                              ifelse(is.na(`PubMed ID`[2]) == FALSE, `PubMed ID`[2],
                                           ifelse(is.na(`PubMed ID`[3]) == FALSE, `PubMed ID`[3], `PubMed ID`[4]))),
            Authors = ifelse(is.na(`Authors`[1]) == FALSE, Authors[1],
                              ifelse(is.na(Authors[2]) == FALSE, Authors[2],
                                           ifelse(is.na(Authors[3]) == FALSE, Authors[3], Authors[4]))),
            NumAuthors = ifelse(Resource[1] == 'OpenAlex', length(str_split(Authors[1], ',')[[1]]), length(str_split(Authors[1], ';')[[1]])),
            SourceTitleA = `Source title`[1],
            SourceTitleB = ifelse(length(unique(Resource)) == 1, '', `Source title`[2]),
            SourceTitleC = ifelse(length(unique(Resource)) < 3, '', `Source title`[3]),
            SourceTitleD = ifelse(length(unique(Resource)) == 4, `Source title`[4], ''),
            DocumentType = `Document Type`[1],
            ResearchArea1 = `Research Areas`[1],
            ResearchArea2 = ifelse(length(unique(Resource)) == 1, '', `Research Areas`[2]),
            ResearchArea3 = ifelse(length(unique(Resource)) < 3, '', `Research Areas`[3]),
            ResearchArea4 = ifelse(length(unique(Resource)) == 4, `Research Areas`[4], ''),
            TimesCited = max(`Times Cited`, na.rm = TRUE),
            Affiliation1 = Affiliations[1],
            Affiliation2 = ifelse(length(unique(Resource)) == 1, '', Affiliations[2]),
            Affiliation3 = ifelse(length(unique(Resource)) < 3, '', Affiliations[3]),
            Affiliation4 = ifelse(length(unique(Resource)) == 4, Affiliations[4], ''),
            ISBN1 = ISBN[1],
            ISBN2 = ifelse(length(unique(Resource)) == 1, '', ISBN[2]),
            ISBN3 = ifelse(length(unique(Resource)) < 3, '', ISBN[3]),
            ISBN4 = ifelse(length(unique(Resource)) == 4, ISBN[4], ''),
            ISSN1 = ISSN[1],
            ISSN2 = ifelse(length(unique(Resource)) == 1, '', ISSN[2]),
            ISSN3 = ifelse(length(unique(Resource)) < 3, '', ISSN[3]),
            ISSN4 = ifelse(length(unique(Resource)) == 4, ISSN[4], ''),
            pageCount1 = `Page count`[1],
            pageCount2 = `Page count`[2],
            pageCount3 = `Page count`[3],
            pageCount4 = `Page count`[4],
            Title = Title[1],
            isCA1 = ifelse(grepl('University of Oklahoma', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | `Correspondence Address`[1] == 'Yes', 1, 0),
            isCA2 = ifelse(grepl('University of Oklahoma', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | `Correspondence Address`[2] == 'Yes', 1, 0),
            isCA3 = ifelse(grepl('University of Oklahoma', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | `Correspondence Address`[3] == 'Yes', 1, 0),
            isCA4 = ifelse(grepl('University of Oklahoma', `Correspondence Address`[4], ignore.case = TRUE) == TRUE | `Correspondence Address`[4] == 'Yes', 1, 0)) |>
  mutate(isCA1 = ifelse(is.na(isCA1) == TRUE, 0, isCA1),
         isCA2 = ifelse(is.na(isCA2) == TRUE, 0, isCA2),
         isCA3 = ifelse(is.na(isCA3) == TRUE, 0, isCA3),
         isCA4 = ifelse(is.na(isCA4) == TRUE, 0, isCA4)) |>
  mutate(OpenAccess = case_when(
          OA4 == 'closed' | OA3 == 'Closed' | OA2 == 'Closed' | OA1 == 'Closed' ~ 'Closed',
          str_detect(OA4, 'diamond') | str_detect(OA3, 'diamond') | str_detect(OA2, 'diamond') | str_detect(OA1, 'diamond') ~ 'Diamond',
          str_detect(OA4, 'hybrid') | str_detect(OA3, 'Hybrid') | str_detect(OA2, 'Hybrid') | str_detect(OA1, 'Hybrid') | str_detect(OA1, 'hybrid') ~ 'Hybrid',
          str_detect(OA4, 'gold') | str_detect(OA3, 'Gold') | str_detect(OA2, 'Gold') | str_detect(OA1, 'Gold') | str_detect(OA1, 'gold')  ~ 'Gold',
          str_detect(OA4, 'bronze') | str_detect(OA3, 'Bronze') | str_detect(OA2, 'Bronze') | str_detect(OA1, 'Bronze') ~ 'Bronze',
          str_detect(OA4, 'green') | str_detect(OA3, 'Green') | str_detect(OA2, 'Green') | str_detect(OA1, 'Green') ~ 'Green',
          .default = 'Not Given'
        ),
        pageCount = pmax(pageCount1, pageCount2, pageCount3, pageCount4, na.rm = TRUE),
        SourceTitle = case_when(
          SourceTitleD != '' ~ SourceTitleD,
          SourceTitleC != '' ~ SourceTitleC,
          SourceTitleB != '' ~ SourceTitleB,
          SourceTitleA != '' ~ SourceTitleA,
          .default = 'Not Given'
        ),
        ResearchArea = case_when(
          ResearchArea4 != '' ~ ResearchArea4,
          ResearchArea3 != '' ~ ResearchArea3,
          ResearchArea2 != '' ~ ResearchArea2,
          ResearchArea1 != '' ~ ResearchArea1,
          .default = 'Not Given'
        ),
        Affiliation = case_when(
          Affiliation4 != '' ~ Affiliation4,
          Affiliation3 != '' ~ Affiliation3,
          Affiliation2 != '' ~ Affiliation2,
          Affiliation1 != '' ~ Affiliation1,
          .default = 'Not Given'
        ),
        ISSN = case_when(
          ISSN4 != '' ~ ISSN4,
          ISSN3 != '' ~ ISSN3,
          ISSN2 != '' ~ ISSN2,
          ISSN1 != '' ~ ISSN1,
          .default = 'Not Given'
        ),
        ISBN = case_when(
          ISBN4 != '' ~ ISBN4,
          ISBN3 != '' ~ ISBN3,
          ISBN2 != '' ~ ISBN2,
          ISBN1 != '' ~ ISBN1,
          .default = 'Not Given'
        ),
        isCorrespondingAuthor = ifelse(isCA1 == 1 | isCA2 == 1 | isCA3 == 1 | isCA4 == 1, 1, 0),
        Databases = paste0(locationA, ', ', locationB, ', ', locationC, ', ', locationD)) |>
  mutate(Databases = str_replace(Databases, ",,", ",")) |>
  mutate(Databases = str_replace(Databases, " ,", ",")) |>
  mutate(Databases = str_replace(Databases, ",,", "")) |>
  mutate(Databases = ifelse(
    substr(Databases, nchar(Databases) - 1, nchar(Databases)) == ', ', substr(Databases, 1, nchar(Databases) - 2), Databases
  )) |>
  mutate(`Unified Document Type` = case_when(
    DocumentType %in% c('Review', 'Review Article', 'Book Review', 'Review; Book Chapter', 'Review; Early Access', 'Art Exhibit Review', 'Music Performance Review', 'Theater Review', 'Book Review; Early Access', 'Film Review', 'Art Exhibit Review', 'Book Review; Book Chapter', 'Database Review', 'review', 'peer-review') ~ 'Review',
    DocumentType %in% c('Article', 'Research Article', 'Article; Early Access', 'Article; Data Paper', 'Article; Publication with Expression of Concern', 'Article in press', 'article', 'preprint', 'report', 'dissertation') ~ 'Article',
    DocumentType %in% c('Book', 'Book chapter', 'Article; Book Chapter', 'Fiction, Creative Prose', 'Biographical-Item; Book Chapter', 'book-chapter', 'book') ~ 'Book',
    DocumentType %in% c('Letter', 'Letter To Editor', 'Letter to Editor', 'Editorial', 'Editorial Material', 'Editorial Material; Early Access', 'Editorial Material; Book Chapter', 'Letter; Early Access', 'editorial', 'letter') ~ 'Editorial Material',
    DocumentType %in% c('Correction', 'Correction; Book Chapter', 'Correction Erratum', 'Correction; Early Access') ~ 'Correction',
    DocumentType %in% c('Conference paper', 'Proceedings Paper', 'Article; Proceedings Paper') ~ 'Proceedings Paper',
    DocumentType %in% c('Conference Abstract', 'Meeting Abstract') ~ 'Abstract',
    .default = 'Other'
  )) |>
  mutate(ResearchArea = sapply(ResearchArea, function(x) paste(unique(unlist(str_split(x," , "))), collapse = ", "))) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor) |>
  mutate(`Publication Campus` = 'University of Oklahoma')



for (i in 1:dim(oklahomaFinal)[1]){

  stringSplit = ifelse(
    length(str_split(oklahomaFinal$Affiliation[i], ' , ')[[1]]) > 1, str_split(oklahomaFinal$Affiliation[i], ' , ')[[1]], str_split(oklahomaFinal$Affiliation[i], ';')[[1]]
  )

  oklahomaFinal$isFirstAuthor[i] = ifelse(grepl('University of Oklahoma', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
  oklahomaFinal$isLastAuthor[i] = ifelse(grepl('University of Oklahoma', stringSplit[length(stringSplit)], fixed = TRUE) == TRUE , 1, 0)
}



oklahomaFinal
```




## Export to the Database


```{r}
dbWriteTable(con, name = 'full_pubs_oklahoma', value = oklahomaFinal, append = FALSE, overwrite = TRUE)
```














# South Carolina Publications

```{r, warning = FALSE}
scSmallA <- webOfScience |>
  filter(`Publication Campus` == 'University of South Carolina') |>
  select(`Publication Type`, Authors, `Source Title`, `Book Author Full Names`, `Article Title`, `Document Type`, Affiliations, ORCIDs, `Funding Orgs`, `Cited Reference Count`, `Times Cited, All Databases`, Publisher, ISSN, eISSN, ISBN, `Publication Date`, `Publication Year`, DOI, `DOI Link`, `Book DOI`, `WoS Categories`, `Research Areas`, `Pubmed Id`, `Open Access Designations`, `Highly Cited Status`, `Hot Paper Status`, `Publication Campus`, `Unified Publisher`, Resource, `Number of Pages`, `Reprint Addresses`)

scSmallB <- scopus |>
  filter(`Publication Campus` == 'University of South Carolina') |>
  select(Authors, Title, Year, DOI, `Source title`, Link, Affiliations, Publisher, Sponsors, ISSN, ISBN, `PubMed ID`, `Document Type`, `Publication Campus`, `Unified Publisher`, Resource, `Open Access`, `Page count`) |>
  mutate(`Page count` = as.numeric(`Page count`))

scSmallC <- dimensions |>
  filter(`Publication Campus` == 'University of South Carolina') |>
  select(DOI, ISBN, Title, Funding, Publisher, `Source title`, ISSN, `Publication date`, PubYear, `Open Access`, `Publication Type`, `Document Type`, Authors, `Corresponding Authors`, `Authors Affiliations`, Funder, `Times cited`, `Publication Campus`, `Unified Publisher`, PMID, Resource, `Units of Assessment`, `Funder Group`, Pagination, `Corresponding Authors`) |>
  mutate(`Page count` = ifelse(length(str_split(dimensions$Pagination[1], "-")[[1]]) != 2, NA, as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][2]) - as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][1])))

scSmallD <- openAlex |>
  filter(`Publication Campus` == 'University of South Carolina') |>
  mutate(`Page count` = ifelse(is.na(last_page) == TRUE | is.na(first_page) == TRUE, 0, as.numeric(last_page) - as.numeric(first_page)),
         doi = substring(doi, 17, length(doi)),
         PubMedID = NA,
         Funding = NA,
         ISBN = NA)
```


## Clean Up Columns

```{r}
scCleanA <- scSmallA |>
  select(DOI, `Article Title`, Resource, `Publication Year`, `Unified Publisher`, `Open Access Designations`, `Pubmed Id`, Authors, `Source Title`, `Document Type`, `Research Areas`, `Times Cited, All Databases`, Affiliations, ISSN, ISBN, `Number of Pages`, `Reprint Addresses`) |>
  mutate(`Source Title` = str_to_title(`Source Title`),
         `Number of Pages` = ifelse(is.na(`Number of Pages`) == TRUE, 0, `Number of Pages`))

scCleanB <- scSmallB |>
  select(DOI, Title, Resource, Year, `Unified Publisher`, `Open Access`, `PubMed ID`, Authors, `Source title`, `Document Type`, Affiliations, ISSN, ISBN, `Page count`) |>
  mutate(`Research Areas` = NA,
         `Times Cited` = 0,
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`),
         `Correspondence Address` = NA)

scCleanC <- scSmallC |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Units of Assessment`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`) |>
  mutate(`Research Areas` = substr(`Units of Assessment`, 5, nchar(`Units of Assessment`)),
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`)) |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Research Areas`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`)

scCleanD <- scSmallD |>
  select(doi, title, `Publication Source`, publication_year, `Unified Publisher`, oa_status, PubMedID, Authors, source_display_name, type, Subjects, cited_by_count, Affiliations, issn_l, ISBN, `Page count`, isCorrespondingAuthor) |>
  mutate(isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 'Yes', 'University of South Carolina', isCorrespondingAuthor))

colnames(scCleanA) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(scCleanC) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(scCleanD) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
```


## Row Bind the Tables

```{r}
scFull <- rbind(scCleanA, scCleanB, scCleanC, scCleanD)
```



## Clean Final Table

```{r}
scFinal <- scFull |>
  group_by(DOI) |>
  summarise(locationCount = length(unique(Resource)),
            locationA = Resource[1],
            locationB = ifelse(length(unique(Resource)) == 1, '', Resource[2]),
            locationC = ifelse(length(unique(Resource)) < 3, '', Resource[3]),
            locationD = ifelse(length(unique(Resource)) == 4, Resource[4], ''),
            pubYear = min(Year),
            `Unified Publisher` = `Unified Publisher`[1],
            OA1 = `Open Access`[1],
            OA2 = ifelse(length(unique(Resource)) == 1, '', `Open Access`[2]),
            OA3 = ifelse(length(unique(Resource)) < 3, '', `Open Access`[3]),
            OA4 = ifelse(length(unique(Resource)) == 4, `Open Access`[4], ''),
            PubMedID = ifelse(is.na(`PubMed ID`[1]) == FALSE, `PubMed ID`[1],
                              ifelse(is.na(`PubMed ID`[2]) == FALSE, `PubMed ID`[2],
                                           ifelse(is.na(`PubMed ID`[3]) == FALSE, `PubMed ID`[3], `PubMed ID`[4]))),
            Authors = ifelse(is.na(`Authors`[1]) == FALSE, Authors[1],
                              ifelse(is.na(Authors[2]) == FALSE, Authors[2],
                                           ifelse(is.na(Authors[3]) == FALSE, Authors[3], Authors[4]))),
            NumAuthors = ifelse(Resource[1] == 'OpenAlex', length(str_split(Authors[1], ',')[[1]]), length(str_split(Authors[1], ';')[[1]])),
            SourceTitleA = `Source title`[1],
            SourceTitleB = ifelse(length(unique(Resource)) == 1, '', `Source title`[2]),
            SourceTitleC = ifelse(length(unique(Resource)) < 3, '', `Source title`[3]),
            SourceTitleD = ifelse(length(unique(Resource)) == 4, `Source title`[4], ''),
            DocumentType = `Document Type`[1],
            ResearchArea1 = `Research Areas`[1],
            ResearchArea2 = ifelse(length(unique(Resource)) == 1, '', `Research Areas`[2]),
            ResearchArea3 = ifelse(length(unique(Resource)) < 3, '', `Research Areas`[3]),
            ResearchArea4 = ifelse(length(unique(Resource)) == 4, `Research Areas`[4], ''),
            TimesCited = max(`Times Cited`, na.rm = TRUE),
            Affiliation1 = Affiliations[1],
            Affiliation2 = ifelse(length(unique(Resource)) == 1, '', Affiliations[2]),
            Affiliation3 = ifelse(length(unique(Resource)) < 3, '', Affiliations[3]),
            Affiliation4 = ifelse(length(unique(Resource)) == 4, Affiliations[4], ''),
            ISBN1 = ISBN[1],
            ISBN2 = ifelse(length(unique(Resource)) == 1, '', ISBN[2]),
            ISBN3 = ifelse(length(unique(Resource)) < 3, '', ISBN[3]),
            ISBN4 = ifelse(length(unique(Resource)) == 4, ISBN[4], ''),
            ISSN1 = ISSN[1],
            ISSN2 = ifelse(length(unique(Resource)) == 1, '', ISSN[2]),
            ISSN3 = ifelse(length(unique(Resource)) < 3, '', ISSN[3]),
            ISSN4 = ifelse(length(unique(Resource)) == 4, ISSN[4], ''),
            pageCount1 = `Page count`[1],
            pageCount2 = `Page count`[2],
            pageCount3 = `Page count`[3],
            pageCount4 = `Page count`[4],
            Title = Title[1],
            isCA1 = ifelse(grepl('University of South Carolina', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | `Correspondence Address`[1] == 'Yes', 1, 0),
            isCA2 = ifelse(grepl('University of South Carolina', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | `Correspondence Address`[2] == 'Yes', 1, 0),
            isCA3 = ifelse(grepl('University of South Carolina', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | `Correspondence Address`[3] == 'Yes', 1, 0),
            isCA4 = ifelse(grepl('University of South Carolina', `Correspondence Address`[4], ignore.case = TRUE) == TRUE | `Correspondence Address`[4] == 'Yes', 1, 0)) |>
  mutate(isCA1 = ifelse(is.na(isCA1) == TRUE, 0, isCA1),
         isCA2 = ifelse(is.na(isCA2) == TRUE, 0, isCA2),
         isCA3 = ifelse(is.na(isCA3) == TRUE, 0, isCA3),
         isCA4 = ifelse(is.na(isCA4) == TRUE, 0, isCA4)) |>
  mutate(OpenAccess = case_when(
          OA4 == 'closed' | OA3 == 'Closed' | OA2 == 'Closed' | OA1 == 'Closed' ~ 'Closed',
          str_detect(OA4, 'diamond') | str_detect(OA3, 'diamond') | str_detect(OA2, 'diamond') | str_detect(OA1, 'diamond') ~ 'Diamond',
          str_detect(OA4, 'hybrid') | str_detect(OA3, 'Hybrid') | str_detect(OA2, 'Hybrid') | str_detect(OA1, 'Hybrid') | str_detect(OA1, 'hybrid') ~ 'Hybrid',
          str_detect(OA4, 'gold') | str_detect(OA3, 'Gold') | str_detect(OA2, 'Gold') | str_detect(OA1, 'Gold') | str_detect(OA1, 'gold')  ~ 'Gold',
          str_detect(OA4, 'bronze') | str_detect(OA3, 'Bronze') | str_detect(OA2, 'Bronze') | str_detect(OA1, 'Bronze') ~ 'Bronze',
          str_detect(OA4, 'green') | str_detect(OA3, 'Green') | str_detect(OA2, 'Green') | str_detect(OA1, 'Green') ~ 'Green',
          .default = 'Not Given'
        ),
        pageCount = pmax(pageCount1, pageCount2, pageCount3, pageCount4, na.rm = TRUE),
        SourceTitle = case_when(
          SourceTitleD != '' ~ SourceTitleD,
          SourceTitleC != '' ~ SourceTitleC,
          SourceTitleB != '' ~ SourceTitleB,
          SourceTitleA != '' ~ SourceTitleA,
          .default = 'Not Given'
        ),
        ResearchArea = case_when(
          ResearchArea4 != '' ~ ResearchArea4,
          ResearchArea3 != '' ~ ResearchArea3,
          ResearchArea2 != '' ~ ResearchArea2,
          ResearchArea1 != '' ~ ResearchArea1,
          .default = 'Not Given'
        ),
        Affiliation = case_when(
          Affiliation4 != '' ~ Affiliation4,
          Affiliation3 != '' ~ Affiliation3,
          Affiliation2 != '' ~ Affiliation2,
          Affiliation1 != '' ~ Affiliation1,
          .default = 'Not Given'
        ),
        ISSN = case_when(
          ISSN4 != '' ~ ISSN4,
          ISSN3 != '' ~ ISSN3,
          ISSN2 != '' ~ ISSN2,
          ISSN1 != '' ~ ISSN1,
          .default = 'Not Given'
        ),
        ISBN = case_when(
          ISBN4 != '' ~ ISBN4,
          ISBN3 != '' ~ ISBN3,
          ISBN2 != '' ~ ISBN2,
          ISBN1 != '' ~ ISBN1,
          .default = 'Not Given'
        ),
        isCorrespondingAuthor = ifelse(isCA1 == 1 | isCA2 == 1 | isCA3 == 1 | isCA4 == 1, 1, 0),
        Databases = paste0(locationA, ', ', locationB, ', ', locationC, ', ', locationD)) |>
  mutate(Databases = str_replace(Databases, ",,", ",")) |>
  mutate(Databases = str_replace(Databases, " ,", ",")) |>
  mutate(Databases = str_replace(Databases, ",,", "")) |>
  mutate(Databases = ifelse(
    substr(Databases, nchar(Databases) - 1, nchar(Databases)) == ', ', substr(Databases, 1, nchar(Databases) - 2), Databases
  )) |>
  mutate(`Unified Document Type` = case_when(
    DocumentType %in% c('Review', 'Review Article', 'Book Review', 'Review; Book Chapter', 'Review; Early Access', 'Art Exhibit Review', 'Music Performance Review', 'Theater Review', 'Book Review; Early Access', 'Film Review', 'Art Exhibit Review', 'Book Review; Book Chapter', 'Database Review', 'review', 'peer-review') ~ 'Review',
    DocumentType %in% c('Article', 'Research Article', 'Article; Early Access', 'Article; Data Paper', 'Article; Publication with Expression of Concern', 'Article in press', 'article', 'preprint', 'report', 'dissertation') ~ 'Article',
    DocumentType %in% c('Book', 'Book chapter', 'Article; Book Chapter', 'Fiction, Creative Prose', 'Biographical-Item; Book Chapter', 'book-chapter', 'book') ~ 'Book',
    DocumentType %in% c('Letter', 'Letter To Editor', 'Letter to Editor', 'Editorial', 'Editorial Material', 'Editorial Material; Early Access', 'Editorial Material; Book Chapter', 'Letter; Early Access', 'editorial', 'letter') ~ 'Editorial Material',
    DocumentType %in% c('Correction', 'Correction; Book Chapter', 'Correction Erratum', 'Correction; Early Access') ~ 'Correction',
    DocumentType %in% c('Conference paper', 'Proceedings Paper', 'Article; Proceedings Paper') ~ 'Proceedings Paper',
    DocumentType %in% c('Conference Abstract', 'Meeting Abstract') ~ 'Abstract',
    .default = 'Other'
  )) |>
  mutate(ResearchArea = sapply(ResearchArea, function(x) paste(unique(unlist(str_split(x," , "))), collapse = ", "))) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor) |>
  mutate(`Publication Campus` = 'University of South Carolina')



for (i in 1:dim(scFinal)[1]){

  stringSplit = ifelse(
    length(str_split(scFinal$Affiliation[i], ' , ')[[1]]) > 1, str_split(scFinal$Affiliation[i], ' , ')[[1]], str_split(scFinal$Affiliation[i], ';')[[1]]
  )

  scFinal$isFirstAuthor[i] = ifelse(grepl('University of South Carolina', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
  scFinal$isLastAuthor[i] = ifelse(grepl('University of South Carolina', stringSplit[length(stringSplit)], fixed = TRUE) == TRUE , 1, 0)
}



scFinal
```




## Export to the Database


```{r}
dbWriteTable(con, name = 'full_pubs_southcarolina', value = scFinal, append = FALSE, overwrite = TRUE)
```












# Virginia Tech Publications

```{r, warning = FALSE}
vtSmallA <- webOfScience |>
  filter(`Publication Campus` == 'Virginia Tech') |>
  select(`Publication Type`, Authors, `Source Title`, `Book Author Full Names`, `Article Title`, `Document Type`, Affiliations, ORCIDs, `Funding Orgs`, `Cited Reference Count`, `Times Cited, All Databases`, Publisher, ISSN, eISSN, ISBN, `Publication Date`, `Publication Year`, DOI, `DOI Link`, `Book DOI`, `WoS Categories`, `Research Areas`, `Pubmed Id`, `Open Access Designations`, `Highly Cited Status`, `Hot Paper Status`, `Publication Campus`, `Unified Publisher`, Resource, `Number of Pages`, `Reprint Addresses`)

vtSmallB <- scopus |>
  filter(`Publication Campus` == 'Virginia Tech') |>
  select(Authors, Title, Year, DOI, `Source title`, Link, Affiliations, Publisher, Sponsors, ISSN, ISBN, `PubMed ID`, `Document Type`, `Publication Campus`, `Unified Publisher`, Resource, `Open Access`, `Page count`) |>
  mutate(`Page count` = as.numeric(`Page count`))

vtSmallC <- dimensions |>
  filter(`Publication Campus` == 'Virginia Tech') |>
  select(DOI, ISBN, Title, Funding, Publisher, `Source title`, ISSN, `Publication date`, PubYear, `Open Access`, `Publication Type`, `Document Type`, Authors, `Corresponding Authors`, `Authors Affiliations`, Funder, `Times cited`, `Publication Campus`, `Unified Publisher`, PMID, Resource, `Units of Assessment`, `Funder Group`, Pagination, `Corresponding Authors`) |>
  mutate(`Page count` = ifelse(length(str_split(dimensions$Pagination[1], "-")[[1]]) != 2, NA, as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][2]) - as.numeric(str_split(dimensions$Pagination[1], "-")[[1]][1])))

vtSmallD <- openAlex |>
  filter(`Publication Campus` == 'Virginia Tech') |>
  mutate(`Page count` = ifelse(is.na(last_page) == TRUE | is.na(first_page) == TRUE, 0, as.numeric(last_page) - as.numeric(first_page)),
         doi = substring(doi, 17, length(doi)),
         PubMedID = NA,
         Funding = NA,
         ISBN = NA)
```


## Clean Up Columns

```{r}
vtCleanA <- vtSmallA |>
  select(DOI, `Article Title`, Resource, `Publication Year`, `Unified Publisher`, `Open Access Designations`, `Pubmed Id`, Authors, `Source Title`, `Document Type`, `Research Areas`, `Times Cited, All Databases`, Affiliations, ISSN, ISBN, `Number of Pages`, `Reprint Addresses`) |>
  mutate(`Source Title` = str_to_title(`Source Title`),
         `Number of Pages` = ifelse(is.na(`Number of Pages`) == TRUE, 0, `Number of Pages`))

vtCleanB <- vtSmallB |>
  select(DOI, Title, Resource, Year, `Unified Publisher`, `Open Access`, `PubMed ID`, Authors, `Source title`, `Document Type`, Affiliations, ISSN, ISBN, `Page count`) |>
  mutate(`Research Areas` = NA,
         `Times Cited` = 0,
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`),
         `Correspondence Address` = NA)

vtCleanC <- vtSmallC |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Units of Assessment`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`) |>
  mutate(`Research Areas` = substr(`Units of Assessment`, 5, nchar(`Units of Assessment`)),
         `Page count` = ifelse(is.na(`Page count`) == TRUE, 0, `Page count`)) |>
  select(DOI, Title, Resource, PubYear, `Unified Publisher`, `Open Access`, PMID, Authors, `Source title`, `Document Type`, `Research Areas`, `Times cited`, `Authors Affiliations`, ISSN, ISBN, `Page count`, `Corresponding Authors`)

vtCleanD <- vtSmallD |>
  select(doi, title, `Publication Source`, publication_year, `Unified Publisher`, oa_status, PubMedID, Authors, source_display_name, type, Subjects, cited_by_count, Affiliations, issn_l, ISBN, `Page count`, isCorrespondingAuthor) |>
  mutate(isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 'Yes', 'Virginia Tech', isCorrespondingAuthor))

colnames(vtCleanA) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(vtCleanC) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
colnames(vtCleanD) <- c('DOI', 'Title', 'Resource', 'Year', 'Unified Publisher', 'Open Access', 'PubMed ID', 'Authors', 'Source title', 'Document Type', 'Research Areas', 'Times Cited', 'Affiliations', 'ISSN', 'ISBN', 'Page count', 'Correspondence Address')
```


## Row Bind the Tables

```{r}
vtFull <- rbind(vtCleanA, vtCleanB, vtCleanC, vtCleanD)
```



## Clean Final Table

```{r}
vtFinal <- vtFull |>
  group_by(DOI) |>
  summarise(locationCount = length(unique(Resource)),
            locationA = Resource[1],
            locationB = ifelse(length(unique(Resource)) == 1, '', Resource[2]),
            locationC = ifelse(length(unique(Resource)) < 3, '', Resource[3]),
            locationD = ifelse(length(unique(Resource)) == 4, Resource[4], ''),
            pubYear = min(Year),
            `Unified Publisher` = `Unified Publisher`[1],
            OA1 = `Open Access`[1],
            OA2 = ifelse(length(unique(Resource)) == 1, '', `Open Access`[2]),
            OA3 = ifelse(length(unique(Resource)) < 3, '', `Open Access`[3]),
            OA4 = ifelse(length(unique(Resource)) == 4, `Open Access`[4], ''),
            PubMedID = ifelse(is.na(`PubMed ID`[1]) == FALSE, `PubMed ID`[1],
                              ifelse(is.na(`PubMed ID`[2]) == FALSE, `PubMed ID`[2],
                                           ifelse(is.na(`PubMed ID`[3]) == FALSE, `PubMed ID`[3], `PubMed ID`[4]))),
            Authors = ifelse(is.na(`Authors`[1]) == FALSE, Authors[1],
                              ifelse(is.na(Authors[2]) == FALSE, Authors[2],
                                           ifelse(is.na(Authors[3]) == FALSE, Authors[3], Authors[4]))),
            NumAuthors = ifelse(Resource[1] == 'OpenAlex', length(str_split(Authors[1], ',')[[1]]), length(str_split(Authors[1], ';')[[1]])),
            SourceTitleA = `Source title`[1],
            SourceTitleB = ifelse(length(unique(Resource)) == 1, '', `Source title`[2]),
            SourceTitleC = ifelse(length(unique(Resource)) < 3, '', `Source title`[3]),
            SourceTitleD = ifelse(length(unique(Resource)) == 4, `Source title`[4], ''),
            DocumentType = `Document Type`[1],
            ResearchArea1 = `Research Areas`[1],
            ResearchArea2 = ifelse(length(unique(Resource)) == 1, '', `Research Areas`[2]),
            ResearchArea3 = ifelse(length(unique(Resource)) < 3, '', `Research Areas`[3]),
            ResearchArea4 = ifelse(length(unique(Resource)) == 4, `Research Areas`[4], ''),
            TimesCited = max(`Times Cited`, na.rm = TRUE),
            Affiliation1 = Affiliations[1],
            Affiliation2 = ifelse(length(unique(Resource)) == 1, '', Affiliations[2]),
            Affiliation3 = ifelse(length(unique(Resource)) < 3, '', Affiliations[3]),
            Affiliation4 = ifelse(length(unique(Resource)) == 4, Affiliations[4], ''),
            ISBN1 = ISBN[1],
            ISBN2 = ifelse(length(unique(Resource)) == 1, '', ISBN[2]),
            ISBN3 = ifelse(length(unique(Resource)) < 3, '', ISBN[3]),
            ISBN4 = ifelse(length(unique(Resource)) == 4, ISBN[4], ''),
            ISSN1 = ISSN[1],
            ISSN2 = ifelse(length(unique(Resource)) == 1, '', ISSN[2]),
            ISSN3 = ifelse(length(unique(Resource)) < 3, '', ISSN[3]),
            ISSN4 = ifelse(length(unique(Resource)) == 4, ISSN[4], ''),
            pageCount1 = `Page count`[1],
            pageCount2 = `Page count`[2],
            pageCount3 = `Page count`[3],
            pageCount4 = `Page count`[4],
            Title = Title[1],
            isCA1 = ifelse(grepl('Blacksburg', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | 
                           grepl('Virginia Tech', `Correspondence Address`[1], ignore.case = TRUE) == TRUE |
                           grepl('Virginia Polytechnic', `Correspondence Address`[1], ignore.case = TRUE) == TRUE | `Correspondence Address`[1] == 'Yes', 1, 0),
            isCA2 = ifelse(grepl('Blacksburg', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | 
                           grepl('Virginia Tech', `Correspondence Address`[2], ignore.case = TRUE) == TRUE |
                           grepl('Virginia Polytechnic', `Correspondence Address`[2], ignore.case = TRUE) == TRUE | `Correspondence Address`[2] == 'Yes', 1, 0),
            isCA3 = ifelse(grepl('Blacksburg', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | 
                           grepl('Virginia Tech', `Correspondence Address`[3], ignore.case = TRUE) == TRUE |
                           grepl('Virginia Polytechnic', `Correspondence Address`[3], ignore.case = TRUE) == TRUE | `Correspondence Address`[3] == 'Yes', 1, 0),
            isCA4 = ifelse(grepl('Blacksburg', `Correspondence Address`[4], ignore.case = TRUE) == TRUE | 
                           grepl('Virginia Tech', `Correspondence Address`[4], ignore.case = TRUE) == TRUE |
                           grepl('Virginia Polytechnic', `Correspondence Address`[4], ignore.case = TRUE) == TRUE |`Correspondence Address`[4] == 'Yes', 1, 0)) |>
  mutate(isCA1 = ifelse(is.na(isCA1) == TRUE, 0, isCA1),
         isCA2 = ifelse(is.na(isCA2) == TRUE, 0, isCA2),
         isCA3 = ifelse(is.na(isCA3) == TRUE, 0, isCA3),
         isCA4 = ifelse(is.na(isCA4) == TRUE, 0, isCA4)) |>
  mutate(OpenAccess = case_when(
          OA4 == 'closed' | OA3 == 'Closed' | OA2 == 'Closed' | OA1 == 'Closed' ~ 'Closed',
          str_detect(OA4, 'diamond') | str_detect(OA3, 'diamond') | str_detect(OA2, 'diamond') | str_detect(OA1, 'diamond') ~ 'Diamond',
          str_detect(OA4, 'hybrid') | str_detect(OA3, 'Hybrid') | str_detect(OA2, 'Hybrid') | str_detect(OA1, 'Hybrid') | str_detect(OA1, 'hybrid') ~ 'Hybrid',
          str_detect(OA4, 'gold') | str_detect(OA3, 'Gold') | str_detect(OA2, 'Gold') | str_detect(OA1, 'Gold') | str_detect(OA1, 'gold')  ~ 'Gold',
          str_detect(OA4, 'bronze') | str_detect(OA3, 'Bronze') | str_detect(OA2, 'Bronze') | str_detect(OA1, 'Bronze') ~ 'Bronze',
          str_detect(OA4, 'green') | str_detect(OA3, 'Green') | str_detect(OA2, 'Green') | str_detect(OA1, 'Green') ~ 'Green',
          .default = 'Not Given'
        ),
        pageCount = pmax(pageCount1, pageCount2, pageCount3, pageCount4, na.rm = TRUE),
        SourceTitle = case_when(
          SourceTitleD != '' ~ SourceTitleD,
          SourceTitleC != '' ~ SourceTitleC,
          SourceTitleB != '' ~ SourceTitleB,
          SourceTitleA != '' ~ SourceTitleA,
          .default = 'Not Given'
        ),
        ResearchArea = case_when(
          ResearchArea4 != '' ~ ResearchArea4,
          ResearchArea3 != '' ~ ResearchArea3,
          ResearchArea2 != '' ~ ResearchArea2,
          ResearchArea1 != '' ~ ResearchArea1,
          .default = 'Not Given'
        ),
        Affiliation = case_when(
          Affiliation4 != '' ~ Affiliation4,
          Affiliation3 != '' ~ Affiliation3,
          Affiliation2 != '' ~ Affiliation2,
          Affiliation1 != '' ~ Affiliation1,
          .default = 'Not Given'
        ),
        ISSN = case_when(
          ISSN4 != '' ~ ISSN4,
          ISSN3 != '' ~ ISSN3,
          ISSN2 != '' ~ ISSN2,
          ISSN1 != '' ~ ISSN1,
          .default = 'Not Given'
        ),
        ISBN = case_when(
          ISBN4 != '' ~ ISBN4,
          ISBN3 != '' ~ ISBN3,
          ISBN2 != '' ~ ISBN2,
          ISBN1 != '' ~ ISBN1,
          .default = 'Not Given'
        ),
        isCorrespondingAuthor = ifelse(isCA1 == 1 | isCA2 == 1 | isCA3 == 1 | isCA4 == 1, 1, 0),
        Databases = paste0(locationA, ', ', locationB, ', ', locationC, ', ', locationD)) |>
  mutate(Databases = str_replace(Databases, ",,", ",")) |>
  mutate(Databases = str_replace(Databases, " ,", ",")) |>
  mutate(Databases = str_replace(Databases, ",,", "")) |>
  mutate(Databases = ifelse(
    substr(Databases, nchar(Databases) - 1, nchar(Databases)) == ', ', substr(Databases, 1, nchar(Databases) - 2), Databases
  )) |>
  mutate(`Unified Document Type` = case_when(
    DocumentType %in% c('Review', 'Review Article', 'Book Review', 'Review; Book Chapter', 'Review; Early Access', 'Art Exhibit Review', 'Music Performance Review', 'Theater Review', 'Book Review; Early Access', 'Film Review', 'Art Exhibit Review', 'Book Review; Book Chapter', 'Database Review', 'review', 'peer-review') ~ 'Review',
    DocumentType %in% c('Article', 'Research Article', 'Article; Early Access', 'Article; Data Paper', 'Article; Publication with Expression of Concern', 'Article in press', 'article', 'preprint', 'report', 'dissertation') ~ 'Article',
    DocumentType %in% c('Book', 'Book chapter', 'Article; Book Chapter', 'Fiction, Creative Prose', 'Biographical-Item; Book Chapter', 'book-chapter', 'book') ~ 'Book',
    DocumentType %in% c('Letter', 'Letter To Editor', 'Letter to Editor', 'Editorial', 'Editorial Material', 'Editorial Material; Early Access', 'Editorial Material; Book Chapter', 'Letter; Early Access', 'editorial', 'letter') ~ 'Editorial Material',
    DocumentType %in% c('Correction', 'Correction; Book Chapter', 'Correction Erratum', 'Correction; Early Access') ~ 'Correction',
    DocumentType %in% c('Conference paper', 'Proceedings Paper', 'Article; Proceedings Paper') ~ 'Proceedings Paper',
    DocumentType %in% c('Conference Abstract', 'Meeting Abstract') ~ 'Abstract',
    .default = 'Other'
  )) |>
  mutate(ResearchArea = sapply(ResearchArea, function(x) paste(unique(unlist(str_split(x," , "))), collapse = ", "))) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor) |>
  mutate(`Publication Campus` = 'Virginia Tech')



for (i in 1:dim(vtFinal)[1]){

  stringSplit = ifelse(
    length(str_split(vtFinal$Affiliation[i], ' , ')[[1]]) > 1, str_split(vtFinal$Affiliation[i], ' , ')[[1]], str_split(vtFinal$Affiliation[i], ';')[[1]]
  )

  vtFinal$isFirstAuthor[i] = ifelse(grepl('Virginia Tech', stringSplit[1], fixed = TRUE) == TRUE |
                                    grepl('Blacksburg', stringSplit[1], fixed = TRUE) == TRUE |
                                    grepl('Virginia Polytechnic', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
  vtFinal$isLastAuthor[i] = ifelse(grepl('Virginia Tech', stringSplit[length(stringSplit)], fixed = TRUE) == TRUE |
                                    grepl('Blacksburg', stringSplit[1], fixed = TRUE) == TRUE |
                                    grepl('Virginia Polytechnic', stringSplit[1], fixed = TRUE) == TRUE, 1, 0)
}



vtFinal
```




## Export to the Database


```{r}
dbWriteTable(con, name = 'full_pubs_virginiatech', value = vtFinal, append = FALSE, overwrite = TRUE)
```







# Combine All Universities


```{r}
peerFinal <- rbind(auburnFinal, clemsonFinal, iowaStateFinal, coloradoFinal, kentuckyFinal, missouriFinal, nebraskaFinal, oklahomaFinal, scFinal, vtFinal)

peerFinal
```


```{r}
test <- peerFinal |>
  group_by(OpenAccess) |>
  summarise(n = n()) |>
  arrange(desc(n))

dim(peerFinal)
test
```




```{r}
dbWriteTable(con, name = 'full_pubs_peerinstitutions', value = peerFinal, append = FALSE, overwrite = TRUE)
```



```{r}
peerFinal <- dbGetQuery(con, 
                           "
                           SELECT *
                           FROM full_pubs_peerinstitutions
                           ")

peerFinal
```



# Export for PowerBI


```{r, warning = FALSE}
setwd('C:\\Users\\aharrima\\OneDrive - University of Tennessee\\Documents\\Big Package Usage Across the UT System\\Publication Analysis')

peerExport <- peerFinal |>
  mutate(isOAwithGreen = ifelse(OpenAccess %in% c('Closed', 'Not Given'), 0, 1),
         isOAwithGreenPerc = ifelse(OpenAccess %in% c('Closed', 'Not Given'), 0, 1),
         isOAwithoutGreen = ifelse(OpenAccess %in% c('Closed', 'Not Given', 'Green'), 0, 1),
         isOAwithoutGreenPerc = ifelse(OpenAccess %in% c('Closed', 'Not Given', 'Green'), 0, 1),
         isNotAnyOA = ifelse(OpenAccess %in% c('Closed', 'Not Given'), 1, 0),
         isNotGoodOA = ifelse(OpenAccess %in% c('Closed', 'Not Given', 'Green'), 1, 0),
         isBronze = ifelse(OpenAccess == 'Bronze', 1, 0),
         isGold = ifelse(OpenAccess == 'Gold', 1, 0), 
         isHybrid = ifelse(OpenAccess == 'Hybrid', 1, 0),
         isGreen = ifelse(OpenAccess == 'Green', 1, 0),
         isGreen2 = ifelse(OpenAccess == 'Green', 1, 0),
         isDiamond = ifelse(OpenAccess == 'Diamond', 1, 0),
         isFirstOrLast = ifelse(isFirstAuthor == 1 | isLastAuthor == 1, 1, 0),
         isCorrespondingAuthor = ifelse(isCorrespondingAuthor == 1, 1, 0)) |>
  mutate(Authors = ifelse(nchar(Authors) > 25000, paste0(substr(Authors, 1, 25000), '...'), Authors),
         Affiliation = ifelse(nchar(Affiliation) > 25000, paste0(substr(Affiliation, 1, 25000), '...'), Affiliation)) |>
  filter(is.na(DOI) == FALSE) |>
  select(DOI, locationCount, pubYear, `Unified Publisher`, Databases, OpenAccess, PubMedID, Authors, NumAuthors, SourceTitle, DocumentType, `Unified Document Type`, ResearchArea, TimesCited, Affiliation, ISSN, ISBN, pageCount, Title, isCorrespondingAuthor, `Publication Campus`, isFirstAuthor, isLastAuthor, isOAwithGreen, isOAwithGreenPerc, isOAwithoutGreen, isOAwithoutGreenPerc, isNotAnyOA, isNotGoodOA, isBronze, isGold, isHybrid, isGreen, isGreen2, isDiamond, isFirstOrLast)

write_xlsx(peerExport, 'All Publications UT Peer Institutions.xlsx')
```

